### 2022-05-05 docs/preprint/manuscript.tex
init

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  doc, donotrepeattitle,floatsintext]{apa7}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
\usepackage{csquotes}
\usepackage{pdflscape}
\usepackage{setspace}
\raggedbottom
\renewcommand\author[1]{}
\renewcommand\affiliation[1]{}
\authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Exercising choice over feedback schedules during practice is not advantageous for motor learning},
  pdflang={en-EN},
  pdfkeywords={Self-controlled, Knowledge of results, OPTIMAL theory, Retention},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Exercising choice over feedback schedules during practice is not advantageous for motor learning}
\author{\phantom{0}}
\date{}

\shorttitle{Choice and feedback characteristics}

\authornote{

\vspace{-0.5cm}

\noindent \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183} \newline
\noindent \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
\noindent \addORCIDlink{Joshua G.A. Cashaback}{0000-0002-8642-6648} \newline
\noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
\noindent Data and code: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics} \vspace{2ex} \newline
\noindent \textbf{Corresponding authors:} Michael J. Carter (\href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}) and Laura St.~Germain (\href{mailto:stgerml@mcmaster.ca}{\nolinkurl{stgerml@mcmaster.ca}}).

}

\affiliation{\phantom{0}}

\abstract{%
The idea that there is a self-controlled learning advantage, where individuals demonstrate improved motor learning after exercising choice over an aspect of practice compared to no-choice groups, has different causal explanations according to the OPTIMAL theory or an information-processing perspective. Within OPTIMAL theory, giving learners choice is considered an autonomy-supportive manipulation that enhances expectations for success and intrinsic motivation. In the information-processing view, choice allows learners to engage in performance-dependent strategies that reduce uncertainty about task outcomes. To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a rapid reaching task with spatial and timing goals. Across both experiments (N = 228 participants), we did not find evidence to support a self-controlled learning advantage. Exercising choice during practice did not increase perceptions of autonomy, competence, or intrinsic motivation, nor did it lead to more accurate error estimation skills. Both error and graded feedback facilitated skill acquisition and learning, whereas no improvements from pre-test performance were found with binary feedback. Finally, the impact of graded and binary feedback on perceived competence highlights a potential dissociation of motivational and informational roles of feedback. Although our results regarding self-controlled practice conditions are difficult to reconcile with either the OPTIMAL theory or the information-processing perspective, they are consistent with a growing body of evidence that strongly suggests self-controlled conditions are not an effective approach to enhance motor performance and learning.
}

\begin{document}
\maketitle

The underlying source of errors in skilled actions are often ambiguous and difficult to assign as the learner must rely on noisy and delayed sensory information. Feedback from an external source, such as a coach or computer display, can facilitate or augment this process (Sigrist et al., 2013). Knowledge of results feedback (Salmoni et al., 1984) can provide varying amounts of information to learners depending on its characteristics. Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., ``too far''), and binary feedback indicates only success or failure information (e.g., ``miss'') (Luft, 2014). When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning. These self-controlled feedback schedules have typically enhanced motor skill learning compared to yoked feedback schedules, wherein learners experience the feedback schedule created by a self-controlled counterpart, but without any choice (see Sanli et al., 2013; Ste-Marie et al., 2020 for reviews).

Why self-controlled learning advantages emerge has garnered considerable attention in the motor skill learning literature. Within their OPTIMAL (Optimizing performance through intrinsic motivation and attentional learning) theory of motor learning, Wulf and Lewthwaite (2016) have argued that providing participants the opportunity to exercise choice, as in a self-controlled group, creates a virtuous cycle. Specifically, choice leads to increased (perceived) autonomy, leading to enhanced expectancies (e.g., perceived competence) and increased (intrinsic) motivation. These motivational influences lead to improved motor performance, creating a positive feedback loop that ultimately enhances motor learning compared to those not given the same choice opportunities. Support for this view has been drawn from experimental work where participants exercise choice over task-irrelevant or incidental choices. Exercising choice over the color of golf balls to putt (Lewthwaite et al., 2015 Experiment 1) or the mat underneath a target (Wulf et al., 2018 Experiment 1), which picture to hang in a lab (Lewthwaite et al., 2015 Experiment 2), hand order in a maximal force production task (Iwatsuki et al., 2017), which photos to look at while running (Iwatsuki et al., 2018), and the order of exercises to perform (Wulf et al., 2014) have been suggested to improve motor performance or learning. Other research, however, have failed to replicate this benefit of task-irrelevant or incidental choices on motor performance or learning (Carter \& Ste-Marie, 2017a; Grand et al., 2017; McKay \& Ste-Marie, 2020a, 2020b).

Rather than a motivational account, others have forwarded an information-processing explanation. From this perspective, exercising choice allows learners to tailor practice to their individual needs (Chiviacowsky \& Wulf, 2005, 2002) by engaging in performance-contingent strategies (Carter et al., 2014, 2016; Laughlin et al., 2015; Pathania et al., 2019) to reduce uncertainty about movement outcomes (Barros et al., 2019; Carter et al., 2014; Carter \& Ste-Marie, 2017a, 2017b; Grand et al., 2015). Evidence for this view has come from experiments that showed the timing of the feedback decision relative to task performance matters (Carter et al., 2014; Chiviacowsky \& Wulf, 2005), that task-relevant choices are more effective than task-irrelevant choices (Carter \& Ste-Marie, 2017a; cf. Wulf et al., 2018 Experiment 2), that interfering with information-processing activities during (Couvillion et al., 2020; Woodard \& Fairbrother, 2020) or after (Carter \& Ste-Marie, 2017b; Woodard \& Fairbrother, 2020) task performance eliminates self-controlled learning benefits, and that the ability to accurately estimate one's performance is enhanced in choice compared to yoked groups (Carter et al., 2014; Carter \& Patterson, 2012). Thus, further investigation is required to test predictions from these two explanations to better understand why exercising choice during practice confers an advantage for motor skill learning.

To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we provided participants in choice and yoked (i.e., no-choice) groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) during the acquisition of a rapid aiming task. Motor learning was assessed using delayed (\textasciitilde24 hours) retention and transfer tests. If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule \emph{would not matter} for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups. Thus, we predicted all choice groups would demonstrate superior performance and learning compared to the yoked groups. Alternatively, if the information-processing account is correct, we hypothesized that the characteristics of one's feedback schedule \emph{would matter} for the self-controlled learning advantage as feedback with greater informational value would be more effective for reducing uncertainties about movement outcomes. Thus, we predicted that choice over an error feedback schedule would be the most effective pairing for performance and learning. We also included self-report measures of perceptions of autonomy, competence, and intrinsic motivation, and assessments of error estimation abilities to respectively test auxiliary assumptions of the OPTIMAL theory and information-processing explanations.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012). All data and \texttt{R} scripts can be accessed here: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{experiment-1}{%
\subsubsection{Experiment 1}\label{experiment-1}}

One hundred and fifty-two right-handed (Oldfield, 1971), healthy adults participated in Experiment 1 (\(M_{age}\) = 20.64 years, \(SD_{age}\) = 2.45, 88 females). Sample size was determined from an \emph{a-priori} power analysis using the \emph{ANOVA: fixed effects, main effects and interactions} option in G*Power (Faul et al., 2009) with the following parameters: \(\alpha\) = 0.05, \(\beta\) = .20, \(f\) = 0.23, numerator = 1, and groups = 2. This revealed a required sample of 151 participants. Our chosen effect size was based on a meta-analytic estimate (\(f\) = .32) by McKay et al. (2014); however, we used a more conservative estimate given the uncertainty of how choice would interact with our feedback characteristic manipulation. Participants were compensated \$15 CAD or with course-credit for their time. All participants gave written informed consent and the experiment was approved by McMaster University's Research Ethics Board.

\hypertarget{experiment-2}{%
\subsubsection{Experiment 2}\label{experiment-2}}

A new sample of 76 right-handed (Oldfield, 1971), healthy adults participated in Experiment 2 (\(M_{age}\) = 20.18 years, \(SD_{age}\) = 3.18, 47 females). Sample size was selected so group size matched that used in Experiment 1. Participants were compensated \$15 CAD or with course-credit for their time. All participants gave written informed consent and the experiment was approved by McMaster University's Research Ethics Board.

\hypertarget{task}{%
\subsection{Task}\label{task}}

In Experiments 1 and 2, participants sat in a chair facing a monitor (1920x1080 resolution) with their left arm in a custom manipulandum that restricted movement to the horizontal plane. Their elbow was bent at approximately 90° and they grasped a vertical handle with their left hand. Handle position was adjusted as needed to ensure the central axis of rotation was about the elbow. The task required a rapid ``out-and-back'' movement such that the reversal happened at \(40^\circ\) (in pre-test, acquisition, and retention) or \(60^\circ\) (in transfer). The starting point for all trials was \(0^\circ\). Participants were instructed to make a smooth movement to the reversal and back without hesitating when reversing their movement. The movement time goal to the reversal was always 225 ms. The task and instructions were similar to those used by Sherwood (1996; 2009). Vision of the manipulandum and limb were occluded during all phases of the experiment. Angular displacement for the elbow was collected via a potentiometer attached to the axis of rotation of the custom manipulandum. Potentiometer data were digitally sampled at 1000 Hz (National Instruments PCIe-6321) using a custom LabVIEW program and stored for offline analysis.

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{experiment-1-1}{%
\subsubsection{Experiment 1}\label{experiment-1-1}}

The first 76 participants were randomly assigned to either the Choice+Error-Feedback group (\(n\) = 38; \(M_{age}\) = 20.24 years, \(SD_{age}\) = 2.37, 22 females) or the Choice+Graded-Feedback group (\(n\) = 38; \(M_{age}\) = 20.76 years, \(SD_{age}\) = 3.02, 26 females). This is typical in the self-controlled learning literature as the self-controlled participants' self-selected feedback schedules are required for providing feedback to the participants in the yoked (i.e., control) groups. The remaining 76 participants were randomly assigned to either the Yoked+Error-Feedback group (\(n\) = 38; \(M_{age}\) = 20.53 years, \(SD_{age}\) = 2.13, 23 females) or the Yoked+Graded-Feedback group (\(n\) = 38; \(M_{age}\) = 21.03 years, \(SD_{age}\) = 2.32, 22 females).

Data collection consisted of two sessions separated by approximately 24 hours.\footnote{Six participants (three Choice+Error-Feedback and three Choice+Graded-Feedback) had their second session completed approximately 48 hours later because a snowstorm closed the University.} Session one included a pre-test (12 trials) and an acquisition phase (72 trials). Session two included the delayed retention (12 trials) and transfer (12 trials) tests. No feedback about motor performance was provided in pre-test, retention, or transfer. Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals. Additionally, half of the participants in each group were randomly selected to estimate their performance on the spatial and timing goals after each trial in the pre-test. Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested (e.g., Chiviacowsky \& Wulf, 2005) to be adopted spontaneously by participants controlling their feedback schedule. However, asking participants to estimate their performance during pre-test is necessary to be able to assess how this skill develops as a function of one's practice condition.

Participants were reminded of the instructions about the task and its associated goals at the start of the acquisition phase. Group specific instructions regarding feedback were also provided. Participants in the Choice+Error-Feedback group and the Choice+Graded-Feedback group were told they could choose their feedback schedule, with the restriction that they must select feedback on 24 of the 72 acquisition trials. They were informed that if the number of remaining feedback requests equaled the number of remaining acquisition trials, these trials would default to feedback trials. This feedback restriction was implemented to ensure the relative frequency of feedback was equated across all groups. Similar restrictions have been used in past research involving multiple choice groups (e.g., Chiviacowsky \& Wulf, 2005). Participants in the Yoked+Error-Feedback group and the Yoked+Graded-Feedback group were told they may or may not receive feedback following a trial based on a predetermined schedule. Thus, participants in these groups were not aware that their feedback schedule was actually created by a participant in a corresponding choice group. While this yoking procedure ensures that the total number of feedback trials and their relative placement during acquisition are identical, the content of the feedback reflected each participant's own performance. Error feedback for the spatial and timing goals was provided as the difference between the participant's actual performance and the task goal (i.e., constant error). Graded feedback for the spatial goal was provided as ``too short'' if performance was \textless{} 40 degrees (or 60 degrees in transfer), ``hit'' if exactly 40 degrees, and ``too far'' if \textgreater{} 40 degrees. For the timing goal, graded feedback was provided as ``too fast'' when performance was \textless{} 225 ms, ``hit'' if exactly 225 ms, and ``too slow'' if \textgreater{} 225 ms. All participants were shown a sample feedback display that corresponded to their experimental group and were asked to interpret it aloud for the researcher to verify understanding.

\begin{figure}

{\centering \includegraphics[height=0.45\textheight]{../../figs/fig1}

}

\caption{\small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase. Trials began by informing participants the trial number (500 ms) they were on in acquisition. Shortly after, the text ``Get Ready!'' appeared on the screen and 800 ms later a visual go-signal was presented in the form of a green circle in the center of the screen. Participants began their movement when ready after seeing the visual go-signal as we were not interested in reaction time. While participants completed their rapid out-and-back movement, the computer screen was blank. Upon returning to the starting position, a red circle appeared in the center of the screen. A 2000 ms feedback delay interval was used and this interval was followed by the feedback prompt. The feedback prompt also displayed an updated counter representing the number of feedback trials they had left. If the number of remaining feedback trials matched the number of acquisition trials left, these trials automatically defaulted to feedback trials. On trials where feedback was not requested, a blank screen \textbf{(A)} was shown for 3000 ms. When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group. The error feedback group \textbf{(B)} saw their constant error, the graded feedback group \textbf{(C)} saw either ``too far'' or ``too short'' for the spatial goal and ``too fast'' or ``too slow'' for the timing goal, and the binary feedback group \textbf{(D)} saw either ``hit'' or ``miss'' for the task goals. The sequence of events was the same for the yoked groups with the exception they did not see a feedback prompt. The sequence of events was similar in pre-test, retention, and transfer except all trials were no-feedback trials.}\label{fig:fig1}
\end{figure}

A typical acquisition trial (see Figure \ref{fig:fig1}) began with the current trial number displayed (500 ms), followed by a visual ``Get Ready!'' and a visual go-signal (800 ms apart). Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task. The computer screen was blank while participants made their movement. When participants returned to the starting position, a red circle was displayed on the monitor. Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups. If feedback was not selected, a blank screen was displayed for 3000 ms. If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.

Before the retention and transfer tests, participants were reminded about the task and its associated goals. All participants were asked to estimate their performance after each trial in retention and transfer. After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy. The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a). Cronbach's alpha values for each questionnaire at each time point are reported in Table \ref{tab:table1}.

\hypertarget{experiment-2-1}{%
\subsubsection{Experiment 2}\label{experiment-2-1}}

Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 22.37 years, \(SD_{age}\) = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 18.00 years, \(SD_{age}\) = 0.93, 28 females). Binary feedback for the spatial goal was provided as ``hit'' if performance was exactly 40 degrees (or 60 degrees in transfer) and as ``miss'' for everything else. For the timing goal, binary feedback was provided as ``hit'' when performance was exactly 225 ms and as ``miss'' for everything else. Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.

\begin{table}

\caption{\label{tab:table1}Cronbach's alpha for each questionnaire at each timepoint.}
\fontsize{11}{13}\selectfont
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
\toprule
Questionnaire & After pre-test & After block 1 & After block 6 & Before retention\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 1}}\\
\hspace{1em}Perceived autonomy & 0.68 & 0.81 & 0.80 & 0.83\\
\hspace{1em}Perceived competence & 0.86 & 0.93 & 0.95 & 0.94\\
\hspace{1em}Intrinsic motivation & 0.86 & 0.90 & 0.92 & 0.93\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Experiment 2}}\\
\hspace{1em}Perceived autonomy & 0.39 & 0.73 & 0.79 & 0.85\\
\hspace{1em}Perceived competence & 0.92 & 0.88 & 0.91 & 0.91\\
\hspace{1em}Intrinsic motivation & 0.91 & 0.91 & 0.93 & 0.94\\
\bottomrule
\multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase.}\\
\end{tabular}
\end{table}

\hypertarget{data-analysis}{%
\subsection{Data Analysis}\label{data-analysis}}

Movement trajectories for all trials were visually inspected by a researcher and trials with errors (e.g., technical issues, moving before the ``go'' signal) were removed. A total of 4.03\% (662/16146) and 3.73\% (306/8208) of trials for Experiments 1 and 2 were removed, respectively. Trials were aggregated into blocks of 12 trials, resulting in one block of trials for pre-test, retention, and transfer, and six blocks of trials for acquisition. Our primary performance outcome variable was total error (E) (Henry, 1974, 1975) and was computed using the equation:
\begin{equation}
E = \sqrt{\sum{(x_{i} - T)^2 / n}}
\end{equation}
where \(x_{i}\) is the score on the \(i\)th trial, \(T\) is the target goal, and \(n\) is the number of trials in a block.

To test for performance differences in pre-test, retention, and transfer, total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 3 Test; \emph{Experiment 2:} 2 Choice x 3 Test). To test for performance differences during acquisition, total error for the spatial and timing goals during acquisition were analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 6 Block; \emph{Experiment 2:} 2 Choice x 6 Block). Our primary psychological outcome variables were intrinsic motivation (i.e., interest/enjoyment), perceived competence, and perceived autonomy. The mean score of the responses for these constructs at each time point was calculated for each participant and analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 4 Time; \emph{Experiment 2:} 2 Choice x 4 Time). Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50\% of the participants in each group in Experiments 1 and 2), retention, and transfer (see \textbf{Supplementary A}).

Alpha was set to .05 for all statistical analyses. Corrected degrees of freedom using the Greenhouse-Geisser technique are always reported for repeated measures with more than two levels. Generalized eta squared \((\eta_{G}^2)\) is provided as an effect size statistic (Bakeman, 2005; Lakens, 2013; Olejnik \& Algina, 2003) for all omnibus tests. Post hoc comparisons were Holm-Bonferroni corrected to control for multiple comparisons. Statistical tests were conducted using R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann et al., 2021), \emph{computees} (Re, 2013), \emph{ggResidpanel} (Version 0.3.0.9000; Goode \& Rey, 2022), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{metafor} (Version 3.4.0; Viechtbauer, 2010), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.0.9000; Pedersen, 2020), \emph{rogme} (Version 0.2.1; Rousselet et al., 2017), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) were used in this project.

\hypertarget{results}{%
\section{Results}\label{results}}

Model diagnostics of total error for the spatial and timing goals revealed skewed distributions. We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions (Rousselet \& Wilcox, 2020; Wilcox, 2021). The results of these analyses (see \textbf{Supplementary B}) were consistent with those of the mixed ANOVAs, which we report below.

\hypertarget{pre-test-retention-and-transfer}{%
\subsection{Pre-test, retention, and transfer}\label{pre-test-retention-and-transfer}}

\hypertarget{experiment-1-2}{%
\subsubsection{Experiment 1}\label{experiment-1-2}}

Spatial (Fig. \ref{fig:fig2}A) and timing (Fig. \ref{fig:fig2}B) error decreased from the pre-test to the retention and transfer tests. There was a main effect of Test for spatial error, \(F(1.33,196.52) = 40.20\), \(p < .001\), \(\eta_{G}^2 = .138\), where performance was less errorful in retention and transfer than pre-test (\(p\)'s \textless{} .001) and performance in retention was better than transfer (\(p\) \textless{} .001). A main effect of Test was also found for timing error, \(F(1.08,160.23) = 81.21\), \(p < .001\), \(\eta_{G}^2 = .245\), with pre-test performance more errorful than both retention and transfer (\(p\)'s \textless{} .001), and retention was less errorful than transfer (\(p\) \textless{} .001).

\hypertarget{experiment-2-2}{%
\subsubsection{Experiment 2}\label{experiment-2-2}}

Spatial (Fig. \ref{fig:fig3}A) and timing (Fig. \ref{fig:fig3}B) error did not change considerably from the pre-test to the retention and transfer tests. There were no significant main effects or interactions for either task goals.

\vspace{4ex}

\begin{figure}

{\centering \includegraphics{../../figs/fig2}

}

\caption{\small \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses. Error bars denote 95\% bootstrapped confidence intervals. \textbf{(A)} Spatial total error (degrees) and \textbf{(B)} timing total error (ms) averaged across blocks and participants within each group. Dotted vertical lines denote the different experimental phases. Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2. Self-reported scores for perceived autonomy \textbf{(C)}, perceived competence \textbf{(D)}, and intrinsic motivation \textbf{(E)} after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2. Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree). Dots represent individual data points.}\label{fig:fig2}
\end{figure}

\begin{figure}

{\centering \includegraphics{../../figs/fig3}

}

\caption{\small \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares. Error bars denote 95\% bootstrapped confidence intervals. \textbf{(A)} Spatial total error (degrees) and \textbf{(B)} timing total error (ms) averaged across blocks and participants within each group. Dotted vertical lines denote the different experimental phases. Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2. Self-reported scores for perceived autonomy \textbf{(C)}, perceived competence \textbf{(D)}, and intrinsic motivation \textbf{(E)} after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2. Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree). Dots represent individual data points.}\label{fig:fig3}
\end{figure}

\newpage

\hypertarget{acquisition}{%
\subsection{Acquisition}\label{acquisition}}

\hypertarget{experiment-1-3}{%
\subsubsection{Experiment 1}\label{experiment-1-3}}

All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig. \ref{fig:fig2}A). This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)). Timing error also decreased during the acquisition period (Fig. \ref{fig:fig2}B). The significant main effect of Block, \(F(1.75,259.59) = 55.44\), \(p < .001\), \(\eta_{G}^2 = .138\), was superseded by a significant Feedback x Block interaction, \(F(1.75, 259.59) = 3.56\), \(p = .035\), \(\eta_{G}^2 = .010\). Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)), but performance plateaued from block 2 onward in acquisition (\(p\)'s \(\geq .257\)). Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).

\hypertarget{experiment-2-3}{%
\subsubsection{Experiment 2}\label{experiment-2-3}}

Spatial (Fig. \ref{fig:fig3}A) and timing (Fig. \ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period. None of the main effects or interactions for either task goals were significant.

\hypertarget{psychological-variables}{%
\subsection{Psychological variables}\label{psychological-variables}}

\hypertarget{experiment-1-4}{%
\subsubsection{Experiment 1}\label{experiment-1-4}}

Perceptions of autonomy (Fig. \ref{fig:fig2}C) showed a slight decrease across time points, supported by a main effect of Time, \(F(2.25,332.95) = 3.69\), \(p < .022\), \(\eta_{G}^2 = .003\). Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test (\(p = .031\)). Self-ratings for perceived competence (Fig. \ref{fig:fig2}D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic. Main effects of Time, \(F(1.92, 283.47) = 3.43\), \(p = .036\), \(\eta_{G}^2 = .006\), and Feedback, \(F(1,148) = 47.36\), \(p < .001\), \(\eta_{G}^2 = .188\), were superseded by a Feedback x Time interaction, \(F(1.92, 283.47) = 28.04\), \(p < .001\), \(\eta_{G}^2 = .050\). Perceived competence scores were not significantly different after the pre-test (\(p = .232\)); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points (\(p\)'s \(< .001\)). Self-reported scores for intrinsic motivation (Fig. \ref{fig:fig2}E) generally decreased after block 1, which was supported by a main effect of Time, \(F(2.40,355.90) = 14.69\), \(p < .001\), \(\eta_{G}^2 = .012\). Intrinsic motivation scores initially increased following the pre-test to after block 1 (\(p = .003\)); however, scores after block 1 of acquisition were greater than those reported at the end of acquisition (i.e., block 6) and before retention (\(p\)'s \(< .001\)). Self-reported ratings were also lower before retention compared to after the pre-test (\(p = .043\)).

\hypertarget{experiment-2-4}{%
\subsubsection{Experiment 2}\label{experiment-2-4}}

Self-reported scores for perceived autonomy (Fig. \ref{fig:fig3}C) were similar across all time points. There were no main effects or interactions. Perceptions of competence (Fig. \ref{fig:fig3}D) showed a considerable decrease after the pre-test, \(F(1.85,136.91) = 106.10\), \(p < .001\), \(\eta_{g}^2 = .298\), where scores were significantly greater after the pre-test compared to all other time points (\(p\)'s \(< .001\)), and were higher after block 1 of acquisition than before retention (\(p = .004\)). Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, \(F(2.37,175.55) = 15.31\), \(p < .001\), \(\eta_{G}^2 = .018\). Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention (\(p\)'s \(< .001\)), and higher after block 1 than after block 6 and before retention (\(p\)'s \(< .026\)).

\hypertarget{equivalence-analysis}{%
\subsection{Equivalence analysis}\label{equivalence-analysis}}

Our main comparison of interest was between choice and no-choice (i.e., yoked groups). To evaluate the self-controlled learning effect observed across Experiments 1 and 2, Hedges' \emph{g} for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies. Next, a random effects meta-analysis was conducted on the retention test data\footnote{We report an estimate for retention tests to facilitate comparison to a recent meta-analysis (McKay et al., in-press) that produced estimated effects of self-controlled learning at retention specifically.} to generate a summary point estimate and 90\% confidence intervals (CI). This resulted in an overall estimated effect of \(g = .05\) (favoring self-controlled) and \(90\% \,CI \,[-.12,.23]\).

Equivalence tests can be conducted to evaluate whether the observed differences are significantly smaller than a pre-determined smallest effect size of interest (see Harms \& Lakens, 2018 for a discussion). Typically, a two one-sided tests procedure is used to compare the observed effect to upper and lower equivalence bounds, and if the effect is significantly smaller than both bounds then the hypothesis that the effect is large enough to be of interest is rejected (Lakens, 2017; Schuirmann, 1987). However, we did not pre-specify a smallest effect of interest, so instead we report the 90\% confidence intervals (see above). All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not. Therefore, the present experiments can be considered inconsistent with all effects larger than \(g = \pm.23\).

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The purpose of the present experiments was to test between motivational and information-processing accounts of the putative self-controlled learning advantage (see Ste-Marie et al., 2020 for a review). According to the OPTIMAL theory (Wulf \& Lewthwaite, 2016), self-controlled practice or choice conditions are advantageous because the provision of choice increases perceptions of autonomy and competence, which increase intrinsic motivation and ultimately both motor performance and learning. Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals (Carter et al., 2014; Carter \& Ste-Marie, 2017b; Grand et al., 2015). In contrast to these predictions, we did not find evidence that providing learners with choice over their feedback schedule was beneficial for motor learning, despite collecting a much larger sample (\emph{N} = 228 across both Experiments) than those commonly used in self-controlled learning experiments (median sample size \emph{N} = 36 in a meta-analysis by McKay et al., in-press) and motor learning experiments in general (median \emph{n}/group = 11 in a review by Lohse et al., 2016). Further, exercising choice in practice did not enhance perceptions of autonomy, competence, or intrinsic motivation, and also did not result in more accurate performance estimations in delayed tests of motor learning. Overall, we found no support for the OPTIMAL theory or information-processing perspective. Our results challenge the prevailing view that the self-controlled learning benefit is a robust effect.

The failed replication of a self-controlled learning advantage was surprising given the dominant view for the past 25 years has been that it is a robust effect and one that should be recommended to coaches and practitioners (Sanli et al., 2013; Ste-Marie et al., 2020; Wulf \& Lewthwaite, 2016). Our findings are, however, consistent with a growing list of relatively large--often pre-registered--experiments that have not found self-controlled learning benefits (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press). One possible explanation for this discrepancy between earlier and more recent experiments may be that the self-controlled learning advantage was the result of underpowered designs, which has been highlighted as a problem in motor learning research (see Lohse et al., 2016 for a discussion). When underpowered designs find significant results, they are prone to be false positives with inflated estimates of effects (Button et al., 2013; Lakens \& Evers, 2014), which can be further exaggerated with questionable research practices such as \emph{p}-hacking and selective reporting (e.g., Munafò et al., 2017; Simmons et al., 2011). Thus, a self-controlled learning advantage may not actually exist. Alternatively, if one does exist then it seems likely it is a much smaller effect than originally estimated and requires considerably larger samples to reliability detect than those commonly used in motor learning research. Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results (McKay et al., in-press). We estimated the overall effect of self-controlled practice in retention to be significantly smaller than any effect larger than \(g = .23\). This is consistent with the estimates from McKay et al. (in-press) after accounting for publication bias (\(g =\) -.11 to .26), which suggested either no effect or a small effect in an unknown direction. Taken together, we argue that it may be time for the self-controlled learning advantage to be considered a non-replicable effect in motor learning.

Given our current replication failure with those in recent years (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press) and the conclusions from McKay et al. (in-press), motivational (i.e., OPTIMAL theory) versus information-processing explanations seem moot. Nevertheless, the present results are incompatible with both perspectives. Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory. Similarly, self-controlled feedback schedules did not enhance error estimation skills (see \textbf{Supplementary A}) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective. Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose. When feedback provided information about the direction of an error or when it contained both direction and magnitude of an error, participants were able to improve at the task throughout acquisition and retain these improvements in skill relative to pre-test. However, when feedback was binary and direction and magnitude of an error was absent, there was no improvement in skill from baseline levels. This is in contrast with past research that has shown people can learn motor tasks with binary feedback (e.g., Cashaback et al., 2017, 2019; Izawa \& Shadmehr, 2011). One possible explanation for this discrepancy may be the amount of practice trials (Magill \& Wood, 1986). Practicing with binary feedback may inherently require a longer training period for learning to occur compared to graded and error feedback, which both have greater precision. Additionally, we used a strict criteria with binary feedback where any outcome other than zero error was considered a miss. Thus, binary feedback may be more effective when paired with a tolerance zone such as that used in the bandwidth technique (see Anderson et al., 2020 for a review; Cauraugh et al., 1993; Lee \& Carnahan, 1990).

Although unexpected, the influence of feedback characteristics on perceptions of competence may hint to a dissociation between informational and motivational impacts of knowledge-of-results feedback. In Experiment 1, participants who received graded feedback reported significantly lower perceptions of competence than participants who received error feedback. Yet, despite these lower expectations for success, the graded feedback groups did not demonstrate degraded performance or learning compared to the error feedback group. Participants in Experiment 2 who received binary feedback reported the lowest perceptions of competence and were also the only participants who did not show improvements in task performance from pre-test. Thus, future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.

In two experiments we failed to observe the predicted benefits of self-controlled feedback on motor learning. Similarly, we failed to find the predicted motivational and informational consequences of choice in either experiment, challenging both the OPTIMAL theory and information-processing explanation of the so-called self-controlled learning advantage. Although the present experiments were not pre-registered, the analysis plan was determined prior to viewing the data. In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see \textbf{Supplementary B}). The sensitivity analyses supported the conclusions of the primary analyses and are consistent with research that has followed pre-registered analysis plans (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press). Lastly, our results and conclusions are in line with a recent meta-analysis (McKay et al., in-press) that suggests the apparent benefits of self-controlled practice are due to selection bias rather than true effects.

\vspace{2.5ex}

\hypertarget{funding}{%
\section{Funding}\label{funding}}

This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University. LSG was supported by an NSERC Postgraduate Scholarship. JGAC was supported by an NIH U45GM104941 grant. AW and AP were supported by NSERC Undergraduate Student Research Awards.

\hypertarget{conflicts-of-interestcompeting-interests}{%
\section{Conflicts of interest/Competing interests}\label{conflicts-of-interestcompeting-interests}}

None.

\hypertarget{availability-of-data-materials-and-code}{%
\section{Availability of data, materials, and code}\label{availability-of-data-materials-and-code}}

Can be accessed here: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}.

\hypertarget{authors-contributions-using-credit}{%
\section{Authors' contributions using CRediT}\label{authors-contributions-using-credit}}

Laura St.~Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization. Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing. Andrew Poskus served as a lead for investigation - performed experiment and served in a supporting role for writing- original draft preparation and writing - review and editing. Allison Williams served as a lead for investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Olena Leshchyshen contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Sherry Feldman contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Joshua G.A. Cashaback contributed equally to conceptualization, methodology, writing - original draft preparation, and writing - review and editing. Michael J. Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.

\hypertarget{references}{%
\section{References}\label{references}}

\vspace{2ex}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-anderson2020}{}}%
Anderson, D. I., Magill, R. A., Mayo, A. M., \& Steel, K. A. (2020). Enhancing motor skill acquisition with augmented feedback. In \emph{Skill acquisition in sport: Research, theory and practice} (3rd ed.). {Routledge}.

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-bacelar2022}{}}%
Bacelar, M. F. B., Parma, J. O., Cabral, D., Daou, M., Lohse, K. R., \& Miller, M. W. (2022). Dissociating the contributions of motivational and information processing factors to the self-controlled feedback learning benefit. \emph{Psychology of Sport and Exercise}, \emph{59}, 102119. \url{https://doi.org/10.1016/j.psychsport.2021.102119}

\leavevmode\vadjust pre{\hypertarget{ref-bakeman2005}{}}%
Bakeman, R. (2005). Recommended effect size statistics for repeated measures designs. \emph{Behavior Research Methods}, \emph{37}(3), 379--384. \url{https://doi.org/10.3758/bf03192707}

\leavevmode\vadjust pre{\hypertarget{ref-barros2019}{}}%
Barros, J. A. C., Yantha, Z. D., Carter, M. J., Hussien, J., \& Ste-Marie, D. M. (2019). Examining the impact of error estimation on the effects of self-controlled feedback. \emph{Human Movement Science}, \emph{63}, 182--198. \url{https://doi.org/10.1016/j.humov.2018.12.002}

\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. \url{https://cran.r-project.org/package=tinylabels}

\leavevmode\vadjust pre{\hypertarget{ref-button2013}{}}%
Button, K. S., Ioannidis, J. P. A., Mokrysz, C., Nosek, B. A., Flint, J., Robinson, E. S. J., \& Munafò, M. R. (2013). Power failure: why small sample size undermines the reliability of neuroscience. \emph{Nature Reviews Neuroscience}, \emph{14}(5), 365--376. \url{https://doi.org/10.1038/nrn3475}

\leavevmode\vadjust pre{\hypertarget{ref-carter2014}{}}%
Carter, M. J., Carlsen, A. N., \& Ste-Marie, D. M. (2014). Self-controlled feedback is effective if it is based on the learner's performance: A replication and extension of {Chiviacowsky} and {Wulf} (2005). \emph{Frontiers in Psychology}, \emph{5}, 1--10. \url{https://doi.org/10.3389/fpsyg.2014.01325}

\leavevmode\vadjust pre{\hypertarget{ref-carter2012}{}}%
Carter, M. J., \& Patterson, J. T. (2012). Self-controlled knowledge of results: {Age-related} differences in motor learning, strategies, and error detection. \emph{Human Movement Science}, \emph{31}(6), 1459--1472. \url{https://doi.org/10.1016/j.humov.2012.07.008}

\leavevmode\vadjust pre{\hypertarget{ref-carter2016}{}}%
Carter, M. J., Rathwell, S., \& Ste-Marie, D. M. (2016). Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules. \emph{Journal of Motor Learning and Development}, \emph{4}, 100--115. \url{https://doi.org/10.1123/jmld.2015-0023}

\leavevmode\vadjust pre{\hypertarget{ref-carter2017b}{}}%
Carter, M. J., \& Ste-Marie, D. M. (2017a). Not all choices are created equal: {Task}-relevant choices enhance motor learning compared to task-irrelevant choices. \emph{Psychonomic Bulletin \& Review}, \emph{24}(6), 1879--1888. \url{https://doi.org/10.3758/s13423-017-1250-7}

\leavevmode\vadjust pre{\hypertarget{ref-carter2017a}{}}%
Carter, M. J., \& Ste-Marie, D. M. (2017b). An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules. \emph{Psychological Research}, \emph{81}(2), 399--406. \url{https://doi.org/10.1007/s00426-016-0757-2}

\leavevmode\vadjust pre{\hypertarget{ref-cashaback2019}{}}%
Cashaback, J. G. A., Lao, C. K., Palidis, D. J., Coltman, S. K., McGregor, H. R., \& Gribble, P. L. (2019). The gradient of the reinforcement landscape influences sensorimotor learning. \emph{PLoS Computational Biology}, \emph{15}(3), e1006839. \url{https://doi.org/10.1371/journal.pcbi.1006839}

\leavevmode\vadjust pre{\hypertarget{ref-cashaback2017}{}}%
Cashaback, J. G. A., McGregor, H. R., Mohatarem, A., \& Gribble, P. L. (2017). Dissociating error-based and reinforcement-based loss functions during sensorimotor learning. \emph{PLoS Computational Biology}, \emph{13}(7), e1005623. \url{https://doi.org/10.1371/journal.pcbi.1005623}

\leavevmode\vadjust pre{\hypertarget{ref-cauraugh1993}{}}%
Cauraugh, J. H., Chen, D., \& Radio, S. J. (1993). Effects of traditional and reversed bandwidth knowledge of results on motor learning. \emph{Research Quarterly for Exercise and Sport}, \emph{64}(4), 413--417. \url{https://doi.org/10.1080/02701367.1993.10607594}

\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2005}{}}%
Chiviacowsky, S., \& Wulf, G. (2005). Self-controlled feedback is effective if it is based on the learner's performance. \emph{Research Quarterly for Exercise and Sport}, \emph{76}(1), 42--48. \url{https://doi.org/10.1080/02701367.2005.10599260}

\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2002}{}}%
Chiviacowsky, S., \& Wulf, G. (2002). Self-controlled feedback: {Does} it enhance learning because performers get feedback when they need it? \emph{Research Quarterly for Exercise and Sport}, \emph{73}(4), 408--415. \url{https://doi.org/10.1080/02701367.2002.10609040}

\leavevmode\vadjust pre{\hypertarget{ref-couvillion2020}{}}%
Couvillion, K. F., Bass, A. D., \& Fairbrother, J. T. (2020). Increased cognitive load during acquisition of a continuous task eliminates the learning effects of self-controlled knowledge of results. \emph{Journal of Sports Sciences}, \emph{38}(1), 94--99. \url{https://doi.org/10.1080/02640414.2019.1682901}

\leavevmode\vadjust pre{\hypertarget{ref-faul2009}{}}%
Faul, F., Erdfelder, E., Buchner, A., \& Lang, A.-G. (2009). Statistical power analyses using g*power 3.1: Tests for correlation and regression analyses. \emph{Behavior Research Methods}, \emph{41}(4), 1149--1160. \url{https://doi.org/10.3758/BRM.41.4.1149}

\leavevmode\vadjust pre{\hypertarget{ref-R-ggResidpanel}{}}%
Goode, K., \& Rey, K. (2022). \emph{ggResidpanel: Panels and interactive versions of diagnostic plots using 'ggplot2'}. \url{https://goodekat.github.io/ggResidpanel/}

\leavevmode\vadjust pre{\hypertarget{ref-grand2015}{}}%
Grand, K. F., Bruzi, A. T., Dyke, F. B., Godwin, M. M., Leiker, A. M., Thompson, A. G., Buchanan, T. L., \& Miller, M. W. (2015). Why self-controlled feedback enhances motor learning: {Answers} from electroencephalography and indices of motivation. \emph{Human Movement Science}, \emph{43}, 23--32. \url{https://doi.org/10.1016/j.humov.2015.06.013}

\leavevmode\vadjust pre{\hypertarget{ref-grand2017}{}}%
Grand, K. F., Daou, M., Lohse, K. R., \& Miller, M. W. (2017). Investigating the mechanisms underlying the effects of an incidental choice on motor learning. \emph{Journal of Motor Learning and Development}, \emph{5}(2), 207--226. \url{https://doi.org/10.1123/jmld.2016-0041}

\leavevmode\vadjust pre{\hypertarget{ref-harms2018}{}}%
Harms, C., \& Lakens, D. (2018). Making 'null effects' informative: Statistical techniques and inferential frameworks. \emph{Translational Research}, \emph{3}(Suppl 2), 382--393. \url{https://doi.org/10.18053/jctres.03.2017S2.007}

\leavevmode\vadjust pre{\hypertarget{ref-henry1974}{}}%
Henry, F. M. (1974). Variable and constant performance errors within a group of individuals. \emph{Journal of Motor Behavior}, \emph{6}(3), 149--154. \url{https://doi.org/10.1080/00222895.1974.10734991}

\leavevmode\vadjust pre{\hypertarget{ref-henry1975}{}}%
Henry, F. M. (1975). Absolute error vs {``e''} in target accuracy. \emph{Journal of Motor Behavior}, \emph{7}(3), 227--228. \url{https://doi.org/10.1080/00222895.1975.10735039}

\leavevmode\vadjust pre{\hypertarget{ref-iwatsuki2017}{}}%
Iwatsuki, T., Abdollahipour, R., Psotta, R., Lewthwaite, R., \& Wulf, G. (2017). Autonomy facilitates repeated maximum force productions. \emph{Human Movement Science}, \emph{55}, 264--268. \url{https://doi.org/10.1016/j.humov.2017.08.016}

\leavevmode\vadjust pre{\hypertarget{ref-iwatsuki2018}{}}%
Iwatsuki, T., Navalta, J. W., \& Wulf, G. (2018). Autonomy enhances running efficiency. \emph{Journal of Sports Sciences}, \emph{37}(6), 685--691. \url{https://doi.org/10.1080/02640414.2018.1522939}

\leavevmode\vadjust pre{\hypertarget{ref-izawa2011}{}}%
Izawa, J., \& Shadmehr, R. (2011). Learning from sensory and reward prediction errors during motor adaptation. \emph{PLoS Computational Biology}, \emph{7}(3), e1002012. \url{https://doi.org/10.1371/journal.pcbi.1002012}

\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
Lakens, D. (2017). Equivalence tests: {A} practical primer for t tests, correlations, and meta-analyses. \emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362. \url{https://doi.org/10.1177/1948550617697177}

\leavevmode\vadjust pre{\hypertarget{ref-lakens2013}{}}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and {ANOVAs}. \emph{Frontiers in Psychology}, \emph{4}, 863. \url{https://doi.org/10.3389/fpsyg.2013.00863}

\leavevmode\vadjust pre{\hypertarget{ref-lakens2014}{}}%
Lakens, D., \& Evers, E. R. K. (2014). Sailing from the seas of chaos into the corridor of stability: Practical recommendations to increase the informational value of studies. \emph{Perspectives on Psychological Science}, \emph{9}(3), 278--292.

\leavevmode\vadjust pre{\hypertarget{ref-laughlin2015}{}}%
Laughlin, D. D., Fairbrother, J. T., Wrisberg, C. A., Alami, A., Fisher, L. A., \& Huck, S. W. (2015). Self-control behaviors during the learning of a cascade juggling task. \emph{Human Movement Science}, \emph{41}, 9--19. \url{https://doi.org/10.1016/j.humov.2015.02.002}

\leavevmode\vadjust pre{\hypertarget{ref-lee1990}{}}%
Lee, T. D., \& Carnahan, H. (1990). Bandwidth knowledge of results and motor learning: More than just a relative frequency effect. \emph{The Quarterly Journal of Experimental Psychology}, \emph{42}(4), 777--789. \url{https://doi.org/10.1080/14640749008401249}

\leavevmode\vadjust pre{\hypertarget{ref-leiker2019}{}}%
Leiker, A. M., Pathania, A., Miller, M. W., \& Lohse, K. R. (2019). Exploring the {Neurophysiological} {Effects} of {Self}-{Controlled} {Practice} in {Motor} {Skill} {Learning}. \emph{Journal of Motor Learning and Development}, \emph{7}(1), 13--34. \url{https://doi.org/10.1123/jmld.2017-0051}

\leavevmode\vadjust pre{\hypertarget{ref-lewthwaite2015}{}}%
Lewthwaite, R., Chiviacowsky, S., Drews, R., \& Wulf, G. (2015). Choose to move: {The} motivational impact of autonomy support on motor learning. \emph{Psychonomic Bulletin \& Review}, \emph{22}(5), 1383--1388. \url{https://doi.org/10.3758/s13423-015-0814-7}

\leavevmode\vadjust pre{\hypertarget{ref-lohse2016}{}}%
Lohse, K. R., Buchanan, T., \& Miller, M. W. (2016). Underpowered and Overworked: Problems With Data Analysis in Motor Learning Studies. \emph{Journal of Motor Learning and Development}, \emph{4}(1), 37--58. \url{https://doi.org/10.1123/jmld.2015-0010}

\leavevmode\vadjust pre{\hypertarget{ref-luft2014}{}}%
Luft, C. D. B. (2014). Learning from feedback: The neural mechanisms of feedback processing facilitating better performance. \emph{Behavioural Brain Research}, \emph{261}, 356--368. \url{https://doi.org/10.1016/j.bbr.2013.12.043}

\leavevmode\vadjust pre{\hypertarget{ref-magill1986}{}}%
Magill, R. A., \& Wood, C. A. (1986). Knowledge of results precision as a learning variable in motor skill acquisition. \emph{Research Quarterly for Exercise and Sport}, \emph{57}(2), 170--173. \url{https://doi.org/10.1080/02701367.1986.10762195}

\leavevmode\vadjust pre{\hypertarget{ref-mcauley1989}{}}%
McAuley, E., Duncan, T., \& Tammen, V. V. (1989). Psychometric properties of the {Intrinsic} {Motivation} {Inventory} in a competitive sport setting: A confirmatory factor analysis. \emph{Research Quarterly for Exercise and Sport}, \emph{60}(1), 48--58. \url{https://doi.org/10.1080/02701367.1989.10607413}

\leavevmode\vadjust pre{\hypertarget{ref-mckay2014}{}}%
McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlled learning: {A} meta analysis. \emph{Journal of Sport and Exercise Psychology}, \emph{36}(s1).

\leavevmode\vadjust pre{\hypertarget{ref-mckay2020a}{}}%
McKay, B., \& Ste-Marie, D. M. (2020a). Autonomy support and reduced feedback frequency have trivial effects on learning and performance of a golf putting task. \emph{Human Movement Science}, \emph{71}, 102612. \url{https://doi.org/10.1016/j.humov.2020.102612}

\leavevmode\vadjust pre{\hypertarget{ref-mckay2020b}{}}%
McKay, B., \& Ste-Marie, D. M. (2020b). Autonomy {Support} via {Instructionally} {Irrelevant} {Choice} {Not} {Beneficial} for {Motor} {Performance} or {Learning}. \emph{Research Quarterly for Exercise and Sport}, 1--13. \url{https://doi.org/10.1080/02701367.2020.1795056}

\leavevmode\vadjust pre{\hypertarget{ref-mckay2021}{}}%
McKay, B., Yantha, Z. D., Hussien, J., Carter, M. J., \& Ste-Marie, D. M. (in-press). Meta-analytic findings in the self-controlled motor learning literature: {Underpowered}, biased, and lacking evidential value. \emph{Meta-Psychology}. In-press. \url{https://doi.org/10.31234/osf.io/8d3nb}

\leavevmode\vadjust pre{\hypertarget{ref-munafo2017}{}}%
Munafò, M. R., Nosek, B. A., Bishop, D. V. M., Button, K. S., Chambers, C. D., Percie du Sert, N., Simonsohn, U., Wagenmakers, E.-J., Ware, J. J., \& Ioannidis, J. (2017). A manifesto for reproducible science. \emph{Nature Human Behaviour}, \emph{1}(1), 1--9. \url{https://doi.org/10.1038/s41562-016-0021}

\leavevmode\vadjust pre{\hypertarget{ref-oldfield1971}{}}%
Oldfield, R. C. (1971). The assessment and analysis of handedness: The {Edinburgh} inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}

\leavevmode\vadjust pre{\hypertarget{ref-olejnik2003}{}}%
Olejnik, S., \& Algina, J. (2003). Generalized eta and omega squared statistics: Measures of effect size for some common research designs. \emph{Psychological Methods}, \emph{8}(4), 434--447. \url{https://doi.org/10.1037/1082-989X.8.4.434}

\leavevmode\vadjust pre{\hypertarget{ref-pathania2019}{}}%
Pathania, A., Leiker, A. M., Euler, M., Miller, M. W., \& Lohse, K. R. (2019). Challenge, motivation, and effort: {Neural} and behavioral correlates of self-control of difficulty during practice. \emph{Biological Psychology}, \emph{141}, 52--63. \url{https://doi.org/10.1016/j.biopsycho.2019.01.001}

\leavevmode\vadjust pre{\hypertarget{ref-R-patchwork}{}}%
Pedersen, T. L. (2020). \emph{Patchwork: The composer of plots}. \url{https://patchwork.data-imaginist.com/}

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\vadjust pre{\hypertarget{ref-R-computees}{}}%
Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. \url{https://cran.r-project.org/package=compute.es}

\leavevmode\vadjust pre{\hypertarget{ref-R-rogme}{}}%
Rousselet, G. A., Pernet, C. R., \& Wilcox, R. R. (2017). Beyond differences in means: Robust graphical methods to compare two groups in neuroscience. \emph{European Journal of Neuroscience}, \emph{46}(2), 1738--1748.

\leavevmode\vadjust pre{\hypertarget{ref-rousselet2020}{}}%
Rousselet, G. A., \& Wilcox, R. R. (2020). Reaction times and other skewed distributions: Problems with the mean and the median. \emph{Meta-Psychology}, \emph{4}, 1--39.

\leavevmode\vadjust pre{\hypertarget{ref-ryan1982}{}}%
Ryan, R. M. (1982). Control and information in the intrapersonal sphere: {An} extension of cognitive evaluation theory. \emph{Journal of Personality and Social Psychology}, \emph{43}(3), 450--461. \url{https://doi.org/10.1037/0022-3514.43.3.450}

\leavevmode\vadjust pre{\hypertarget{ref-salmoni1984}{}}%
Salmoni, A. W., Schmidt, R. A., \& Walter, C. B. (1984). Knowledge of results and motor learning: A review and critical reappraisal. \emph{Psychological Bulletin}, \emph{95}(3), 355--386. \url{https://doi.org/10.1037/0033-2909.95.3.355}

\leavevmode\vadjust pre{\hypertarget{ref-sanli2013}{}}%
Sanli, E. A., Patterson, J. T., Bray, S. R., \& Lee, T. D. (2013). Understanding self-controlled motor learning protocols through the self-determination theory. \emph{Frontiers in Psychology}, \emph{3}. \url{https://doi.org/10.3389/fpsyg.2012.00611}

\leavevmode\vadjust pre{\hypertarget{ref-schuirmann1987}{}}%
Schuirmann, D. J. (1987). A comparison of the Two One-Sided Tests Procedure and the Power Approach for assessing the equivalence of average bioavailability. \emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680. \url{https://doi.org/10.1007/BF01068419}

\leavevmode\vadjust pre{\hypertarget{ref-sherwood1996}{}}%
Sherwood, D. E. (1996). The benefits of random variable practice for spatial accuracy and error detection in a rapid aiming task. \emph{Research Quarterly for Exercise and Sport}, \emph{67}(1), 35--43. \url{https://doi.org/10.1080/02701367.1996.10607923}

\leavevmode\vadjust pre{\hypertarget{ref-sherwood2009}{}}%
Sherwood, D. E. (2009). Spatial error detection in rapid unimanual and bimanual aiming movements. \emph{Perceptual and Motor Skills}, \emph{108}(1), 3--14. \url{https://doi.org/10.2466/PMS.108.1.3-14}

\leavevmode\vadjust pre{\hypertarget{ref-sigrist2013}{}}%
Sigrist, R., Rauter, G., Riener, R., \& Wolf, P. (2013). Augmented visual, auditory, haptic, and multimodal feedback in motor learning: A review. \emph{Psychonomic Bulletin \& Review}, \emph{20}(1), 21--53. \url{https://doi.org/10.3758/s13423-012-0333-8}

\leavevmode\vadjust pre{\hypertarget{ref-simmons2012}{}}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 Word Solution}. \url{https://doi.org/10.2139/ssrn.2160588}

\leavevmode\vadjust pre{\hypertarget{ref-simmons2011}{}}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2011). False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant. \emph{Psychological Science}, \emph{22}(11), 1359--1366. \url{https://doi.org/10.1177/0956797611417632}

\leavevmode\vadjust pre{\hypertarget{ref-R-afex}{}}%
Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{Afex: Analysis of factorial experiments}. \url{https://CRAN.R-project.org/package=afex}

\leavevmode\vadjust pre{\hypertarget{ref-stgermain2022}{}}%
St Germain, L., Williams, A., Balbaa, N., Poskus, A., Leshchyshen, O., Lohse, K. R., \& Carter, M. J. (in-press). Increased perceptions of autonomy through choice fail to enhance motor skill retention. \emph{Journal of Experimental Psychology: Human Perception and Performance}. In-press. \url{https://doi.org/10.1037/xhp0000992}

\leavevmode\vadjust pre{\hypertarget{ref-stemarie2019}{}}%
Ste-Marie, D. M., Carter, M. J., \& Yantha, Z. D. (2020). Self-controlled learning: {Current} findings, theoretical perspectives, and future directions. In \emph{Skill acquisition in sport: Research, theory and practice} (3rd ed.). {Routledge}.

\leavevmode\vadjust pre{\hypertarget{ref-R-metafor}{}}%
Viechtbauer, W. (2010). Conducting meta-analyses in {R} with the {metafor} package. \emph{Journal of Statistical Software}, \emph{36}(3), 1--48. \url{https://doi.org/10.18637/jss.v036.i03}

\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L. D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T. L., Miller, E., Bache, S. M., Müller, K., Ooms, J., Robinson, D., Seidel, D. P., Spinu, V., \ldots{} Yutani, H. (2019). Welcome to the {tidyverse}. \emph{Journal of Open Source Software}, \emph{4}(43), 1686. \url{https://doi.org/10.21105/joss.01686}

\leavevmode\vadjust pre{\hypertarget{ref-wilcox2021}{}}%
Wilcox, R. R. (2021). \emph{Introduction to robust estimation and hypothesis testing} (5th ed.). Academic press.

\leavevmode\vadjust pre{\hypertarget{ref-woodard2020}{}}%
Woodard, K. F., \& Fairbrother, J. T. (2020). Cognitive loading during and after continuous task execution alters the effects of self-controlled knowledge of results. \emph{Frontiers in Psychology}, \emph{11}. \url{https://doi.org/10.3389/fpsyg.2020.01046}

\leavevmode\vadjust pre{\hypertarget{ref-wulf2014}{}}%
Wulf, G., Freitas, H. E., \& Tandy, R. D. (2014). Choosing to exercise more: {Small} choices increase exercise engagement. \emph{Psychology of Sport and Exercise}, \emph{15}(3), 268--271. \url{https://doi.org/10.1016/j.psychsport.2014.01.007}

\leavevmode\vadjust pre{\hypertarget{ref-wulf2018}{}}%
Wulf, G., Iwatsuki, T., Machin, B., Kellogg, J., Copeland, C., \& Lewthwaite, R. (2018). Lassoing skill through learner choice. \emph{Journal of Motor Behavior}, \emph{50}(3), 285--292. \url{https://doi.org/10.1080/00222895.2017.1341378}

\leavevmode\vadjust pre{\hypertarget{ref-wulf2016}{}}%
Wulf, G., \& Lewthwaite, R. (2016). Optimizing performance through intrinsic motivation and attention for learning: {The} {OPTIMAL} theory of motor learning. \emph{Psychonomic Bulletin \& Review}, \emph{23}(5), 1382--1414. \url{https://doi.org/10.3758/s13423-015-0999-9}

\leavevmode\vadjust pre{\hypertarget{ref-yantha2021}{}}%
Yantha, Z. D., McKay, B., \& Ste-Marie, D. M. (in-press). The recommendation for learners to be provided with control over their feedback schedule is questioned in a self-controlled learning paradigm. \emph{Journal of Sports Sciences}, 1--14. https://doi.org/\url{https://doi.org/10.1080/02640414.2021.2015945}

\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}

\end{CSLReferences}

\end{document}

### 2022-05-05 scripts/main_analyses.R

@@ -1,0 +1,478 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Manuscript - Analyses
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: March 30 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+# SCRIPT SETUP ----
+#
+# Required files and tibbles
+source("scripts/main_wrangle.R")
+
+# DATA SETUP ----
+#
+# Create tibbles to work with
+#
+# PRETEST, RETENTION, TRANSFER
+#
+# EXPERIMENT 1
+#
+# Spatial goal
+#
+# Omnibus test
+expt1_prt_deg_lm <- afex::aov_ez(
+  "id", "p_mean_e_deg", expt1_performance_prt_p,
+  between = c("choice_id", "fb_id"),
+  within = "block_id"
+)
+expt1_prt_deg_lm
+
+# Post hoc for main effect of Test
+expt1_prt_deg_me_test <- emmeans::emmeans(
+  expt1_prt_deg_lm, ~block_id
+)
+pairs(expt1_prt_deg_me_test, adjust = "holm")
+
+# Timing goal
+#
+# Omnibus test
+expt1_prt_ms_lm <- afex::aov_ez(
+  "id", "p_mean_e_ms", expt1_performance_prt_p,
+  between = c("choice_id", "fb_id"),
+  within = "block_id"
+)
+expt1_prt_ms_lm
+
+# Post hoc for main effect of Test
+expt1_prt_ms_me_test <- emmeans::emmeans(
+  expt1_prt_ms_lm, ~block_id
+)
+pairs(expt1_prt_ms_me_test, adjust = "holm")
+
+
+# EXPERIMENT 2
+#
+# Spatial goal
+#
+# Omnibus test
+expt2_prt_deg_lm <- afex::aov_ez(
+  "id", "p_mean_e_deg", expt2_performance_prt_p,
+  between = "group_id",
+  within = "block_id"
+)
+expt2_prt_deg_lm
+
+# Timing goal
[…]

### 2022-05-05 docs/preprint/manuscript.Rmd
init

---
title             : "Exercising choice over feedback schedules during practice is not advantageous for motor learning"
shorttitle        : "Choice and feedback characteristics"

# note: |
#   \vspace{5ex}
#   \textcolor{orange}{\textbf{\emph{NOT PEER-REVIEWED}}}

authornote: |
  \vspace{-0.5cm}
  \noindent \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183} \newline
  \noindent \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
  \noindent \addORCIDlink{Joshua G.A. Cashaback}{0000-0002-8642-6648} \newline
  \noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
  \noindent Data and code: https://github.com/cartermaclab/expt_sc-feedback-characteristics \vspace{2ex} \newline
  \noindent \textbf{Corresponding authors:} Michael J. Carter (michaelcarter@mcmaster.ca) and Laura St. Germain (stgerml@mcmaster.ca).

abstract: |
  The idea that there is a self-controlled learning advantage, where individuals demonstrate improved motor learning after exercising choice over an aspect of practice compared to no-choice groups, has different causal explanations according to the OPTIMAL theory or an information-processing perspective. Within OPTIMAL theory, giving learners choice is considered an autonomy-supportive manipulation that enhances expectations for success and intrinsic motivation. In the information-processing view, choice allows learners to engage in performance-dependent strategies that reduce uncertainty about task outcomes. To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a rapid reaching task with spatial and timing goals. Across both experiments (N = 228 participants), we did not find evidence to support a self-controlled learning advantage. Exercising choice during practice did not increase perceptions of autonomy, competence, or intrinsic motivation, nor did it lead to more accurate error estimation skills. Both error and graded feedback facilitated skill acquisition and learning, whereas no improvements from pre-test performance were found with binary feedback. Finally, the impact of graded and binary feedback on perceived competence highlights a potential dissociation of motivational and informational roles of feedback. Although our results regarding self-controlled practice conditions are difficult to reconcile with either the OPTIMAL theory or the information-processing perspective, they are consistent with a growing body of evidence that strongly suggests self-controlled conditions are not an effective approach to enhance motor performance and learning.

keywords          : "Self-controlled, Knowledge of results, OPTIMAL theory, Retention"
#wordcount         : "2978 for Introduction, Results, and Discussion"

bibliography      : ["../references.bib", "../r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "doc, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
 # - \pagewiselinenumbers
  - \raggedbottom

  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
---

```{r setup, include = FALSE}
library(papaja)
library(kableExtra)
library(tidyverse)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

The underlying source of errors in skilled actions are often ambiguous and difficult to assign as the learner must rely on noisy and delayed sensory information. Feedback from an external source, such as a coach or computer display, can facilitate or augment this process [@sigrist2013]. Knowledge of results feedback [@salmoni1984] can provide varying amounts of information to learners depending on its characteristics. Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., "too far"), and binary feedback indicates only success or failure information (e.g., "miss") [@luft2014]. When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning. These self-controlled feedback schedules have typically enhanced motor skill learning compared to yoked feedback schedules, wherein learners experience the feedback schedule created by a self-controlled counterpart, but without any choice [see @sanli2013; @stemarie2019 for reviews].

Why self-controlled learning advantages emerge has garnered considerable attention in the motor skill learning literature. Within their OPTIMAL (Optimizing performance through intrinsic motivation and attentional learning) theory of motor learning, @wulf2016 have argued that providing participants the opportunity to exercise choice, as in a self-controlled group, creates a virtuous cycle. Specifically, choice leads to increased (perceived) autonomy, leading to enhanced expectancies (e.g., perceived competence) and increased (intrinsic) motivation. These motivational influences lead to improved motor performance, creating a positive feedback loop that ultimately enhances motor learning compared to those not given the same choice opportunities. Support for this view has been drawn from experimental work where participants exercise choice over task-irrelevant or incidental choices. Exercising choice over the color of golf balls to putt [@lewthwaite2015 Experiment 1] or the mat underneath a target [@wulf2018 Experiment 1], which picture to hang in a lab [@lewthwaite2015 Experiment 2], hand order in a maximal force production task [@iwatsuki2017], which photos to look at while running [@iwatsuki2018], and the order of exercises to perform [@wulf2014] have been suggested to improve motor performance or learning. Other research, however, have failed to replicate this benefit of task-irrelevant or incidental choices on motor performance or learning [@carter2017b; @mckay2020a; @grand2017; @mckay2020b].

Rather than a motivational account, others have forwarded an information-processing explanation. From this perspective, exercising choice allows learners to tailor practice to their individual needs [@chiviacowsky2002; @chiviacowsky2005] by engaging in performance-contingent strategies [@carter2014; @carter2016; @laughlin2015; @pathania2019] to reduce uncertainty about movement outcomes [@barros2019; @carter2014; @carter2017a; @carter2017b; @grand2015]. Evidence for this view has come from experiments that showed the timing of the feedback decision relative to task performance matters [@carter2014; @chiviacowsky2005], that task-relevant choices are more effective than task-irrelevant choices [@carter2017b; cf. @wulf2018 Experiment 2], that interfering with information-processing activities during [@couvillion2020; @woodard2020] or after [@carter2017a; @woodard2020] task performance eliminates self-controlled learning benefits, and that the ability to accurately estimate one’s performance is enhanced in choice compared to yoked groups [@carter2012; @carter2014]. Thus, further investigation is required to test predictions from these two explanations to better understand why exercising choice during practice confers an advantage for motor skill learning.

To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we provided participants in choice and yoked (i.e., no-choice) groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) during the acquisition of a rapid aiming task. Motor learning was assessed using delayed (~24 hours) retention and transfer tests. If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule *would not matter* for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups. Thus, we predicted all choice groups would demonstrate superior performance and learning compared to the yoked groups. Alternatively, if the information-processing account is correct, we hypothesized that the characteristics of one's feedback schedule *would matter* for the self-controlled learning advantage as feedback with greater informational value would be more effective for reducing uncertainties about movement outcomes. Thus, we predicted that choice over an error feedback schedule would be the most effective pairing for performance and learning. We also included self-report measures of perceptions of autonomy, competence, and intrinsic motivation, and assessments of error estimation abilities to respectively test auxiliary assumptions of the OPTIMAL theory and information-processing explanations.

# Methods

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study [@simmons2012]. All data and `R` scripts can be accessed here: https://github.com/cartermaclab/expt_sc-feedback-characteristics.

## Participants

### Experiment 1

One hundred and fifty-two right-handed [@oldfield1971], healthy adults participated in Experiment 1 ($M_{age}$ = 20.64 years, $SD_{age}$ = 2.45, 88 females). Sample size was determined from an *a-priori* power analysis using the *ANOVA: fixed effects, main effects and interactions* option in G*Power [@faul2009] with the following parameters: $\alpha$ = 0.05, $\beta$ = .20, $f$ = 0.23, numerator = 1, and groups = 2. This revealed a required sample of 151 participants. Our chosen effect size was based on a meta-analytic estimate ($f$ = .32) by @mckay2014; however, we used a more conservative estimate given the uncertainty of how choice would interact with our feedback characteristic manipulation. Participants were compensated $15 CAD or with course-credit for their time. All participants gave written informed consent and the experiment was approved by McMaster University’s Research Ethics Board.

### Experiment 2

A new sample of 76 right-handed [@oldfield1971], healthy adults participated in Experiment 2 ($M_{age}$ = 20.18 years, $SD_{age}$ = 3.18, 47 females). Sample size was selected so group size matched that used in Experiment 1. Participants were compensated $15 CAD or with course-credit for their time. All participants gave written informed consent and the experiment was approved by McMaster University’s Research Ethics Board.

## Task

In Experiments 1 and 2, participants sat in a chair facing a monitor (1920x1080 resolution) with their left arm in a custom manipulandum that restricted movement to the horizontal plane. Their elbow was bent at approximately 90° and they grasped a vertical handle with their left hand. Handle position was adjusted as needed to ensure the central axis of rotation was about the elbow. The task required a rapid "out-and-back" movement such that the reversal happened at $40^\circ$ (in pre-test, acquisition, and retention) or $60^\circ$ (in transfer). The starting point for all trials was $0^\circ$. Participants were instructed to make a smooth movement to the reversal and back without hesitating when reversing their movement. The movement time goal to the reversal was always 225 ms. The task and instructions were similar to those used by Sherwood [-@sherwood1996; -@sherwood2009]. Vision of the manipulandum and limb were occluded during all phases of the experiment. Angular displacement for the elbow was collected via a potentiometer attached to the axis of rotation of the custom manipulandum. Potentiometer data were digitally sampled at 1000 Hz (National Instruments PCIe-6321) using a custom LabVIEW program and stored for offline analysis.

## Procedure

### Experiment 1

The first 76 participants were randomly assigned to either the Choice+Error-Feedback group ($n$ = 38; $M_{age}$ = 20.24 years, $SD_{age}$ = 2.37, 22 females) or the Choice+Graded-Feedback group ($n$ = 38; $M_{age}$ = 20.76 years, $SD_{age}$ = 3.02, 26 females). This is typical in the self-controlled learning literature as the self-controlled participants’ self-selected feedback schedules are required for providing feedback to the participants in the yoked (i.e., control) groups. The remaining 76 participants were randomly assigned to either the Yoked+Error-Feedback group ($n$ = 38; $M_{age}$ = 20.53 years, $SD_{age}$ = 2.13, 23 females) or the Yoked+Graded-Feedback group ($n$ = 38; $M_{age}$ = 21.03 years, $SD_{age}$ = 2.32, 22 females).

Data collection consisted of two sessions separated by approximately 24 hours.[^1] Session one included a pre-test (12 trials) and an acquisition phase (72 trials). Session two included the delayed retention (12 trials) and transfer (12 trials) tests. No feedback about motor performance was provided in pre-test, retention, or transfer. Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals. Additionally, half of the participants in each group were randomly selected to estimate their performance on the spatial and timing goals after each trial in the pre-test. Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested [e.g., @chiviacowsky2005] to be adopted spontaneously by participants controlling their feedback schedule. However, asking participants to estimate their performance during pre-test is necessary to be able to assess how this skill develops as a function of one's practice condition.

[^1]: Six participants (three Choice+Error-Feedback and three Choice+Graded-Feedback) had their second session completed approximately 48 hours later because a snowstorm closed the University.

Participants were reminded of the instructions about the task and its associated goals at the start of the acquisition phase. Group specific instructions regarding feedback were also provided. Participants in the Choice+Error-Feedback group and the Choice+Graded-Feedback group were told they could choose their feedback schedule, with the restriction that they must select feedback on 24 of the 72 acquisition trials. They were informed that if the number of remaining feedback requests equaled the number of remaining acquisition trials, these trials would default to feedback trials. This feedback restriction was implemented to ensure the relative frequency of feedback was equated across all groups. Similar restrictions have been used in past research involving multiple choice groups [e.g., @chiviacowsky2005]. Participants in the Yoked+Error-Feedback group and the Yoked+Graded-Feedback group were told they may or may not receive feedback following a trial based on a predetermined schedule. Thus, participants in these groups were not aware that their feedback schedule was actually created by a participant in a corresponding choice group. While this yoking procedure ensures that the total number of feedback trials and their relative placement during acquisition are identical, the content of the feedback reflected each participant's own performance. Error feedback for the spatial and timing goals was provided as the difference between the participant's actual performance and the task goal (i.e., constant error). Graded feedback for the spatial goal was provided as "too short" if performance was < 40 degrees (or 60 degrees in transfer), "hit" if exactly 40 degrees, and "too far" if > 40 degrees. For the timing goal, graded feedback was provided as "too fast" when performance was < 225 ms, "hit" if exactly 225 ms, and "too slow" if > 225 ms. All participants were shown a sample feedback display that corresponded to their experimental group and were asked to interpret it aloud for the researcher to verify understanding.

```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "45%"}
knitr::include_graphics("../../figs/fig1.pdf")
```

(ref:fig1-caption) \small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase. Trials began by informing participants the trial number (500 ms) they were on in acquisition. Shortly after, the text "Get Ready!" appeared on the screen and 800 ms later a visual go-signal was presented in the form of a green circle in the center of the screen. Participants began their movement when ready after seeing the visual go-signal as we were not interested in reaction time. While participants completed their rapid out-and-back movement, the computer screen was blank. Upon returning to the starting position, a red circle appeared in the center of the screen. A 2000 ms feedback delay interval was used and this interval was followed by the feedback prompt. The feedback prompt also displayed an updated counter representing the number of feedback trials they had left. If the number of remaining feedback trials matched the number of acquisition trials left, these trials automatically defaulted to feedback trials. On trials where feedback was not requested, a blank screen **(A)** was shown for 3000 ms. When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group. The error feedback group **(B)** saw their constant error, the graded feedback group **(C)** saw either "too far" or "too short" for the spatial goal and "too fast" or "too slow" for the timing goal, and the binary feedback group **(D)** saw either "hit" or "miss" for the task goals. The sequence of events was the same for the yoked groups with the exception they did not see a feedback prompt. The sequence of events was similar in pre-test, retention, and transfer except all trials were no-feedback trials.

A typical acquisition trial (see Figure \@ref(fig:fig1)) began with the current trial number displayed (500 ms), followed by a visual "Get Ready!" and a visual go-signal (800 ms apart). Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task. The computer screen was blank while participants made their movement. When participants returned to the starting position, a red circle was displayed on the monitor. Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups. If feedback was not selected, a blank screen was displayed for 3000 ms. If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.

Before the retention and transfer tests, participants were reminded about the task and its associated goals. All participants were asked to estimate their performance after each trial in retention and transfer. After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy. The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory [@mcauley1989; @ryan1982] and the perceived autonomy questions were used in earlier work [@barros2019; @carter2017b]. Cronbach's alpha values for each questionnaire at each time point are reported in Table \@ref(tab:table1).

### Experiment 2

Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group ($n$ = 38; $M_{age}$ = 22.37 years, $SD_{age}$ = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group ($n$ = 38; $M_{age}$ = 18.00 years, $SD_{age}$ = 0.93, 28 females). Binary feedback for the spatial goal was provided as "hit" if performance was exactly 40 degrees (or 60 degrees in transfer) and as "miss" for everything else. For the timing goal, binary feedback was provided as "hit" when performance was exactly 225 ms and as "miss" for everything else. Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.

```{r table1, echo = FALSE, results = "asis"}
table1 <- tibble::tibble(
    c1 = c("Perceived autonomy",
           "Perceived competence",
           "Intrinsic motivation",
           "Perceived autonomy",
           "Perceived competence",
           "Intrinsic motivation"),
    c2 = c("0.68",
           "0.86",
           "0.86",
           "0.39",
           "0.92",
           "0.91"),
    c3 = c("0.81",
           "0.93",
           "0.90",
           "0.73",
           "0.88",
           "0.91"),
    c4 = c("0.80",
           "0.95",
           "0.92",
           "0.79",
           "0.91",
           "0.93"),
    c5 = c("0.83",
           "0.94",
           "0.93",
           "0.85",
           "0.91",
           "0.94"),
)
table1 %>%
  kbl(booktabs = TRUE,
      escape = TRUE,
      linesep = "\\addlinespace",
      caption = "Cronbach's alpha for each questionnaire at each timepoint.",
      col.names = c("Questionnaire",
                  "After pre-test",
                  "After block 1",
                  "After block 6",
                  "Before retention")
  ) %>%
  kable_styling(position = "left",
                font_size = 11) %>%
  column_spec(1, width = "12em") %>%
  column_spec(2, width = "6em") %>%
  column_spec(3, width = "6em") %>%
  column_spec(4, width = "6em") %>%
  column_spec(5, width = "7em") %>%
  pack_rows("Experiment 1", 1, 3) %>%
  pack_rows("Experiment 2", 4, 6) %>%
  footnote(general = "Block 1 and 6 are from the acquisition phase.",
           general_title = "Note.",
           title_format = "italic",
           footnote_as_chunk = TRUE
           )
```

## Data Analysis

Movement trajectories for all trials were visually inspected by a researcher and trials with errors (e.g., technical issues, moving before the "go" signal) were removed. A total of 4.03% (662/16146) and 3.73% (306/8208) of trials for Experiments 1 and 2 were removed, respectively. Trials were aggregated into blocks of 12 trials, resulting in one block of trials for pre-test, retention, and transfer, and six blocks of trials for acquisition. Our primary performance outcome variable was total error (E) [@henry1974; @henry1975] and was computed using the equation:
\begin{equation}
E = \sqrt{\sum{(x_{i} - T)^2 / n}}
\end{equation}
where $x_{i}$ is the score on the $i$th trial, $T$ is the target goal, and $n$ is the number of trials in a block.

To test for performance differences in pre-test, retention, and transfer, total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (*Experiment 1:* 2 Choice x 2 Feedback x 3 Test; *Experiment 2:* 2 Choice x 3 Test). To test for performance differences during acquisition, total error for the spatial and timing goals during acquisition were analyzed in separate mixed ANOVAs (*Experiment 1:* 2 Choice x 2 Feedback x 6 Block; *Experiment 2:* 2 Choice x 6 Block). Our primary psychological outcome variables were intrinsic motivation (i.e., interest/enjoyment), perceived competence, and perceived autonomy. The mean score of the responses for these constructs at each time point was calculated for each participant and analyzed in separate mixed ANOVAs (*Experiment 1:* 2 Choice x 2 Feedback x 4 Time; *Experiment 2:* 2 Choice x 4 Time). Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50% of the participants in each group in Experiments 1 and 2), retention, and transfer (see **Supplementary A**).

Alpha was set to .05 for all statistical analyses. Corrected degrees of freedom using the Greenhouse-Geisser technique are always reported for repeated measures with more than two levels. Generalized eta squared $(\eta_{G}^2)$ is provided as an effect size statistic [@bakeman2005; @lakens2013; @olejnik2003] for all omnibus tests. Post hoc comparisons were Holm-Bonferroni corrected to control for multiple comparisons. Statistical tests were conducted using `r cite_r("../r-references.bib")` were used in this project.

# Results

Model diagnostics of total error for the spatial and timing goals revealed skewed distributions. We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions [@rousselet2020; @wilcox2021]. The results of these analyses (see **Supplementary B**) were consistent with those of the mixed ANOVAs, which we report below.

## Pre-test, retention, and transfer

### Experiment 1

Spatial (Fig. \@ref(fig:fig2)A) and timing (Fig. \@ref(fig:fig2)B) error decreased from the pre-test to the retention and transfer tests. There was a main effect of Test for spatial error, $F(1.33,196.52) = 40.20$, $p < .001$, $\eta_{G}^2 = .138$, where performance was less errorful in retention and transfer than pre-test ($p$'s < .001) and performance in retention was better than transfer ($p$ < .001). A main effect of Test was also found for timing error, $F(1.08,160.23) = 81.21$, $p < .001$, $\eta_{G}^2 = .245$, with pre-test performance more errorful than both retention and transfer ($p$'s < .001), and retention was less errorful than transfer ($p$ < .001).

### Experiment 2

Spatial (Fig. \@ref(fig:fig3)A) and timing (Fig. \@ref(fig:fig3)B) error did not change considerably from the pre-test to the retention and transfer tests. There were no significant main effects or interactions for either task goals.

\vspace{4ex}

```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center"}
knitr::include_graphics("../../figs/fig2.pdf")
```

(ref:fig2-caption) \small \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses. Error bars denote 95% bootstrapped confidence intervals. **(A)** Spatial total error (degrees) and **(B)** timing total error (ms) averaged across blocks and participants within each group. Dotted vertical lines denote the different experimental phases. Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2. Self-reported scores for perceived autonomy **(C)**, perceived competence **(D)**, and intrinsic motivation **(E)** after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2. Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree). Dots represent individual data points.

<!-- \vspace{2ex} -->

```{r fig3, echo = FALSE, fig.cap = "(ref:fig3-caption)", fig.align = "center"}
knitr::include_graphics("../../figs/fig3.pdf")
```
(ref:fig3-caption) \small \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares. Error bars denote 95% bootstrapped confidence intervals. **(A)** Spatial total error (degrees) and **(B)** timing total error (ms) averaged across blocks and participants within each group. Dotted vertical lines denote the different experimental phases. Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2. Self-reported scores for perceived autonomy **(C)**, perceived competence **(D)**, and intrinsic motivation **(E)** after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2. Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree). Dots represent individual data points.

\newpage

## Acquisition

### Experiment 1

All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig. \@ref(fig:fig2)A). This was supported by a significant main effect of Block, $F(2.41,357.13) = 60.18$, $p < .001$, $\eta_{G}^2 = .130$, where block 1 was less accurate than all other blocks ($p$'s $< .001$), block 2 was less accurate than all subsequent blocks ($p$'s $\leq .021$), and blocks 3 and 4 were more errorful than block 6 ($p$'s $\leq .015$). Timing error also decreased during the acquisition period (Fig. \@ref(fig:fig2)B). The significant main effect of Block, $F(1.75,259.59) = 55.44$, $p < .001$, $\eta_{G}^2 = .138$, was superseded by a significant Feedback x Block interaction, $F(1.75, 259.59) = 3.56$, $p = .035$, $\eta_{G}^2 = .010$. Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks ($p$'s $< .001$), but performance plateaued from block 2 onward in acquisition ($p$'s $\geq .257$). Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks ($p$'s $< .001$); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 ($p$'s $\leq .028$).

### Experiment 2

Spatial (Fig. \@ref(fig:fig3)A) and timing (Fig. \@ref(fig:fig3)B) error remained relatively flat from block 1 to block 6 in the acquisition period. None of the main effects or interactions for either task goals were significant.

## Psychological variables

### Experiment 1

Perceptions of autonomy (Fig. \@ref(fig:fig2)C) showed a slight decrease across time points, supported by a main effect of Time, $F(2.25,332.95) = 3.69$, $p < .022$, $\eta_{G}^2 = .003$. Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test ($p = .031$). Self-ratings for perceived competence (Fig. \@ref(fig:fig2)D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic. Main effects of Time, $F(1.92, 283.47) = 3.43$, $p = .036$, $\eta_{G}^2 = .006$, and Feedback, $F(1,148) = 47.36$, $p < .001$, $\eta_{G}^2 = .188$, were superseded by a Feedback x Time interaction, $F(1.92, 283.47) = 28.04$, $p < .001$, $\eta_{G}^2 = .050$. Perceived competence scores were not significantly different after the pre-test ($p = .232$); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points ($p$'s $< .001$). Self-reported scores for intrinsic motivation (Fig. \@ref(fig:fig2)E) generally decreased after block 1, which was supported by a main effect of Time, $F(2.40,355.90) = 14.69$, $p < .001$, $\eta_{G}^2 = .012$. Intrinsic motivation scores initially increased following the pre-test to after block 1 ($p = .003$); however, scores after block 1 of acquisition were greater than those reported at the end of acquisition (i.e., block 6) and before retention ($p$'s $< .001$). Self-reported ratings were also lower before retention compared to after the pre-test ($p = .043$).

### Experiment 2

Self-reported scores for perceived autonomy (Fig. \@ref(fig:fig3)C) were similar across all time points. There were no main effects or interactions. Perceptions of competence (Fig. \@ref(fig:fig3)D) showed a considerable decrease after the pre-test, $F(1.85,136.91) = 106.10$, $p < .001$, $\eta_{g}^2 = .298$, where scores were significantly greater after the pre-test compared to all other time points ($p$'s $< .001$), and were higher after block 1 of acquisition than before retention ($p = .004$). Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, $F(2.37,175.55) = 15.31$, $p < .001$, $\eta_{G}^2 = .018$. Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention ($p$'s $< .001$), and higher after block 1 than after block 6 and before retention ($p$'s $< .026$).

## Equivalence analysis

Our main comparison of interest was between choice and no-choice (i.e., yoked groups). To evaluate the self-controlled learning effect observed across Experiments 1 and 2, Hedges' *g* for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies. Next, a random effects meta-analysis was conducted on the retention test data[^2] to generate a summary point estimate and 90% confidence intervals (CI). This resulted in an overall estimated effect of $g = .05$ (favoring self-controlled) and $90\% \,CI \,[-.12,.23]$.

[^2]: We report an estimate for retention tests to facilitate comparison to a recent meta-analysis [@mckay2021] that produced estimated effects of self-controlled learning at retention specifically.

Equivalence tests can be conducted to evaluate whether the observed differences are significantly smaller than a pre-determined smallest effect size of interest [see @harms2018 for a discussion]. Typically, a two one-sided tests procedure is used to compare the observed effect to upper and lower equivalence bounds, and if the effect is significantly smaller than both bounds then the hypothesis that the effect is large enough to be of interest is rejected [@lakens2017;@schuirmann1987]. However, we did not pre-specify a smallest effect of interest, so instead we report the 90% confidence intervals (see above). All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not. Therefore, the present experiments can be considered inconsistent with all effects larger than $g = \pm.23$.

# Discussion

The purpose of the present experiments was to test between motivational and information-processing accounts of the putative self-controlled learning advantage [see @stemarie2019 for a review]. According to the OPTIMAL theory [@wulf2016], self-controlled practice or choice conditions are advantageous because the provision of choice increases perceptions of autonomy and competence, which increase intrinsic motivation and ultimately both motor performance and learning. Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals [@carter2014; @carter2017a; @grand2015]. In contrast to these predictions, we did not find evidence that providing learners with choice over their feedback schedule was beneficial for motor learning, despite collecting a much larger sample (*N* = 228 across both Experiments) than those commonly used in self-controlled learning experiments [median sample size *N* = 36 in a meta-analysis by @mckay2021] and motor learning experiments in general [median *n*/group = 11 in a review by @lohse2016]. Further, exercising choice in practice did not enhance perceptions of autonomy, competence, or intrinsic motivation, and also did not result in more accurate performance estimations in delayed tests of motor learning. Overall, we found no support for the OPTIMAL theory or information-processing perspective. Our results challenge the prevailing view that the self-controlled learning benefit is a robust effect.

The failed replication of a self-controlled learning advantage was surprising given the dominant view for the past 25 years has been that it is a robust effect and one that should be recommended to coaches and practitioners [@sanli2013; @stemarie2019; @wulf2016]. Our findings are, however, consistent with a growing list of relatively large--often pre-registered--experiments that have not found self-controlled learning benefits [@bacelar2022; @grand2017; @leiker2019; @mckay2020a; @mckay2020b; @stgermain2022; @yantha2021]. One possible explanation for this discrepancy between earlier and more recent experiments may be that the self-controlled learning advantage was the result of underpowered designs, which has been highlighted as a problem in motor learning research [see @lohse2016 for a discussion]. When underpowered designs find significant results, they are prone to be false positives with inflated estimates of effects [@button2013; @lakens2014], which can be further exaggerated with questionable research practices such as *p*-hacking and selective reporting [e.g., @munafo2017; @simmons2011]. Thus, a self-controlled learning advantage may not actually exist. Alternatively, if one does exist then it seems likely it is a much smaller effect than originally estimated and requires considerably larger samples to reliability detect than those commonly used in motor learning research. Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results [@mckay2021]. We estimated the overall effect of self-controlled practice in retention to be significantly smaller than any effect larger than $g = .23$. This is consistent with the estimates from @mckay2021 after accounting for publication bias ($g =$ -.11 to .26), which suggested either no effect or a small effect in an unknown direction. Taken together, we argue that it may be time for the self-controlled learning advantage to be considered a non-replicable effect in motor learning.

Given our current replication failure with those in recent years [@bacelar2022; @grand2017; @leiker2019; @mckay2020a; @mckay2020b; @stgermain2022; @yantha2021] and the conclusions from @mckay2021, motivational (i.e., OPTIMAL theory) versus information-processing explanations seem moot. Nevertheless, the present results are incompatible with both perspectives. Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory. Similarly, self-controlled feedback schedules did not enhance error estimation skills (see **Supplementary A**) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective. Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose. When feedback provided information about the direction of an error or when it contained both direction and magnitude of an error, participants were able to improve at the task throughout acquisition and retain these improvements in skill relative to pre-test. However, when feedback was binary and direction and magnitude of an error was absent, there was no improvement in skill from baseline levels. This is in contrast with past research that has shown people can learn motor tasks with binary feedback [e.g., @cashaback2017; @cashaback2019; @izawa2011]. One possible explanation for this discrepancy may be the amount of practice trials [@magill1986]. Practicing with binary feedback may inherently require a longer training period for learning to occur compared to graded and error feedback, which both have greater precision. Additionally, we used a strict criteria with binary feedback where any outcome other than zero error was considered a miss. Thus, binary feedback may be more effective when paired with a tolerance zone such as that used in the bandwidth technique [see @anderson2020 for a review; @cauraugh1993; @lee1990].

Although unexpected, the influence of feedback characteristics on perceptions of competence may hint to a dissociation between informational and motivational impacts of knowledge-of-results feedback. In Experiment 1, participants who received graded feedback reported significantly lower perceptions of competence than participants who received error feedback. Yet, despite these lower expectations for success, the graded feedback groups did not demonstrate degraded performance or learning compared to the error feedback group. Participants in Experiment 2 who received binary feedback reported the lowest perceptions of competence and were also the only participants who did not show improvements in task performance from pre-test. Thus, future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.

In two experiments we failed to observe the predicted benefits of self-controlled feedback on motor learning. Similarly, we failed to find the predicted motivational and informational consequences of choice in either experiment, challenging both the OPTIMAL theory and information-processing explanation of the so-called self-controlled learning advantage. Although the present experiments were not pre-registered, the analysis plan was determined prior to viewing the data. In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see **Supplementary B**). The sensitivity analyses supported the conclusions of the primary analyses and are consistent with research that has followed pre-registered analysis plans [@bacelar2022; @grand2017; @leiker2019; @mckay2020a; @mckay2020b; @stgermain2022; @yantha2021]. Lastly, our results and conclusions are in line with a recent meta-analysis [@mckay2021] that suggests the apparent benefits of self-controlled practice are due to selection bias rather than true effects.

\vspace{2.5ex}

# Funding

This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University. LSG was supported by an NSERC Postgraduate Scholarship. JGAC was supported by an NIH U45GM104941 grant. AW and AP were supported by NSERC Undergraduate Student Research Awards.

# Conflicts of interest/Competing interests

None.

# Availability of data, materials, and code

Can be accessed here: https://github.com/cartermaclab/expt_sc-feedback-characteristics.

# Authors' contributions using CRediT

Laura St. Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization. Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing. Andrew Poskus served as a lead for investigation - performed experiment and served in a supporting role for writing- original draft preparation and writing - review and editing. Allison Williams served as a lead for investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Olena Leshchyshen contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Sherry Feldman contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing. Joshua G.A. Cashaback contributed equally to conceptualization,  methodology, writing - original  draft preparation, and writing - review and editing. Michael J. Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.

# References

\vspace{2ex}
::: {#refs custom-style="Bibliography"}
:::

### 2022-05-05 docs/preprint/supplementary.Rmd
init

---
title             : "Exercising choice over feedback schedules during practice is not advantageous for motor learning"
shorttitle        : "Choice and feedback characteristics"

authornote: NULL

abstract: NULL

bibliography      : ["../references.bib", "../r-references.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
classoption       : "doc, donotrepeattitle"
#fontsize          : 11pt
output            : papaja::apa6_pdf

header-includes   :
  - \usepackage{pdflscape}
  - \usepackage{setspace}
  #- \pagewiselinenumbers
  - \raggedbottom
  - \AtBeginDocument{\let\maketitle\relax}
  - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Supplementary A

We asked all participants to estimate their performance on the spatial (Fig. \@ref(fig:figS1)) and timing (Fig. \@ref(fig:figS2)) components of the motor task after each trial in retention and transfer, similar to past research [e.g., @barros2019; @carter2012; @carter2014]. Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown). To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial. Next, we computed total estimation error (EE) using the equation:
\begin{equation}
EE = \sqrt{CE^2 + VE^2}
\end{equation}
where $CE$ was the average estimation bias and $VE$ was the standard deviation of these errors. This approach is consistent with that used by @bruechert2003.

## Error estimation in retention and transfer

Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig. \@ref(fig:figS1)) and timing (Fig. \@ref(fig:figS2)) domains in Experiments 1 and 2. For the spatial estimation error, we found a significant main effect of Test in Experiment 1, $F(1,148) = 32.40$, $p < .001$, $\eta_{G}^2 = .060$, and in Experiment 2, $F(1,74) = 18.79$, $p < .001$, $\eta_{G}^2 = .026$, with more accurate estimations in retention than transfer. Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, $F(1,148) = 7.12$, $p = .008$, $\eta_{G}^2 < .001$, we did not decompose the interaction as the effect size estimate was less than $.001$. There were no significant main effects or interactions for timing estimation error in Experiment 2. A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed. Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.

```{r figS1, echo = FALSE, fig.cap = "(ref:figS1-caption)", fig.align = "center"}
knitr::include_graphics("../../figs/figS1.pdf")
```

(ref:figS1-caption) \small \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 **(A)** and Experiment 2 **(B)**. The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple. Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean. Grey connected dots represent individual data for participants in each group. Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.

```{r figS2, echo = FALSE, fig.cap = "(ref:figS2-caption)", fig.align = "center"}
knitr::include_graphics("../../figs/figS2.pdf")
```

(ref:figS2-caption) \small \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 **(A)** and Experiment 2 **(B)**. The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple. Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean. Grey connected dots represent individual data for participants in each group.

## Development of error estimation skills

In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment. We found significant main effects of Test for both the spatial, $F(1.45,104.67) = 20.72$, $p < .001$, $\eta_{G}^2 = .144$, and timing, $F(1.10,79.40) = 46.88$, $p < .001$, $\eta_{G}^2 = .060$, error estimations. For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer ($p$'s < .001), and transfer had higher error than retention ($p$ < .001). Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test ($p$'s < .001). In Experiment 2, none of the main effects or interactions were significant.

\newpage

# Supplementary B

Model diagnostics of total error (E) for the spatial and timing goals revealed skewed distributions. As a result, we carried out sensitivity analyses using shift functions, which is a robust technique that is well-suited for skewed distributions [@rousselet2020; @wilcox2021]. For all shift functions, we collapsed across retention and transfer data to compute a single post-test score for both the spatial and timing goals. Given our primary interest was related to the role of choice during practice for motor learning and shift functions only compare two groups, we only ran these analyses on the choice factor for Experiment 1 (collapsed across feedback) and Experiment 2. Conducting a shift function analysis is a multi-step process that first involved calculating the 20% trimmed means for each participant and time point. Next, deciles for the factor of choice (choice versus yoked) in Experiments 1 and 2 were calculated using the Harrell-Davis estimator [@harrell1982; @R-rogme]. Lastly, differences at each decile were evaluated based on the 95% confidence intervals corrected for multiple comparisons using Hochberg's method [@hochberg1988]. Spatial and timing measures were analyzed separately for Experiments 1 and 2.

## Choice versus yoked

For Experiment 1, the 95% confidence intervals overlapped with zero at each decile when comparing the choice and yoked groups for both the spatial (Fig. \@ref(fig:figS3)A) and timing (Fig. \@ref(fig:figS3)B) goals. Similarly, in Experiment 2 there were no significant differences between the choice and yoked groups in any decile for the spatial (Fig. \@ref(fig:figS3)C) and timing (Fig. \@ref(fig:figS3)D) goals. The results from these shift function analyses are consistent with the analyses reported in the main manuscript and a recent meta-analysis [@mckay2021], suggesting that giving learners choice during practice is not advantageous for motor learning.

```{r figS3, echo = FALSE, fig.cap = "(ref:figS3-caption)", fig.align = "center"}
knitr::include_graphics("../../figs/figS3.pdf")
```

(ref:figS3-caption) \small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) spatial E (deg) shift function.} The top row illustrates scatter plots of individual mean spatial E for each group in Experiment 1 **(A)** and Experiment 2 **(B)**. The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines. The thick black line represents the the median of each distribution. The deciles from each group are joined by colored lines, with blue (Experiment 1) and green (Experiment 2) indicating lower error for the choice group deciles, and red (Experiment 1) and green (Experiment 2) indicating lower error for the yoked group deciles. The bottom row illustrates the shift function, which focuses on the grey shaded region of the x-axis in the middle row. The deciles for the choice group are plotted on the x-axis and the difference in deciles between the choice and yoked group are plotted on the y-axis. The vertical dash line represents the median of the choice distribution. The same color coding for differences in deciles from the middle row is used in the bottom row. Error bars represent 95% confidence intervals, corrected for multiple comparisons. The horizontal dashed line represents zero differences between the deciles of the two group. If a 95% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution. There were no significant differences for any decile in either experiment.

```{r figS4, echo = FALSE, fig.cap = "(ref:figS4-caption)", fig.align = "center"}
knitr::include_graphics("../../figs/figS4.pdf")
```

(ref:figS4-caption) \small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 **(A)** and Experiment 2 **(B)**. The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines. The thick black line represents the the median of each distribution. The deciles from each group are joined by colored lines, with blue (Experiment 1) and green (Experiment 2) indicating lower error for the choice group deciles, and red (Experiment 1) and green (Experiment 2) indicating lower error for the yoked group deciles. The bottom row illustrates the shift function, which focuses on the grey shaded region of the x-axis in the middle row. The deciles for the choice group are plotted on the x-axis and the difference in deciles between the choice and yoked group are plotted on the y-axis. The vertical dash line represents the median of the choice distribution. The same color coding for differences in deciles from the middle row is used in the bottom row. Error bars represent 95% confidence intervals, corrected for multiple comparisons. The horizontal dashed line represents zero differences between the deciles of the two group. If a 95% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution. There were no significant differences for any decile in either experiment.

\newpage

# References

\vspace{2ex}
::: {#refs custom-style="Bibliography"}
:::

### 2022-05-05 docs/preprint/supplementary.tex
init

--- 2022-05-05 docs/preprint/manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
 \usepackage{csquotes}
@@
 \raggedbottom
-\renewcommand\author[1]{}
-\renewcommand\affiliation[1]{}
-\authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
-\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
+\AtBeginDocument{\let\maketitle\relax}
+\renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
 \ifLuaTeX
@@
   pdflang={en-EN},
-  pdfkeywords={Self-controlled, Knowledge of results, OPTIMAL theory, Retention},
   hidelinks,
@@
 
-\authornote{
-
-\vspace{-0.5cm}
-
-\noindent \addORCIDlink{Laura St. Germain}{0000-0002-5513-4183} \newline
-\noindent \addORCIDlink{Brad McKay}{0000-0002-7408-2323} \newline
-\noindent \addORCIDlink{Joshua G.A. Cashaback}{0000-0002-8642-6648} \newline
-\noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
-\noindent Data and code: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics} \vspace{2ex} \newline
-\noindent \textbf{Corresponding authors:} Michael J.
-Carter (\href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}) and Laura St.~Germain (\href{mailto:stgerml@mcmaster.ca}{\nolinkurl{stgerml@mcmaster.ca}}).
-
-}
-
 \affiliation{\phantom{0}}
-
-\abstract{%
-The idea that there is a self-controlled learning advantage, where individuals demonstrate improved motor learning after exercising choice over an aspect of practice compared to no-choice groups, has different causal explanations according to the OPTIMAL theory or an information-processing perspective.
-Within OPTIMAL theory, giving learners choice is considered an autonomy-supportive manipulation that enhances expectations for success and intrinsic motivation.
-In the information-processing view, choice allows learners to engage in performance-dependent strategies that reduce uncertainty about task outcomes.
-To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a rapid reaching task with spatial and timing goals.
-Across both experiments (N = 228 participants), we did not find evidence to support a self-controlled learning advantage.
-Exercising choice during practice did not increase perceptions of autonomy, competence, or intrinsic motivation, nor did it lead to more accurate error estimation skills.
-Both error and graded feedback facilitated skill acquisition and learning, whereas no improvements from pre-test performance were found with binary feedback.
-Finally, the impact of graded and binary feedback on perceived competence highlights a potential dissociation of motivational and informational roles of feedback.
-Although our results regarding self-controlled practice conditions are difficult to reconcile with either the OPTIMAL theory or the information-processing perspective, they are consistent with a growing body of evidence that strongly suggests self-controlled conditions are not an effective approach to enhance motor performance and learning.
-}
 
@@
 
-The underlying source of errors in skilled actions are often ambiguous and difficult to assign as the learner must rely on noisy and delayed sensory information.
-Feedback from an external source, such as a coach or computer display, can facilitate or augment this process (Sigrist et al., 2013).
-Knowledge of results feedback (Salmoni et al., 1984) can provide varying amounts of information to learners depending on its characteristics.
-Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., ``too far''), and binary feedback indicates only success or failure information (e.g., ``miss'') (Luft, 2014).
-When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
-These self-controlled feedback schedules have typically enhanced motor skill learning compared to yoked feedback schedules, wherein learners experience the feedback schedule created by a self-controlled counterpart, but without any choice (see Sanli et al., 2013; Ste-Marie et al., 2020 for reviews).
+\hypertarget{supplementary-a}{%
+\section{Supplementary A}\label{supplementary-a}}
 
-Why self-controlled learning advantages emerge has garnered considerable attention in the motor skill learning literature.
-Within their OPTIMAL (Optimizing performance through intrinsic motivation and attentional learning) theory of motor learning, Wulf and Lewthwaite (2016) have argued that providing participants the opportunity to exercise choice, as in a self-controlled group, creates a virtuous cycle.
-Specifically, choice leads to increased (perceived) autonomy, leading to enhanced expectancies (e.g., perceived competence) and increased (intrinsic) motivation.
-These motivational influences lead to improved motor performance, creating a positive feedback loop that ultimately enhances motor learning compared to those not given the same choice opportunities.
-Support for this view has been drawn from experimental work where participants exercise choice over task-irrelevant or incidental choices.
-Exercising choice over the color of golf balls to putt (Lewthwaite et al., 2015 Experiment 1) or the mat underneath a target (Wulf et al., 2018 Experiment 1), which picture to hang in a lab (Lewthwaite et al., 2015 Experiment 2), hand order in a maximal force production task (Iwatsuki et al., 2017), which photos to look at while running (Iwatsuki et al., 2018), and the order of exercises to perform (Wulf et al., 2014) have been suggested to improve motor performance or learning.
-Other research, however, have failed to replicate this benefit of task-irrelevant or incidental choices on motor performance or learning (Carter \& Ste-Marie, 2017a; Grand et al., 2017; McKay \& Ste-Marie, 2020a, 2020b).
+We asked all participants to estimate their performance on the spatial (Fig.
+\ref{fig:figS1}) and timing (Fig.
+\ref{fig:figS2}) components of the motor task after each trial in retention and transfer, similar to past research (e.g., Barros et al., 2019; Carter et al., 2014; Carter \& Patterson, 2012).
+Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown).
+To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial.
+Next, we computed total estimation error (EE) using the equation:
+\begin{equation}
+EE = \sqrt{CE^2 + VE^2}
+\end{equation}
+where \(CE\) was the average estimation bias and \(VE\) was the standard deviation of these errors. This approach is consistent with that used by Bruechert et al. (2003).
 
-Rather than a motivational account, others have forwarded an information-processing explanation.
-From this perspective, exercising choice allows learners to tailor practice to their individual needs (Chiviacowsky \& Wulf, 2005, 2002) by engaging in performance-contingent strategies (Carter et al., 2014, 2016; Laughlin et al., 2015; Pathania et al., 2019) to reduce uncertainty about movement outcomes (Barros et al., 2019; Carter et al., 2014; Carter \& Ste-Marie, 2017a, 2017b; Grand et al., 2015).
-Evidence for this view has come from experiments that showed the timing of the feedback decision relative to task performance matters (Carter et al., 2014; Chiviacowsky \& Wulf, 2005), that task-relevant choices are more effective than task-irrelevant choices (Carter \& Ste-Marie, 2017a; cf.
-Wulf et al., 2018 Experiment 2), that interfering with information-processing activities during (Couvillion et al., 2020; Woodard \& Fairbrother, 2020) or after (Carter \& Ste-Marie, 2017b; Woodard \& Fairbrother, 2020) task performance eliminates self-controlled learning benefits, and that the ability to accurately estimate one's performance is enhanced in choice compared to yoked groups (Carter et al., 2014; Carter \& Patterson, 2012).
-Thus, further investigation is required to test predictions from these two explanations to better understand why exercising choice during practice confers an advantage for motor skill learning.
+\hypertarget{error-estimation-in-retention-and-transfer}{%
+\subsection{Error estimation in retention and transfer}\label{error-estimation-in-retention-and-transfer}}
 
-To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we provided participants in choice and yoked (i.e., no-choice) groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) during the acquisition of a rapid aiming task.
-Motor learning was assessed using delayed (\textasciitilde24 hours) retention and transfer tests.
-If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule \emph{would not matter} for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups.
-Thus, we predicted all choice groups would demonstrate superior performance and learning compared to the yoked groups.
-Alternatively, if the information-processing account is correct, we hypothesized that the characteristics of one's feedback schedule \emph{would matter} for the self-controlled learning advantage as feedback with greater informational value would be more effective for reducing uncertainties about movement outcomes.
-Thus, we predicted that choice over an error feedback schedule would be the most effective pairing for performance and learning.
-We also included self-report measures of perceptions of autonomy, competence, and intrinsic motivation, and assessments of error estimation abilities to respectively test auxiliary assumptions of the OPTIMAL theory and information-processing explanations.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study (Simmons et al., 2012).
-All data and \texttt{R} scripts can be accessed here: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}.
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\hypertarget{experiment-1}{%
-\subsubsection{Experiment 1}\label{experiment-1}}
-
-One hundred and fifty-two right-handed (Oldfield, 1971), healthy adults participated in Experiment 1 (\(M_{age}\) = 20.64 years, \(SD_{age}\) = 2.45, 88 females).
-Sample size was determined from an \emph{a-priori} power analysis using the \emph{ANOVA: fixed effects, main effects and interactions} option in G*Power (Faul et al., 2009) with the following parameters: \(\alpha\) = 0.05, \(\beta\) = .20, \(f\) = 0.23, numerator = 1, and groups = 2.
-This revealed a required sample of 151 participants.
-Our chosen effect size was based on a meta-analytic estimate (\(f\) = .32) by McKay et al.
-(2014); however, we used a more conservative estimate given the uncertainty of how choice would interact with our feedback characteristic manipulation.
-Participants were compensated \$15 CAD or with course-credit for their time.
-All participants gave written informed consent and the experiment was approved by McMaster University's Research Ethics Board.
-
-\hypertarget{experiment-2}{%
-\subsubsection{Experiment 2}\label{experiment-2}}
-
-A new sample of 76 right-handed (Oldfield, 1971), healthy adults participated in Experiment 2 (\(M_{age}\) = 20.18 years, \(SD_{age}\) = 3.18, 47 females).
-Sample size was selected so group size matched that used in Experiment 1.
-Participants were compensated \$15 CAD or with course-credit for their time.
-All participants gave written informed consent and the experiment was approved by McMaster University's Research Ethics Board.
-
-\hypertarget{task}{%
-\subsection{Task}\label{task}}
-
-In Experiments 1 and 2, participants sat in a chair facing a monitor (1920x1080 resolution) with their left arm in a custom manipulandum that restricted movement to the horizontal plane.
-Their elbow was bent at approximately 90° and they grasped a vertical handle with their left hand.
-Handle position was adjusted as needed to ensure the central axis of rotation was about the elbow.
-The task required a rapid ``out-and-back'' movement such that the reversal happened at \(40^\circ\) (in pre-test, acquisition, and retention) or \(60^\circ\) (in transfer).
-The starting point for all trials was \(0^\circ\).
-Participants were instructed to make a smooth movement to the reversal and back without hesitating when reversing their movement.
-The movement time goal to the reversal was always 225 ms.
-The task and instructions were similar to those used by Sherwood (1996; 2009).
-Vision of the manipulandum and limb were occluded during all phases of the experiment.
-Angular displacement for the elbow was collected via a potentiometer attached to the axis of rotation of the custom manipulandum.
-Potentiometer data were digitally sampled at 1000 Hz (National Instruments PCIe-6321) using a custom LabVIEW program and stored for offline analysis.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-\hypertarget{experiment-1-1}{%
-\subsubsection{Experiment 1}\label{experiment-1-1}}
-
-The first 76 participants were randomly assigned to either the Choice+Error-Feedback group (\(n\) = 38; \(M_{age}\) = 20.24 years, \(SD_{age}\) = 2.37, 22 females) or the Choice+Graded-Feedback group (\(n\) = 38; \(M_{age}\) = 20.76 years, \(SD_{age}\) = 3.02, 26 females).
-This is typical in the self-controlled learning literature as the self-controlled participants' self-selected feedback schedules are required for providing feedback to the participants in the yoked (i.e., control) groups.
-The remaining 76 participants were randomly assigned to either the Yoked+Error-Feedback group (\(n\) = 38; \(M_{age}\) = 20.53 years, \(SD_{age}\) = 2.13, 23 females) or the Yoked+Graded-Feedback group (\(n\) = 38; \(M_{age}\) = 21.03 years, \(SD_{age}\) = 2.32, 22 females).
-
-Data collection consisted of two sessions separated by approximately 24 hours.\footnote{Six participants (three Choice+Error-Feedback and three Choice+Graded-Feedback) had their second session completed approximately 48 hours later because a snowstorm closed the University.} Session one included a pre-test (12 trials) and an acquisition phase (72 trials).
-Session two included the delayed retention (12 trials) and transfer (12 trials) tests.
-No feedback about motor performance was provided in pre-test, retention, or transfer.
-Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals.
-Additionally, half of the participants in each group were randomly selected to estimate their performance on the spatial and timing goals after each trial in the pre-test.
-Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested (e.g., Chiviacowsky \& Wulf, 2005) to be adopted spontaneously by participants controlling their feedback schedule.
-However, asking participants to estimate their performance during pre-test is necessary to be able to assess how this skill develops as a function of one's practice condition.
-
-Participants were reminded of the instructions about the task and its associated goals at the start of the acquisition phase.
-Group specific instructions regarding feedback were also provided.
-Participants in the Choice+Error-Feedback group and the Choice+Graded-Feedback group were told they could choose their feedback schedule, with the restriction that they must select feedback on 24 of the 72 acquisition trials.
-They were informed that if the number of remaining feedback requests equaled the number of remaining acquisition trials, these trials would default to feedback trials.
-This feedback restriction was implemented to ensure the relative frequency of feedback was equated across all groups.
-Similar restrictions have been used in past research involving multiple choice groups (e.g., Chiviacowsky \& Wulf, 2005).
-Participants in the Yoked+Error-Feedback group and the Yoked+Graded-Feedback group were told they may or may not receive feedback following a trial based on a predetermined schedule.
-Thus, participants in these groups were not aware that their feedback schedule was actually created by a participant in a corresponding choice group.
-While this yoking procedure ensures that the total number of feedback trials and their relative placement during acquisition are identical, the content of the feedback reflected each participant's own performance.
-Error feedback for the spatial and timing goals was provided as the difference between the participant's actual performance and the task goal (i.e., constant error).
-Graded feedback for the spatial goal was provided as ``too short'' if performance was \textless{} 40 degrees (or 60 degrees in transfer), ``hit'' if exactly 40 degrees, and ``too far'' if \textgreater{} 40 degrees.
-For the timing goal, graded feedback was provided as ``too fast'' when performance was \textless{} 225 ms, ``hit'' if exactly 225 ms, and ``too slow'' if \textgreater{} 225 ms.
-All participants were shown a sample feedback display that corresponded to their experimental group and were asked to interpret it aloud for the researcher to verify understanding.
+Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig.
+\ref{fig:figS1}) and timing (Fig.
+\ref{fig:figS2}) domains in Experiments 1 and 2.
+For the spatial estimation error, we found a significant main effect of Test in Experiment 1, \(F(1,148) = 32.40\), \(p < .001\), \(\eta_{G}^2 = .060\), and in Experiment 2, \(F(1,74) = 18.79\), \(p < .001\), \(\eta_{G}^2 = .026\), with more accurate estimations in retention than transfer.
+Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, \(F(1,148) = 7.12\), \(p = .008\), \(\eta_{G}^2 < .001\), we did not decompose the interaction as the effect size estimate was less than \(.001\).
+There were no significant main effects or interactions for timing estimation error in Experiment 2.
+A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed.
+Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.
 
@@
 
-{\centering \includegraphics[height=0.45\textheight]{../../figs/fig1}
+{\centering \includegraphics{../../figs/figS1}
 
@@
 
-\caption{\small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
-Trials began by informing participants the trial number (500 ms) they were on in acquisition.
-Shortly after, the text ``Get Ready!'' appeared on the screen and 800 ms later a visual go-signal was presented in the form of a green circle in the center of the screen.
-Participants began their movement when ready after seeing the visual go-signal as we were not interested in reaction time.
-While participants completed their rapid out-and-back movement, the computer screen was blank.
-Upon returning to the starting position, a red circle appeared in the center of the screen.
-A 2000 ms feedback delay interval was used and this interval was followed by the feedback prompt.
-The feedback prompt also displayed an updated counter representing the number of feedback trials they had left.
-If the number of remaining feedback trials matched the number of acquisition trials left, these trials automatically defaulted to feedback trials.
-On trials where feedback was not requested, a blank screen \textbf{(A)} was shown for 3000 ms.
-When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group.
-The error feedback group \textbf{(B)} saw their constant error, the graded feedback group \textbf{(C)} saw either ``too far'' or ``too short'' for the spatial goal and ``too fast'' or ``too slow'' for the timing goal, and the binary feedback group \textbf{(D)} saw either ``hit'' or ``miss'' for the task goals.
-The sequence of events was the same for the yoked groups with the exception they did not see a feedback prompt.
-The sequence of events was similar in pre-test, retention, and transfer except all trials were no-feedback trials.}\label{fig:fig1}
-\end{figure}
-
-A typical acquisition trial (see Figure \ref{fig:fig1}) began with the current trial number displayed (500 ms), followed by a visual ``Get Ready!'' and a visual go-signal (800 ms apart).
-Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
-The computer screen was blank while participants made their movement.
-When participants returned to the starting position, a red circle was displayed on the monitor.
-Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.
-
-Before the retention and transfer tests, participants were reminded about the task and its associated goals.
-All participants were asked to estimate their performance after each trial in retention and transfer.
-After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.
-The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a).
-Cronbach's alpha values for each questionnaire at each time point are reported in Table \ref{tab:table1}.
-
-\hypertarget{experiment-2-1}{%
-\subsubsection{Experiment 2}\label{experiment-2-1}}
-
-Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 22.37 years, \(SD_{age}\) = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 18.00 years, \(SD_{age}\) = 0.93, 28 females).
-Binary feedback for the spatial goal was provided as ``hit'' if performance was exactly 40 degrees (or 60 degrees in transfer) and as ``miss'' for everything else.
-For the timing goal, binary feedback was provided as ``hit'' when performance was exactly 225 ms and as ``miss'' for everything else.
-Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
-
-\begin{table}
-
-\caption{\label{tab:table1}Cronbach's alpha for each questionnaire at each timepoint.}
-\fontsize{11}{13}\selectfont
-\begin{tabular}[t]{>{\raggedright\arraybackslash}p{12em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{6em}>{\raggedright\arraybackslash}p{7em}}
-\toprule
-Questionnaire & After pre-test & After block 1 & After block 6 & Before retention\\
-\midrule
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textbf{Experiment 1}}\\
-\hspace{1em}Perceived autonomy & 0.68 & 0.81 & 0.80 & 0.83\\
-\hspace{1em}Perceived competence & 0.86 & 0.93 & 0.95 & 0.94\\
-\hspace{1em}Intrinsic motivation & 0.86 & 0.90 & 0.92 & 0.93\\
-\addlinespace[0.3em]
-\multicolumn{5}{l}{\textbf{Experiment 2}}\\
-\hspace{1em}Perceived autonomy & 0.39 & 0.73 & 0.79 & 0.85\\
-\hspace{1em}Perceived competence & 0.92 & 0.88 & 0.91 & 0.91\\
-\hspace{1em}Intrinsic motivation & 0.91 & 0.91 & 0.93 & 0.94\\
-\bottomrule
-\multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase.}\\
-\end{tabular}
-\end{table}
-
-\hypertarget{data-analysis}{%
-\subsection{Data Analysis}\label{data-analysis}}
-
-Movement trajectories for all trials were visually inspected by a researcher and trials with errors (e.g., technical issues, moving before the ``go'' signal) were removed.
-A total of 4.03\% (662/16146) and 3.73\% (306/8208) of trials for Experiments 1 and 2 were removed, respectively.
-Trials were aggregated into blocks of 12 trials, resulting in one block of trials for pre-test, retention, and transfer, and six blocks of trials for acquisition.
-Our primary performance outcome variable was total error (E) (Henry, 1974, 1975) and was computed using the equation:
-\begin{equation}
-E = \sqrt{\sum{(x_{i} - T)^2 / n}}
-\end{equation}
-where \(x_{i}\) is the score on the \(i\)th trial, \(T\) is the target goal, and \(n\) is the number of trials in a block.
-
-To test for performance differences in pre-test, retention, and transfer, total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 3 Test; \emph{Experiment 2:} 2 Choice x 3 Test).
-To test for performance differences during acquisition, total error for the spatial and timing goals during acquisition were analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 6 Block; \emph{Experiment 2:} 2 Choice x 6 Block).
-Our primary psychological outcome variables were intrinsic motivation (i.e., interest/enjoyment), perceived competence, and perceived autonomy.
-The mean score of the responses for these constructs at each time point was calculated for each participant and analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 4 Time; \emph{Experiment 2:} 2 Choice x 4 Time).
-Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50\% of the participants in each group in Experiments 1 and 2), retention, and transfer (see \textbf{Supplementary A}).
-
-Alpha was set to .05 for all statistical analyses.
-Corrected degrees of freedom using the Greenhouse-Geisser technique are always reported for repeated measures with more than two levels.
-Generalized eta squared \((\eta_{G}^2)\) is provided as an effect size statistic (Bakeman, 2005; Lakens, 2013; Olejnik \& Algina, 2003) for all omnibus tests.
-Post hoc comparisons were Holm-Bonferroni corrected to control for multiple comparisons.
-Statistical tests were conducted using R (Version 4.1.2; R Core Team, 2021) and the R-packages \emph{afex} (Version 1.1.1; Singmann et al., 2021), \emph{computees} (Re, 2013), \emph{ggResidpanel} (Version 0.3.0.9000; Goode \& Rey, 2022), \emph{kableExtra} (Version 1.3.4; Zhu, 2021), \emph{metafor} (Version 3.4.0; Viechtbauer, 2010), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.0.9000; Pedersen, 2020), \emph{rogme} (Version 0.2.1; Rousselet et al., 2017), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), and \emph{tinylabels} (Version 0.2.3; Barth, 2022) were used in this project.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Model diagnostics of total error for the spatial and timing goals revealed skewed distributions.
-We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions (Rousselet \& Wilcox, 2020; Wilcox, 2021).
-The results of these analyses (see \textbf{Supplementary B}) were consistent with those of the mixed ANOVAs, which we report below.
-
-\hypertarget{pre-test-retention-and-transfer}{%
-\subsection{Pre-test, retention, and transfer}\label{pre-test-retention-and-transfer}}
-
-\hypertarget{experiment-1-2}{%
-\subsubsection{Experiment 1}\label{experiment-1-2}}
-
-Spatial (Fig.
-\ref{fig:fig2}A) and timing (Fig.
-\ref{fig:fig2}B) error decreased from the pre-test to the retention and transfer tests.
-There was a main effect of Test for spatial error, \(F(1.33,196.52) = 40.20\), \(p < .001\), \(\eta_{G}^2 = .138\), where performance was less errorful in retention and transfer than pre-test (\(p\)'s \textless{} .001) and performance in retention was better than transfer (\(p\) \textless{} .001).
-A main effect of Test was also found for timing error, \(F(1.08,160.23) = 81.21\), \(p < .001\), \(\eta_{G}^2 = .245\), with pre-test performance more errorful than both retention and transfer (\(p\)'s \textless{} .001), and retention was less errorful than transfer (\(p\) \textless{} .001).
-
-\hypertarget{experiment-2-2}{%
-\subsubsection{Experiment 2}\label{experiment-2-2}}
-
-Spatial (Fig.
-\ref{fig:fig3}A) and timing (Fig.
-\ref{fig:fig3}B) error did not change considerably from the pre-test to the retention and transfer tests.
-There were no significant main effects or interactions for either task goals.
-
-\vspace{4ex}
-
-\begin{figure}
-
-{\centering \includegraphics{../../figs/fig2}
-
-}
-
-\caption{\small \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses.
-Error bars denote 95\% bootstrapped confidence intervals.
-\textbf{(A)} Spatial total error (degrees) and \textbf{(B)} timing total error (ms) averaged across blocks and participants within each group.
-Dotted vertical lines denote the different experimental phases.
-Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2.
-Self-reported scores for perceived autonomy \textbf{(C)}, perceived competence \textbf{(D)}, and intrinsic motivation \textbf{(E)} after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2.
-Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree).
-Dots represent individual data points.}\label{fig:fig2}
+\caption{\small \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.
+Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS1}
 \end{figure}
@@
 
-{\centering \includegraphics{../../figs/fig3}
+{\centering \includegraphics{../../figs/figS2}
 
@@
 
-\caption{\small \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares.
-Error bars denote 95\% bootstrapped confidence intervals.
-\textbf{(A)} Spatial total error (degrees) and \textbf{(B)} timing total error (ms) averaged across blocks and participants within each group.
-Dotted vertical lines denote the different experimental phases.
-Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2.
-Self-reported scores for perceived autonomy \textbf{(C)}, perceived competence \textbf{(D)}, and intrinsic motivation \textbf{(E)} after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2.
-Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree).
-Dots represent individual data points.}\label{fig:fig3}
+\caption{\small \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.}\label{fig:figS2}
+\end{figure}
+
+\hypertarget{development-of-error-estimation-skills}{%
+\subsection{Development of error estimation skills}\label{development-of-error-estimation-skills}}
+
+In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment.
+We found significant main effects of Test for both the spatial, \(F(1.45,104.67) = 20.72\), \(p < .001\), \(\eta_{G}^2 = .144\), and timing, \(F(1.10,79.40) = 46.88\), \(p < .001\), \(\eta_{G}^2 = .060\), error estimations.
+For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer (\(p\)'s \textless{} .001), and transfer had higher error than retention (\(p\) \textless{} .001).
+Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test (\(p\)'s \textless{} .001).
+In Experiment 2, none of the main effects or interactions were significant.
+
+\newpage
+
+\hypertarget{supplementary-b}{%
+\section{Supplementary B}\label{supplementary-b}}
+
+Model diagnostics of total error (E) for the spatial and timing goals revealed skewed distributions.
+As a result, we carried out sensitivity analyses using shift functions, which is a robust technique that is well-suited for skewed distributions (Rousselet \& Wilcox, 2020; Wilcox, 2021).
+For all shift functions, we collapsed across retention and transfer data to compute a single post-test score for both the spatial and timing goals.
+Given our primary interest was related to the role of choice during practice for motor learning and shift functions only compare two groups, we only ran these analyses on the choice factor for Experiment 1 (collapsed across feedback) and Experiment 2.
+Conducting a shift function analysis is a multi-step process that first involved calculating the 20\% trimmed means for each participant and time point.
+Next, deciles for the factor of choice (choice versus yoked) in Experiments 1 and 2 were calculated using the Harrell-Davis estimator (Harrell \& Davis, 1982; Rousselet et al., 2017).
+Lastly, differences at each decile were evaluated based on the 95\% confidence intervals corrected for multiple comparisons using Hochberg's method (Hochberg, 1988).
+Spatial and timing measures were analyzed separately for Experiments 1 and 2.
+
+\hypertarget{choice-versus-yoked}{%
+\subsection{Choice versus yoked}\label{choice-versus-yoked}}
+
+For Experiment 1, the 95\% confidence intervals overlapped with zero at each decile when comparing the choice and yoked groups for both the spatial (Fig.
+\ref{fig:figS3}A) and timing (Fig.
+\ref{fig:figS3}B) goals.
+Similarly, in Experiment 2 there were no significant differences between the choice and yoked groups in any decile for the spatial (Fig.
+\ref{fig:figS3}C) and timing (Fig.
+\ref{fig:figS3}D) goals.
+The results from these shift function analyses are consistent with the analyses reported in the main manuscript and a recent meta-analysis (McKay et al., in-press), suggesting that giving learners choice during practice is not advantageous for motor learning.
+
+\begin{figure}
+
+{\centering \includegraphics{../../figs/figS3}
+
+}
+
+\caption{\small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) spatial E (deg) shift function.} The top row illustrates scatter plots of individual mean spatial E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines.
+The thick black line represents the the median of each distribution.
+The deciles from each group are joined by colored lines, with blue (Experiment 1) and green (Experiment 2) indicating lower error for the choice group deciles, and red (Experiment 1) and green (Experiment 2) indicating lower error for the yoked group deciles.
+The bottom row illustrates the shift function, which focuses on the grey shaded region of the x-axis in the middle row.
+The deciles for the choice group are plotted on the x-axis and the difference in deciles between the choice and yoked group are plotted on the y-axis.
+The vertical dash line represents the median of the choice distribution.
+The same color coding for differences in deciles from the middle row is used in the bottom row.
+Error bars represent 95\% confidence intervals, corrected for multiple comparisons.
+The horizontal dashed line represents zero differences between the deciles of the two group.
+If a 95\% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution.
+There were no significant differences for any decile in either experiment.}\label{fig:figS3}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{../../figs/figS4}
+
+}
+
+\caption{\small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines.
+The thick black line represents the the median of each distribution.
+The deciles from each group are joined by colored lines, with blue (Experiment 1) and green (Experiment 2) indicating lower error for the choice group deciles, and red (Experiment 1) and green (Experiment 2) indicating lower error for the yoked group deciles.
+The bottom row illustrates the shift function, which focuses on the grey shaded region of the x-axis in the middle row.
+The deciles for the choice group are plotted on the x-axis and the difference in deciles between the choice and yoked group are plotted on the y-axis.
+The vertical dash line represents the median of the choice distribution.
+The same color coding for differences in deciles from the middle row is used in the bottom row.
+Error bars represent 95\% confidence intervals, corrected for multiple comparisons.
+The horizontal dashed line represents zero differences between the deciles of the two group.
+If a 95\% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution.
+There were no significant differences for any decile in either experiment.}\label{fig:figS4}
 \end{figure}
@@
 \newpage
-
-\hypertarget{acquisition}{%
-\subsection{Acquisition}\label{acquisition}}
-
-\hypertarget{experiment-1-3}{%
-\subsubsection{Experiment 1}\label{experiment-1-3}}
-
-All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
-\ref{fig:fig2}A).
-This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)).
-Timing error also decreased during the acquisition period (Fig.
-\ref{fig:fig2}B).
-The significant main effect of Block, \(F(1.75,259.59) = 55.44\), \(p < .001\), \(\eta_{G}^2 = .138\), was superseded by a significant Feedback x Block interaction, \(F(1.75, 259.59) = 3.56\), \(p = .035\), \(\eta_{G}^2 = .010\).
-Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)), but performance plateaued from block 2 onward in acquisition (\(p\)'s \(\geq .257\)).
-Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).
-
-\hypertarget{experiment-2-3}{%
-\subsubsection{Experiment 2}\label{experiment-2-3}}
-
-Spatial (Fig.
-\ref{fig:fig3}A) and timing (Fig.
-\ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-None of the main effects or interactions for either task goals were significant.
-
-\hypertarget{psychological-variables}{%
-\subsection{Psychological variables}\label{psychological-variables}}
-
-\hypertarget{experiment-1-4}{%
-\subsubsection{Experiment 1}\label{experiment-1-4}}
-
-Perceptions of autonomy (Fig.
-\ref{fig:fig2}C) showed a slight decrease across time points, supported by a main effect of Time, \(F(2.25,332.95) = 3.69\), \(p < .022\), \(\eta_{G}^2 = .003\).
-Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test (\(p = .031\)).
-Self-ratings for perceived competence (Fig.
-\ref{fig:fig2}D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic.
-Main effects of Time, \(F(1.92, 283.47) = 3.43\), \(p = .036\), \(\eta_{G}^2 = .006\), and Feedback, \(F(1,148) = 47.36\), \(p < .001\), \(\eta_{G}^2 = .188\), were superseded by a Feedback x Time interaction, \(F(1.92, 283.47) = 28.04\), \(p < .001\), \(\eta_{G}^2 = .050\).
-Perceived competence scores were not significantly different after the pre-test (\(p = .232\)); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points (\(p\)'s \(< .001\)).
-Self-reported scores for intrinsic motivation (Fig.
-\ref{fig:fig2}E) generally decreased after block 1, which was supported by a main effect of Time, \(F(2.40,355.90) = 14.69\), \(p < .001\), \(\eta_{G}^2 = .012\).
-Intrinsic motivation scores initially increased following the pre-test to after block 1 (\(p = .003\)); however, scores after block 1 of acquisition were greater than those reported at the end of acquisition (i.e., block 6) and before retention (\(p\)'s \(< .001\)).
-Self-reported ratings were also lower before retention compared to after the pre-test (\(p = .043\)).
-
-\hypertarget{experiment-2-4}{%
-\subsubsection{Experiment 2}\label{experiment-2-4}}
-
-Self-reported scores for perceived autonomy (Fig.
-\ref{fig:fig3}C) were similar across all time points.
-There were no main effects or interactions.
-Perceptions of competence (Fig.
-\ref{fig:fig3}D) showed a considerable decrease after the pre-test, \(F(1.85,136.91) = 106.10\), \(p < .001\), \(\eta_{g}^2 = .298\), where scores were significantly greater after the pre-test compared to all other time points (\(p\)'s \(< .001\)), and were higher after block 1 of acquisition than before retention (\(p = .004\)).
-Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, \(F(2.37,175.55) = 15.31\), \(p < .001\), \(\eta_{G}^2 = .018\).
-Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention (\(p\)'s \(< .001\)), and higher after block 1 than after block 6 and before retention (\(p\)'s \(< .026\)).
-
-\hypertarget{equivalence-analysis}{%
-\subsection{Equivalence analysis}\label{equivalence-analysis}}
-
-Our main comparison of interest was between choice and no-choice (i.e., yoked groups).
-To evaluate the self-controlled learning effect observed across Experiments 1 and 2, Hedges' \emph{g} for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies.
-Next, a random effects meta-analysis was conducted on the retention test data\footnote{We report an estimate for retention tests to facilitate comparison to a recent meta-analysis (McKay et al., in-press) that produced estimated effects of self-controlled learning at retention specifically.} to generate a summary point estimate and 90\% confidence intervals (CI).
-This resulted in an overall estimated effect of \(g = .05\) (favoring self-controlled) and \(90\% \,CI \,[-.12,.23]\).
-
-Equivalence tests can be conducted to evaluate whether the observed differences are significantly smaller than a pre-determined smallest effect size of interest (see Harms \& Lakens, 2018 for a discussion).
-Typically, a two one-sided tests procedure is used to compare the observed effect to upper and lower equivalence bounds, and if the effect is significantly smaller than both bounds then the hypothesis that the effect is large enough to be of interest is rejected (Lakens, 2017; Schuirmann, 1987).
-However, we did not pre-specify a smallest effect of interest, so instead we report the 90\% confidence intervals (see above).
-All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not.
-Therefore, the present experiments can be considered inconsistent with all effects larger than \(g = \pm.23\).
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-The purpose of the present experiments was to test between motivational and information-processing accounts of the putative self-controlled learning advantage (see Ste-Marie et al., 2020 for a review).
-According to the OPTIMAL theory (Wulf \& Lewthwaite, 2016), self-controlled practice or choice conditions are advantageous because the provision of choice increases perceptions of autonomy and competence, which increase intrinsic motivation and ultimately both motor performance and learning.
-Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals (Carter et al., 2014; Carter \& Ste-Marie, 2017b; Grand et al., 2015).
-In contrast to these predictions, we did not find evidence that providing learners with choice over their feedback schedule was beneficial for motor learning, despite collecting a much larger sample (\emph{N} = 228 across both Experiments) than those commonly used in self-controlled learning experiments (median sample size \emph{N} = 36 in a meta-analysis by McKay et al., in-press) and motor learning experiments in general (median \emph{n}/group = 11 in a review by Lohse et al., 2016).
-Further, exercising choice in practice did not enhance perceptions of autonomy, competence, or intrinsic motivation, and also did not result in more accurate performance estimations in delayed tests of motor learning.
-Overall, we found no support for the OPTIMAL theory or information-processing perspective.
-Our results challenge the prevailing view that the self-controlled learning benefit is a robust effect.
-
-The failed replication of a self-controlled learning advantage was surprising given the dominant view for the past 25 years has been that it is a robust effect and one that should be recommended to coaches and practitioners (Sanli et al., 2013; Ste-Marie et al., 2020; Wulf \& Lewthwaite, 2016).
-Our findings are, however, consistent with a growing list of relatively large--often pre-registered--experiments that have not found self-controlled learning benefits (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press).
-One possible explanation for this discrepancy between earlier and more recent experiments may be that the self-controlled learning advantage was the result of underpowered designs, which has been highlighted as a problem in motor learning research (see Lohse et al., 2016 for a discussion).
-When underpowered designs find significant results, they are prone to be false positives with inflated estimates of effects (Button et al., 2013; Lakens \& Evers, 2014), which can be further exaggerated with questionable research practices such as \emph{p}-hacking and selective reporting (e.g., Munafò et al., 2017; Simmons et al., 2011).
-Thus, a self-controlled learning advantage may not actually exist.
-Alternatively, if one does exist then it seems likely it is a much smaller effect than originally estimated and requires considerably larger samples to reliability detect than those commonly used in motor learning research.
-Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results (McKay et al., in-press).
-We estimated the overall effect of self-controlled practice in retention to be significantly smaller than any effect larger than \(g = .23\).
-This is consistent with the estimates from McKay et al.
-(in-press) after accounting for publication bias (\(g =\) -.11 to .26), which suggested either no effect or a small effect in an unknown direction.
-Taken together, we argue that it may be time for the self-controlled learning advantage to be considered a non-replicable effect in motor learning.
-
-Given our current replication failure with those in recent years (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press) and the conclusions from McKay et al.
-(in-press), motivational (i.e., OPTIMAL theory) versus information-processing explanations seem moot.
-Nevertheless, the present results are incompatible with both perspectives.
-Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
-Similarly, self-controlled feedback schedules did not enhance error estimation skills (see \textbf{Supplementary A}) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
-Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose.
-When feedback provided information about the direction of an error or when it contained both direction and magnitude of an error, participants were able to improve at the task throughout acquisition and retain these improvements in skill relative to pre-test.
-However, when feedback was binary and direction and magnitude of an error was absent, there was no improvement in skill from baseline levels.
-This is in contrast with past research that has shown people can learn motor tasks with binary feedback (e.g., Cashaback et al., 2017, 2019; Izawa \& Shadmehr, 2011).
-One possible explanation for this discrepancy may be the amount of practice trials (Magill \& Wood, 1986).
-Practicing with binary feedback may inherently require a longer training period for learning to occur compared to graded and error feedback, which both have greater precision.
-Additionally, we used a strict criteria with binary feedback where any outcome other than zero error was considered a miss.
-Thus, binary feedback may be more effective when paired with a tolerance zone such as that used in the bandwidth technique (see Anderson et al., 2020 for a review; Cauraugh et al., 1993; Lee \& Carnahan, 1990).
-
-Although unexpected, the influence of feedback characteristics on perceptions of competence may hint to a dissociation between informational and motivational impacts of knowledge-of-results feedback.
-In Experiment 1, participants who received graded feedback reported significantly lower perceptions of competence than participants who received error feedback.
-Yet, despite these lower expectations for success, the graded feedback groups did not demonstrate degraded performance or learning compared to the error feedback group.
-Participants in Experiment 2 who received binary feedback reported the lowest perceptions of competence and were also the only participants who did not show improvements in task performance from pre-test.
-Thus, future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
-
-In two experiments we failed to observe the predicted benefits of self-controlled feedback on motor learning.
-Similarly, we failed to find the predicted motivational and informational consequences of choice in either experiment, challenging both the OPTIMAL theory and information-processing explanation of the so-called self-controlled learning advantage.
-Although the present experiments were not pre-registered, the analysis plan was determined prior to viewing the data.
-In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see \textbf{Supplementary B}).
-The sensitivity analyses supported the conclusions of the primary analyses and are consistent with research that has followed pre-registered analysis plans (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press).
-Lastly, our results and conclusions are in line with a recent meta-analysis (McKay et al., in-press) that suggests the apparent benefits of self-controlled practice are due to selection bias rather than true effects.
-
-\vspace{2.5ex}
-
-\hypertarget{funding}{%
-\section{Funding}\label{funding}}
-
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
-LSG was supported by an NSERC Postgraduate Scholarship.
-JGAC was supported by an NIH U45GM104941 grant.
-AW and AP were supported by NSERC Undergraduate Student Research Awards.
-
-\hypertarget{conflicts-of-interestcompeting-interests}{%
-\section{Conflicts of interest/Competing interests}\label{conflicts-of-interestcompeting-interests}}
-
-None.
-
-\hypertarget{availability-of-data-materials-and-code}{%
-\section{Availability of data, materials, and code}\label{availability-of-data-materials-and-code}}
-
-Can be accessed here: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}.
-
-\hypertarget{authors-contributions-using-credit}{%
-\section{Authors' contributions using CRediT}\label{authors-contributions-using-credit}}
-
-Laura St.~Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization.
-Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing.
-Andrew Poskus served as a lead for investigation - performed experiment and served in a supporting role for writing- original draft preparation and writing - review and editing.
-Allison Williams served as a lead for investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing.
-Olena Leshchyshen contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing.
-Sherry Feldman contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing.
-Joshua G.A.
-Cashaback contributed equally to conceptualization, methodology, writing - original draft preparation, and writing - review and editing.
-Michael J.
-Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-anderson2020}{}}%
-Anderson, D.
-I., Magill, R.
-A., Mayo, A.
-M., \& Steel, K.
-A.
-(2020).
-Enhancing motor skill acquisition with augmented feedback.
-In \emph{Skill acquisition in sport: Research, theory and practice} (3rd ed.).
-{Routledge}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. \url{https://github.com/crsh/papaja}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bacelar2022}{}}%
-Bacelar, M.
-F.
-B., Parma, J.
-O., Cabral, D., Daou, M., Lohse, K.
-R., \& Miller, M.
-W.
-(2022).
-Dissociating the contributions of motivational and information processing factors to the self-controlled feedback learning benefit.
-\emph{Psychology of Sport and Exercise}, \emph{59}, 102119.
-\url{https://doi.org/10.1016/j.psychsport.2021.102119}
-
-\leavevmode\vadjust pre{\hypertarget{ref-bakeman2005}{}}%
-Bakeman, R. (2005). Recommended effect size statistics for repeated measures designs. \emph{Behavior Research Methods}, \emph{37}(3), 379--384. \url{https://doi.org/10.3758/bf03192707}
-
 \leavevmode\vadjust pre{\hypertarget{ref-barros2019}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
-Barth, M. (2022). \emph{{tinylabels}: Lightweight variable labels}. \url{https://cran.r-project.org/package=tinylabels}
-
-\leavevmode\vadjust pre{\hypertarget{ref-button2013}{}}%
-Button, K.
-S., Ioannidis, J.
-P.
-A., Mokrysz, C., Nosek, B.
-A., Flint, J., Robinson, E.
-S.
-J., \& Munafò, M.
-R.
-(2013).
-Power failure: why small sample size undermines the reliability of neuroscience.
-\emph{Nature Reviews Neuroscience}, \emph{14}(5), 365--376.
-\url{https://doi.org/10.1038/nrn3475}
+\leavevmode\vadjust pre{\hypertarget{ref-bruechert2003}{}}%
+Bruechert, L., Lai, Q., \& Shea, C.
+H.
+(2003).
+Reduced knowledge of results frequency enhances error detection.
+\emph{Research Quarterly for Exercise and Sport}, \emph{74}(4), 467--472.
+\url{https://doi.org/10.1080/02701367.2003.10609116}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-carter2016}{}}%
-Carter, M.
-J., Rathwell, S., \& Ste-Marie, D.
-M.
-(2016).
-Motor skill retention is modulated by strategy choice during self-controlled knowledge of results schedules.
-\emph{Journal of Motor Learning and Development}, \emph{4}, 100--115.
-\url{https://doi.org/10.1123/jmld.2015-0023}
+\leavevmode\vadjust pre{\hypertarget{ref-harrell1982}{}}%
+Harrell, F. E., \& Davis, C. (1982). A new distribution-free quantile estimator. \emph{Biometrika}, \emph{69}(3), 635--640. \url{https://doi.org/10.1093/biomet/69.3.635}
 
-\leavevmode\vadjust pre{\hypertarget{ref-carter2017b}{}}%
-Carter, M.
-J., \& Ste-Marie, D.
-M.
-(2017a).
-Not all choices are created equal: {Task}-relevant choices enhance motor learning compared to task-irrelevant choices.
-\emph{Psychonomic Bulletin \& Review}, \emph{24}(6), 1879--1888.
-\url{https://doi.org/10.3758/s13423-017-1250-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-carter2017a}{}}%
-Carter, M.
-J., \& Ste-Marie, D.
-M.
-(2017b).
-An interpolated activity during the knowledge-of-results delay interval eliminates the learning advantages of self-controlled feedback schedules.
-\emph{Psychological Research}, \emph{81}(2), 399--406.
-\url{https://doi.org/10.1007/s00426-016-0757-2}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cashaback2019}{}}%
-Cashaback, J.
-G.
-A., Lao, C.
-K., Palidis, D.
-J., Coltman, S.
-K., McGregor, H.
-R., \& Gribble, P.
-L.
-(2019).
-The gradient of the reinforcement landscape influences sensorimotor learning.
-\emph{PLoS Computational Biology}, \emph{15}(3), e1006839.
-\url{https://doi.org/10.1371/journal.pcbi.1006839}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cashaback2017}{}}%
-Cashaback, J.
-G.
-A., McGregor, H.
-R., Mohatarem, A., \& Gribble, P.
-L.
-(2017).
-Dissociating error-based and reinforcement-based loss functions during sensorimotor learning.
-\emph{PLoS Computational Biology}, \emph{13}(7), e1005623.
-\url{https://doi.org/10.1371/journal.pcbi.1005623}
-
-\leavevmode\vadjust pre{\hypertarget{ref-cauraugh1993}{}}%
-Cauraugh, J.
-H., Chen, D., \& Radio, S.
-J.
-(1993).
-Effects of traditional and reversed bandwidth knowledge of results on motor learning.
-\emph{Research Quarterly for Exercise and Sport}, \emph{64}(4), 413--417.
-\url{https://doi.org/10.1080/02701367.1993.10607594}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2005}{}}%
-Chiviacowsky, S., \& Wulf, G.
-(2005).
-Self-controlled feedback is effective if it is based on the learner's performance.
-\emph{Research Quarterly for Exercise and Sport}, \emph{76}(1), 42--48.
-\url{https://doi.org/10.1080/02701367.2005.10599260}
-
-\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2002}{}}%
-Chiviacowsky, S., \& Wulf, G.
-(2002).
-Self-controlled feedback: {Does} it enhance learning because performers get feedback when they need it?
-\emph{Research Quarterly for Exercise and Sport}, \emph{73}(4), 408--415.
-\url{https://doi.org/10.1080/02701367.2002.10609040}
-
-\leavevmode\vadjust pre{\hypertarget{ref-couvillion2020}{}}%
-Couvillion, K.
-F., Bass, A.
-D., \& Fairbrother, J.
-T.
-(2020).
-Increased cognitive load during acquisition of a continuous task eliminates the learning effects of self-controlled knowledge of results.
-\emph{Journal of Sports Sciences}, \emph{38}(1), 94--99.
-\url{https://doi.org/10.1080/02640414.2019.1682901}
-
-\leavevmode\vadjust pre{\hypertarget{ref-faul2009}{}}%
-Faul, F., Erdfelder, E., Buchner, A., \& Lang, A.-G.
-(2009).
-Statistical power analyses using g*power 3.1: Tests for correlation and regression analyses.
-\emph{Behavior Research Methods}, \emph{41}(4), 1149--1160.
-\url{https://doi.org/10.3758/BRM.41.4.1149}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-ggResidpanel}{}}%
-Goode, K., \& Rey, K. (2022). \emph{ggResidpanel: Panels and interactive versions of diagnostic plots using 'ggplot2'}. \url{https://goodekat.github.io/ggResidpanel/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grand2015}{}}%
-Grand, K.
-F., Bruzi, A.
-T., Dyke, F.
-B., Godwin, M.
-M., Leiker, A.
-M., Thompson, A.
-G., Buchanan, T.
-L., \& Miller, M.
-W.
-(2015).
-Why self-controlled feedback enhances motor learning: {Answers} from electroencephalography and indices of motivation.
-\emph{Human Movement Science}, \emph{43}, 23--32.
-\url{https://doi.org/10.1016/j.humov.2015.06.013}
-
-\leavevmode\vadjust pre{\hypertarget{ref-grand2017}{}}%
-Grand, K.
-F., Daou, M., Lohse, K.
-R., \& Miller, M.
-W.
-(2017).
-Investigating the mechanisms underlying the effects of an incidental choice on motor learning.
-\emph{Journal of Motor Learning and Development}, \emph{5}(2), 207--226.
-\url{https://doi.org/10.1123/jmld.2016-0041}
-
-\leavevmode\vadjust pre{\hypertarget{ref-harms2018}{}}%
-Harms, C., \& Lakens, D.
-(2018).
-Making 'null effects' informative: Statistical techniques and inferential frameworks.
-\emph{Translational Research}, \emph{3}(Suppl 2), 382--393.
-\url{https://doi.org/10.18053/jctres.03.2017S2.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-henry1974}{}}%
-Henry, F.
-M.
-(1974).
-Variable and constant performance errors within a group of individuals.
-\emph{Journal of Motor Behavior}, \emph{6}(3), 149--154.
-\url{https://doi.org/10.1080/00222895.1974.10734991}
-
-\leavevmode\vadjust pre{\hypertarget{ref-henry1975}{}}%
-Henry, F. M. (1975). Absolute error vs {``e''} in target accuracy. \emph{Journal of Motor Behavior}, \emph{7}(3), 227--228. \url{https://doi.org/10.1080/00222895.1975.10735039}
-
-\leavevmode\vadjust pre{\hypertarget{ref-iwatsuki2017}{}}%
-Iwatsuki, T., Abdollahipour, R., Psotta, R., Lewthwaite, R., \& Wulf, G.
-(2017).
-Autonomy facilitates repeated maximum force productions.
-\emph{Human Movement Science}, \emph{55}, 264--268.
-\url{https://doi.org/10.1016/j.humov.2017.08.016}
-
-\leavevmode\vadjust pre{\hypertarget{ref-iwatsuki2018}{}}%
-Iwatsuki, T., Navalta, J. W., \& Wulf, G. (2018). Autonomy enhances running efficiency. \emph{Journal of Sports Sciences}, \emph{37}(6), 685--691. \url{https://doi.org/10.1080/02640414.2018.1522939}
-
-\leavevmode\vadjust pre{\hypertarget{ref-izawa2011}{}}%
-Izawa, J., \& Shadmehr, R.
-(2011).
-Learning from sensory and reward prediction errors during motor adaptation.
-\emph{PLoS Computational Biology}, \emph{7}(3), e1002012.
-\url{https://doi.org/10.1371/journal.pcbi.1002012}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
-Lakens, D.
-(2017).
-Equivalence tests: {A} practical primer for t tests, correlations, and meta-analyses.
-\emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362.
-\url{https://doi.org/10.1177/1948550617697177}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2013}{}}%
-Lakens, D.
-(2013).
-Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and {ANOVAs}.
-\emph{Frontiers in Psychology}, \emph{4}, 863.
-\url{https://doi.org/10.3389/fpsyg.2013.00863}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lakens2014}{}}%
-Lakens, D., \& Evers, E.
-R.
-K.
-(2014).
-Sailing from the seas of chaos into the corridor of stability: Practical recommendations to increase the informational value of studies.
-\emph{Perspectives on Psychological Science}, \emph{9}(3), 278--292.
-
-\leavevmode\vadjust pre{\hypertarget{ref-laughlin2015}{}}%
-Laughlin, D.
-D., Fairbrother, J.
-T., Wrisberg, C.
-A., Alami, A., Fisher, L.
-A., \& Huck, S.
-W.
-(2015).
-Self-control behaviors during the learning of a cascade juggling task.
-\emph{Human Movement Science}, \emph{41}, 9--19.
-\url{https://doi.org/10.1016/j.humov.2015.02.002}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lee1990}{}}%
-Lee, T.
-D., \& Carnahan, H.
-(1990).
-Bandwidth knowledge of results and motor learning: More than just a relative frequency effect.
-\emph{The Quarterly Journal of Experimental Psychology}, \emph{42}(4), 777--789.
-\url{https://doi.org/10.1080/14640749008401249}
-
-\leavevmode\vadjust pre{\hypertarget{ref-leiker2019}{}}%
-Leiker, A.
-M., Pathania, A., Miller, M.
-W., \& Lohse, K.
-R.
-(2019).
-Exploring the {Neurophysiological} {Effects} of {Self}-{Controlled} {Practice} in {Motor} {Skill} {Learning}.
-\emph{Journal of Motor Learning and Development}, \emph{7}(1), 13--34.
-\url{https://doi.org/10.1123/jmld.2017-0051}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lewthwaite2015}{}}%
-Lewthwaite, R., Chiviacowsky, S., Drews, R., \& Wulf, G.
-(2015).
-Choose to move: {The} motivational impact of autonomy support on motor learning.
-\emph{Psychonomic Bulletin \& Review}, \emph{22}(5), 1383--1388.
-\url{https://doi.org/10.3758/s13423-015-0814-7}
-
-\leavevmode\vadjust pre{\hypertarget{ref-lohse2016}{}}%
-Lohse, K.
-R., Buchanan, T., \& Miller, M.
-W.
-(2016).
-Underpowered and Overworked: Problems With Data Analysis in Motor Learning Studies.
-\emph{Journal of Motor Learning and Development}, \emph{4}(1), 37--58.
-\url{https://doi.org/10.1123/jmld.2015-0010}
-
-\leavevmode\vadjust pre{\hypertarget{ref-luft2014}{}}%
-Luft, C.
-D.
-B.
-(2014).
-Learning from feedback: The neural mechanisms of feedback processing facilitating better performance.
-\emph{Behavioural Brain Research}, \emph{261}, 356--368.
-\url{https://doi.org/10.1016/j.bbr.2013.12.043}
-
-\leavevmode\vadjust pre{\hypertarget{ref-magill1986}{}}%
-Magill, R.
-A., \& Wood, C.
-A.
-(1986).
-Knowledge of results precision as a learning variable in motor skill acquisition.
-\emph{Research Quarterly for Exercise and Sport}, \emph{57}(2), 170--173.
-\url{https://doi.org/10.1080/02701367.1986.10762195}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mcauley1989}{}}%
-McAuley, E., Duncan, T., \& Tammen, V.
-V.
-(1989).
-Psychometric properties of the {Intrinsic} {Motivation} {Inventory} in a competitive sport setting: A confirmatory factor analysis.
-\emph{Research Quarterly for Exercise and Sport}, \emph{60}(1), 48--58.
-\url{https://doi.org/10.1080/02701367.1989.10607413}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mckay2014}{}}%
-McKay, B., Carter, M. J., \& Ste-Marie, D. M. (2014). Self-controlled learning: {A} meta analysis. \emph{Journal of Sport and Exercise Psychology}, \emph{36}(s1).
-
-\leavevmode\vadjust pre{\hypertarget{ref-mckay2020a}{}}%
-McKay, B., \& Ste-Marie, D.
-M.
-(2020a).
-Autonomy support and reduced feedback frequency have trivial effects on learning and performance of a golf putting task.
-\emph{Human Movement Science}, \emph{71}, 102612.
-\url{https://doi.org/10.1016/j.humov.2020.102612}
-
-\leavevmode\vadjust pre{\hypertarget{ref-mckay2020b}{}}%
-McKay, B., \& Ste-Marie, D.
-M.
-(2020b).
-Autonomy {Support} via {Instructionally} {Irrelevant} {Choice} {Not} {Beneficial} for {Motor} {Performance} or {Learning}.
-\emph{Research Quarterly for Exercise and Sport}, 1--13.
-\url{https://doi.org/10.1080/02701367.2020.1795056}
+\leavevmode\vadjust pre{\hypertarget{ref-hochberg1988}{}}%
+Hochberg, Y. (1988). A sharper bonferroni procedure for multiple tests of significance. \emph{Biometrika}, \emph{75}(4), 800--802. \url{https://doi.org/10.1093/biomet/75.4.800}
 
@@
 \url{https://doi.org/10.31234/osf.io/8d3nb}
-
-\leavevmode\vadjust pre{\hypertarget{ref-munafo2017}{}}%
-Munafò, M.
-R., Nosek, B.
-A., Bishop, D.
-V.
-M., Button, K.
-S., Chambers, C.
-D., Percie du Sert, N., Simonsohn, U., Wagenmakers, E.-J., Ware, J.
-J., \& Ioannidis, J.
-(2017).
-A manifesto for reproducible science.
-\emph{Nature Human Behaviour}, \emph{1}(1), 1--9.
-\url{https://doi.org/10.1038/s41562-016-0021}
-
-\leavevmode\vadjust pre{\hypertarget{ref-oldfield1971}{}}%
-Oldfield, R. C. (1971). The assessment and analysis of handedness: The {Edinburgh} inventory. \emph{Neuropsychologia}, \emph{9}(1), 97--113. \url{https://doi.org/10.1016/0028-3932(71)90067-4}
-
-\leavevmode\vadjust pre{\hypertarget{ref-olejnik2003}{}}%
-Olejnik, S., \& Algina, J.
-(2003).
-Generalized eta and omega squared statistics: Measures of effect size for some common research designs.
-\emph{Psychological Methods}, \emph{8}(4), 434--447.
-\url{https://doi.org/10.1037/1082-989X.8.4.434}
-
-\leavevmode\vadjust pre{\hypertarget{ref-pathania2019}{}}%
-Pathania, A., Leiker, A.
-M., Euler, M., Miller, M.
-W., \& Lohse, K.
-R.
-(2019).
-Challenge, motivation, and effort: {Neural} and behavioral correlates of self-control of difficulty during practice.
-\emph{Biological Psychology}, \emph{141}, 52--63.
-\url{https://doi.org/10.1016/j.biopsycho.2019.01.001}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-patchwork}{}}%
-Pedersen, T. L. (2020). \emph{Patchwork: The composer of plots}. \url{https://patchwork.data-imaginist.com/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-computees}{}}%
-Re, A. C. D. (2013). Compute.es: Compute effect sizes. In \emph{R Package}. \url{https://cran.r-project.org/package=compute.es}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-ryan1982}{}}%
-Ryan, R.
-M.
-(1982).
-Control and information in the intrapersonal sphere: {An} extension of cognitive evaluation theory.
-\emph{Journal of Personality and Social Psychology}, \emph{43}(3), 450--461.
-\url{https://doi.org/10.1037/0022-3514.43.3.450}
-
-\leavevmode\vadjust pre{\hypertarget{ref-salmoni1984}{}}%
-Salmoni, A.
-W., Schmidt, R.
-A., \& Walter, C.
-B.
-(1984).
-Knowledge of results and motor learning: A review and critical reappraisal.
-\emph{Psychological Bulletin}, \emph{95}(3), 355--386.
-\url{https://doi.org/10.1037/0033-2909.95.3.355}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sanli2013}{}}%
-Sanli, E.
-A., Patterson, J.
-T., Bray, S.
-R., \& Lee, T.
-D.
-(2013).
-Understanding self-controlled motor learning protocols through the self-determination theory.
-\emph{Frontiers in Psychology}, \emph{3}.
-\url{https://doi.org/10.3389/fpsyg.2012.00611}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schuirmann1987}{}}%
-Schuirmann, D.
-J.
-(1987).
-A comparison of the Two One-Sided Tests Procedure and the Power Approach for assessing the equivalence of average bioavailability.
-\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680.
-\url{https://doi.org/10.1007/BF01068419}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherwood1996}{}}%
-Sherwood, D.
-E.
-(1996).
-The benefits of random variable practice for spatial accuracy and error detection in a rapid aiming task.
-\emph{Research Quarterly for Exercise and Sport}, \emph{67}(1), 35--43.
-\url{https://doi.org/10.1080/02701367.1996.10607923}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherwood2009}{}}%
-Sherwood, D. E. (2009). Spatial error detection in rapid unimanual and bimanual aiming movements. \emph{Perceptual and Motor Skills}, \emph{108}(1), 3--14. \url{https://doi.org/10.2466/PMS.108.1.3-14}
-
-\leavevmode\vadjust pre{\hypertarget{ref-sigrist2013}{}}%
-Sigrist, R., Rauter, G., Riener, R., \& Wolf, P.
-(2013).
-Augmented visual, auditory, haptic, and multimodal feedback in motor learning: A review.
-\emph{Psychonomic Bulletin \& Review}, \emph{20}(1), 21--53.
-\url{https://doi.org/10.3758/s13423-012-0333-8}
-
-\leavevmode\vadjust pre{\hypertarget{ref-simmons2012}{}}%
-Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 Word Solution}. \url{https://doi.org/10.2139/ssrn.2160588}
-
-\leavevmode\vadjust pre{\hypertarget{ref-simmons2011}{}}%
-Simmons, J.
-P., Nelson, L.
-D., \& Simonsohn, U.
-(2011).
-False-positive psychology: Undisclosed flexibility in data collection and analysis allows presenting anything as significant.
-\emph{Psychological Science}, \emph{22}(11), 1359--1366.
-\url{https://doi.org/10.1177/0956797611417632}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-afex}{}}%
-Singmann, H., Bolker, B., Westfall, J., Aust, F., \& Ben-Shachar, M. S. (2021). \emph{Afex: Analysis of factorial experiments}. \url{https://CRAN.R-project.org/package=afex}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stgermain2022}{}}%
-St Germain, L., Williams, A., Balbaa, N., Poskus, A., Leshchyshen, O., Lohse, K.
-R., \& Carter, M.
-J.
-(in-press).
-Increased perceptions of autonomy through choice fail to enhance motor skill retention.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}.
-In-press.
-\url{https://doi.org/10.1037/xhp0000992}
-
-\leavevmode\vadjust pre{\hypertarget{ref-stemarie2019}{}}%
-Ste-Marie, D.
-M., Carter, M.
-J., \& Yantha, Z.
-D.
-(2020).
-Self-controlled learning: {Current} findings, theoretical perspectives, and future directions.
-In \emph{Skill acquisition in sport: Research, theory and practice} (3rd ed.).
-{Routledge}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-metafor}{}}%
-Viechtbauer, W. (2010). Conducting meta-analyses in {R} with the {metafor} package. \emph{Journal of Statistical Software}, \emph{36}(3), 1--48. \url{https://doi.org/10.18637/jss.v036.i03}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., Grolemund, G., Hayes, A., Henry, L., Hester, J., Kuhn, M., Pedersen, T.
-L., Miller, E., Bache, S.
-M., Müller, K., Ooms, J., Robinson, D., Seidel, D.
-P., Spinu, V., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
 \leavevmode\vadjust pre{\hypertarget{ref-wilcox2021}{}}%
 Wilcox, R. R. (2021). \emph{Introduction to robust estimation and hypothesis testing} (5th ed.). Academic press.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woodard2020}{}}%
-Woodard, K.
-F., \& Fairbrother, J.
-T.
-(2020).
-Cognitive loading during and after continuous task execution alters the effects of self-controlled knowledge of results.
-\emph{Frontiers in Psychology}, \emph{11}.
-\url{https://doi.org/10.3389/fpsyg.2020.01046}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wulf2014}{}}%
-Wulf, G., Freitas, H.
-E., \& Tandy, R.
-D.
-(2014).
-Choosing to exercise more: {Small} choices increase exercise engagement.
-\emph{Psychology of Sport and Exercise}, \emph{15}(3), 268--271.
-\url{https://doi.org/10.1016/j.psychsport.2014.01.007}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wulf2018}{}}%
-Wulf, G., Iwatsuki, T., Machin, B., Kellogg, J., Copeland, C., \& Lewthwaite, R.
-(2018).
-Lassoing skill through learner choice.
-\emph{Journal of Motor Behavior}, \emph{50}(3), 285--292.
-\url{https://doi.org/10.1080/00222895.2017.1341378}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wulf2016}{}}%
-Wulf, G., \& Lewthwaite, R.
-(2016).
-Optimizing performance through intrinsic motivation and attention for learning: {The} {OPTIMAL} theory of motor learning.
-\emph{Psychonomic Bulletin \& Review}, \emph{23}(5), 1382--1414.
-\url{https://doi.org/10.3758/s13423-015-0999-9}
-
-\leavevmode\vadjust pre{\hypertarget{ref-yantha2021}{}}%
-Yantha, Z.
-D., McKay, B., \& Ste-Marie, D.
-M.
-(in-press).
-The recommendation for learners to be provided with control over their feedback schedule is questioned in a self-controlled learning paradigm.
-\emph{Journal of Sports Sciences}, 1--14.
-https://doi.org/\url{https://doi.org/10.1080/02640414.2021.2015945}
-
-\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
-Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. \url{https://CRAN.R-project.org/package=kableExtra}
 

### 2022-05-05 scripts/libraries.R

@@ -1,0 +1,29 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Required libraries
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: April 04 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+# SCRIPT SETUP ----
+#
+# REQUIRED LIBRARIES
+#
+library(afex)
+library(compute.es)
+library(Cronbach)
+library(ggResidpanel)
+library(metafor)
+library(patchwork)
+library(rogme)
+library(tidyverse)

### 2022-05-05 scripts/main_figs.R

@@ -1,0 +1,541 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Manuscript - Figures
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: March 29 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+# SCRIPT SETUP ----
+#
+# Required files and tibbles
+source("scripts/main_wrangle.R")
+
+# Color and theme setup
+color_expt1 <- c("#5e81ac","#88c0d0", "#bf616a", "#d08770")
+color_expt2 <- c("#a3be8c", "#b48ead")
+
+theme_set(
+  theme_classic() +
+    theme(
+      axis.title = element_text(size = 14, face = "bold"),
+      axis.text = element_text(size = 12, face = "bold")
+    )
+)
+
+
+# FIGURE 2 ----
+#
+# Experiment 1
+#
+# Bind tibbles together
+expt1_9blocks_g <- dplyr::bind_rows(
+  expt1_performance_acq_g,
+  expt1_performance_prt_g
+)
+
+expt1_9blocks_g <- expt1_9blocks_g %>%
+  dplyr::mutate(
+    phase_id = dplyr::case_when(
+      block_id == 1 ~ "pre",
+      block_id %in% c(2:7) ~ "acq",
+      block_id == 8 ~ "ret",
+      block_id == 9 ~ "trn"
+    )
+  )
+
+# Fig 2a - Spatial total error (E) for all phases
+fig2a <- ggplot2::ggplot(
+  expt1_9blocks_g,
+  aes(x = block_id,
+      y = g_mean_e_deg,
+      group = interaction(group_id, phase_id),
+      colour = group_id)) +
+  geom_line(aes(linetype = group_id,
+                group = interaction(group_id, phase_id)),
+            show.legend = FALSE,
+            position = position_dodge(0.6)) +
+  geom_pointrange(aes(ymin = ci_low_deg,
+                      ymax = ci_upp_deg,
+                      shape = group_id),
+                  size = 0.5,
+                  position = position_dodge(0.6)) +
+  scale_x_discrete(name = NULL) +
+  scale_y_continuous(name = "Spatial E (deg)",
[…]

### 2022-05-05 scripts/main_wrangle.R

@@ -1,0 +1,458 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Manuscript - Data wrangling
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: March 30 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+
+# SCRIPT SETUP ----
+#
+# Required libraries
+source("scripts/libraries.R")
+
+# Seed for reproducible bootstrapped confidence intervals
+set.seed(8693)
+
+# Load data files
+expt1_performance_data <- readr::read_csv("data/expt1_performance-data.csv")
+expt1_qaire_data <- readr::read_csv("data/expt1_qaire-data.csv")
+expt1_cronbach_data <- readr::read_csv("data/expt1_cronbach.csv")
+
+expt2_performance_data <- readr::read_csv("data/expt2_performance-data.csv")
+expt2_qaire_data <- readr::read_csv("data/expt2_qaire-data.csv")
+expt2_cronbach_data <- readr::read_csv("data/expt2_cronbach.csv")
+
+
+# DATA SETUP ----
+#
+# Create tibbles to work with
+#
+# EXPERIMENT 1
+#
+# PERFORMANCE DATA
+#
+# Add columns for choice, feedback, blocks, and ce^2. For blocks, we will
+# collapse across the two different pre-tests for now.
+expt1_performance_tib <- expt1_performance_data %>%
+  dplyr::mutate(choice_id = dplyr::if_else(group_id <= 2, 1, 2)) %>%
+  dplyr::mutate(fb_id = dplyr::if_else(group_id %in% c(1, 3), 1, 2)) %>%
+  dplyr::mutate(block_id = rep(rep(1:9, each = 12), 152)) %>%
+  dplyr::mutate(ce2_deg = dplyr::if_else(phase_id != 4, (xi_deg - 40)^2,
[…]

### 2022-05-05 scripts/supplementary-a.R

@@ -1,0 +1,977 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Supplementary A (Error estimation) - Wrangle, analyses, and figures
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: April 28 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+
+# SCRIPT SETUP ----
+#
+# Required libraries
+source("scripts/libraries.R")
+
+# Seed for reproducible bootstrapped confidence intervals
+set.seed(8693)
+
+# Load data files
+expt1_estimation_data <- readr::read_csv("data/expt1_estimation-data.csv")
+expt2_estimation_data <- readr::read_csv("data/expt2_estimation-data.csv")
+
+# Function to calculate variable error (VE)
+ve <- function(x){
+  sd(x, na.rm = TRUE) * (sqrt((length(x) - 1) / length(x)))
+}
+
+
+# WRANGLE: DATA SETUP ----
+#
+# EXPERIMENT 1
+#
+# Add columns for choice, feedback, and constant error for each estimation and
+# actual performance for timing and spatial components
+expt1_estimation_tib <- expt1_estimation_data %>%
+  dplyr::mutate(choice_id = dplyr::if_else(group_id <= 2, 1, 2)) %>%
+  dplyr::mutate(fb_id = dplyr::if_else(group_id %in% c(1, 3), 1, 2)) %>%
+  dplyr::mutate(ce_deg = ee_deg - xi_deg) %>%
+  dplyr::mutate(ce_ms = ee_ms - xi_ms)
+
+# Make factors
+expt1_estimation_tib <- expt1_estimation_tib %>%
+  dplyr::mutate(
+    group_id = forcats::as_factor(group_id),
+    phase_id = forcats::as_factor(phase_id),
+    choice_id = forcats::as_factor(choice_id),
+    fb_id = forcats::as_factor(fb_id)
+  )
+
[…]

### 2022-05-05 scripts/supplementary-b.R

@@ -1,0 +1,529 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Supplementary B (Shift functions) - Wrangle, analyses, and figures
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: May 03 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+
+# SCRIPT SETUP ----
+#
+# Required libraries
+source("scripts/main_wrangle.R")
+
+
+# DATA SETUP ----
+#
+# EXPERIMENT 1
+#
+# Trimmed means
+expt1_prt_trim_p <- expt1_performance_tib %>%
+  dplyr::filter(phase_id != 2) %>%
+  dplyr::group_by(id, group_id, choice_id, fb_id, phase_id, block_id) %>%
+  dplyr::summarize(
+    n = n(),
+    p_tmean_e_deg = sqrt(mean(ce2_deg, trim = 0.2, na.rm = TRUE)),
+    p_tmean_e_ms = sqrt(mean(ce2_ms, trim = 0.2, na.rm = TRUE)),
+    .groups = "drop"
+  )
+
+# Spatial goal and wide format
+expt1_prt_trim_deg_wide_p <- expt1_prt_trim_p %>%
+  dplyr::select(id, choice_id, fb_id, block_id, p_tmean_e_deg) %>%
+  tidyr::pivot_wider(
+    names_from = block_id,
+    values_from = p_tmean_e_deg) %>%
+  # rename phases based on column number
+  dplyr::rename(pre = 4) %>%
+  dplyr::rename(ret = 5) %>%
+  dplyr::rename(trans = 6) %>%
+  # Create post-test score that collapses across ret and trans
+  dplyr::mutate(post = (ret + trans) / 2)
+
+# Spatial goal post-test choice versus yoked
+expt1_deg_choice <- expt1_prt_trim_deg_wide_p %>%
+  dplyr::select(id, choice_id, post) %>%
+  pivot_wider(
+    names_from = choice_id,
+    values_from = post)
+
[…]

### 2022-05-06 docs/preprint/supplementary.tex
update: fix fig caption error

@@
 Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
-Grey connected dots represent individual data for participants in each group.
-Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS1}
+Grey connected dots represent individual data for participants in each group.}\label{fig:figS1}
 \end{figure}
@@
 Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
-Grey connected dots represent individual data for participants in each group.}\label{fig:figS2}
+Grey connected dots represent individual data for participants in each group.
+Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS2}
 \end{figure}

### 2022-05-06 docs/submission/manuscript.Rmd
init

--- 2022-05-05 docs/preprint/manuscript.Rmd
@@
   \noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
-  \noindent Data and code: https://github.com/cartermaclab/expt_sc-feedback-characteristics \vspace{2ex} \newline
-  \noindent \textbf{Corresponding authors:} Michael J. Carter (michaelcarter@mcmaster.ca) and Laura St. Germain (stgerml@mcmaster.ca).
+
+  \noindent Data and code: https://github.com/cartermaclab/expt_sc-feedback-characteristics
+
+  \noindent \textbf{Corresponding authors:} Michael J. Carter (michaelcarter@mcmaster.ca) or Laura St. Germain (stgerml@mcmaster.ca)
 
@@
 keywords          : "Self-controlled, Knowledge of results, OPTIMAL theory, Retention"
-#wordcount         : "2978 for Introduction, Results, and Discussion"
+wordcount         : "2978 for Introduction, Results, and Discussion"
 
@@
 footnotelist      : no
-linenumbers       : no
+linenumbers       : yes
 mask              : no
@@
 documentclass     : "apa7"
-classoption       : "doc, donotrepeattitle"
+classoption       : "man, donotrepeattitle"
 #fontsize          : 11pt
@@
   - \usepackage{setspace}
- # - \pagewiselinenumbers
+  - \pagewiselinenumbers
   - \raggedbottom
@@
   - \renewcommand\affiliation[1]{}
-  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
-  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
+  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St.
+Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A.
+Cashaback, Michael J.
+Carter\vspace{2ex}}
+  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
 ---
@@
 
-```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "45%"}
-knitr::include_graphics("../../figs/fig1.pdf")
-```
-
-(ref:fig1-caption) \small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
-Trials began by informing participants the trial number (500 ms) they were on in acquisition.
-Shortly after, the text "Get Ready!" appeared on the screen and 800 ms later a visual go-signal was presented in the form of a green circle in the center of the screen.
-Participants began their movement when ready after seeing the visual go-signal as we were not interested in reaction time.
-While participants completed their rapid out-and-back movement, the computer screen was blank.
-Upon returning to the starting position, a red circle appeared in the center of the screen.
-A 2000 ms feedback delay interval was used and this interval was followed by the feedback prompt.
-The feedback prompt also displayed an updated counter representing the number of feedback trials they had left.
-If the number of remaining feedback trials matched the number of acquisition trials left, these trials automatically defaulted to feedback trials.
-On trials where feedback was not requested, a blank screen **(A)** was shown for 3000 ms.
-When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group.
-The error feedback group **(B)** saw their constant error, the graded feedback group **(C)** saw either "too far" or "too short" for the spatial goal and "too fast" or "too slow" for the timing goal, and the binary feedback group **(D)** saw either "hit" or "miss" for the task goals.
-The sequence of events was the same for the yoked groups with the exception they did not see a feedback prompt.
-The sequence of events was similar in pre-test, retention, and transfer except all trials were no-feedback trials.
-
 A typical acquisition trial (see Figure \@ref(fig:fig1)) began with the current trial number displayed (500 ms), followed by a visual "Get Ready!" and a visual go-signal (800 ms apart).
@@
 Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
+
+```{r fig1, echo = FALSE, fig.cap = "(ref:fig1-caption)", fig.align = "center", out.height = "45%"}
+knitr::include_graphics("../../figs/fig1.pdf")
+```
+
+(ref:fig1-caption) \small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
+Trials began by informing participants the trial number (500 ms) they were on in acquisition.
+Shortly after, the text "Get Ready!" appeared on the screen and 800 ms later a visual go-signal was presented in the form of a green circle in the center of the screen.
+Participants began their movement when ready after seeing the visual go-signal as we were not interested in reaction time.
+While participants completed their rapid out-and-back movement, the computer screen was blank.
+Upon returning to the starting position, a red circle appeared in the center of the screen.
+A 2000 ms feedback delay interval was used and this interval was followed by the feedback prompt.
+The feedback prompt also displayed an updated counter representing the number of feedback trials they had left.
+If the number of remaining feedback trials matched the number of acquisition trials left, these trials automatically defaulted to feedback trials.
+On trials where feedback was not requested, a blank screen **(A)** was shown for 3000 ms.
+When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group.
+The error feedback group **(B)** saw their constant error, the graded feedback group **(C)** saw either "too far" or "too short" for the spatial goal and "too fast" or "too slow" for the timing goal, and the binary feedback group **(D)** saw either "hit" or "miss" for the task goals.
+The sequence of events was the same for the yoked groups with the exception they did not see a feedback prompt.
+The sequence of events was similar in pre-test, retention, and transfer except all trials were no-feedback trials.
 
@@
 
-\vspace{4ex}
+## Acquisition
+
+### Experiment 1
+
+All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
+\@ref(fig:fig2)A).
+This was supported by a significant main effect of Block, $F(2.41,357.13) = 60.18$, $p < .001$, $\eta_{G}^2 = .130$, where block 1 was less accurate than all other blocks ($p$'s $< .001$), block 2 was less accurate than all subsequent blocks ($p$'s $\leq .021$), and blocks 3 and 4 were more errorful than block 6 ($p$'s $\leq .015$).
+Timing error also decreased during the acquisition period (Fig.
+\@ref(fig:fig2)B).
+The significant main effect of Block, $F(1.75,259.59) = 55.44$, $p < .001$, $\eta_{G}^2 = .138$, was superseded by a significant Feedback x Block interaction, $F(1.75, 259.59) = 3.56$, $p = .035$, $\eta_{G}^2 = .010$.
+Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks ($p$'s $< .001$), but performance plateaued from block 2 onward in acquisition ($p$'s $\geq .257$).
+Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks ($p$'s $< .001$); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 ($p$'s $\leq .028$).
+
+\vspace{2ex}
 
@@
 
-<!-- \vspace{2ex} -->
+### Experiment 2
+
+Spatial (Fig.
+\@ref(fig:fig3)A) and timing (Fig.
+\@ref(fig:fig3)B) error remained relatively flat from block 1 to block 6 in the acquisition period.
+None of the main effects or interactions for either task goals were significant.
+
+\vspace{2ex}
 
@@
 Dots represent individual data points.
-
-\newpage
-
-## Acquisition
-
-### Experiment 1
-
-All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
-\@ref(fig:fig2)A).
-This was supported by a significant main effect of Block, $F(2.41,357.13) = 60.18$, $p < .001$, $\eta_{G}^2 = .130$, where block 1 was less accurate than all other blocks ($p$'s $< .001$), block 2 was less accurate than all subsequent blocks ($p$'s $\leq .021$), and blocks 3 and 4 were more errorful than block 6 ($p$'s $\leq .015$).
-Timing error also decreased during the acquisition period (Fig.
-\@ref(fig:fig2)B).
-The significant main effect of Block, $F(1.75,259.59) = 55.44$, $p < .001$, $\eta_{G}^2 = .138$, was superseded by a significant Feedback x Block interaction, $F(1.75, 259.59) = 3.56$, $p = .035$, $\eta_{G}^2 = .010$.
-Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks ($p$'s $< .001$), but performance plateaued from block 2 onward in acquisition ($p$'s $\geq .257$).
-Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks ($p$'s $< .001$); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 ($p$'s $\leq .028$).
-
-### Experiment 2
-
-Spatial (Fig.
-\@ref(fig:fig3)A) and timing (Fig.
-\@ref(fig:fig3)B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-None of the main effects or interactions for either task goals were significant.
 
@@
 
-\vspace{2.5ex}
+\vspace{10ex}
 
-# Funding
+# Declarations
 
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
+\noindent
+**Funding.** &nbsp;This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
 LSG was supported by an NSERC Postgraduate Scholarship.
@@
 
-# Conflicts of interest/Competing interests
+\noindent
+**Conflicts of interest/Competing interests.** &nbsp;None.
 
-None.
+\noindent
+**Ethics approval.** &nbsp;This project was approved and conducted in accordance with the approval of the McMaster University Research Ethics Board.
 
-# Availability of data, materials, and code
+\noindent
+**Consent to participate.** &nbsp;All participants gave informed consent.
 
-Can be accessed here: https://github.com/cartermaclab/expt_sc-feedback-characteristics.
+\noindent
+**Consent for publication.** &nbsp;All authors approve the manuscript.
 
-# Authors' contributions using CRediT
+\noindent
+**Availability of data, materials, and code.** &nbsp;Can be accessed here: https://github.com/cartermaclab/expt_sc-feedback-characteristics.
 
-Laura St.
+\noindent
+**Authors' contributions using CRediT.** &nbsp;Laura St.
 Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization.

### 2022-05-06 docs/submission/manuscript.tex
init

--- 2022-05-05 docs/preprint/manuscript.tex
@@
 \documentclass[
-  doc, donotrepeattitle,floatsintext]{apa7}
+  man, donotrepeattitle,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 {}{\PatchFailed}
-\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
+\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention\newline\indent Word count: 2978 for Introduction, Results, and Discussion}
+\usepackage{lineno}
+
+\linenumbers
 \usepackage{csquotes}
@@
 \usepackage{setspace}
+\pagewiselinenumbers
 \raggedbottom
@@
 \renewcommand\affiliation[1]{}
-\authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
-\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
+\authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
+\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
 \ifLuaTeX
@@
 \noindent \addORCIDlink{Michael J. Carter}{0000-0002-0675-4271}
-\noindent Data and code: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics} \vspace{2ex} \newline
+
+\noindent Data and code: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}
+
 \noindent \textbf{Corresponding authors:} Michael J.
-Carter (\href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}) and Laura St.~Germain (\href{mailto:stgerml@mcmaster.ca}{\nolinkurl{stgerml@mcmaster.ca}}).
+Carter (\href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}) or Laura St.~Germain (\href{mailto:stgerml@mcmaster.ca}{\nolinkurl{stgerml@mcmaster.ca}})
 
@@
 All participants were shown a sample feedback display that corresponded to their experimental group and were asked to interpret it aloud for the researcher to verify understanding.
+
+A typical acquisition trial (see Figure \ref{fig:fig1}) began with the current trial number displayed (500 ms), followed by a visual ``Get Ready!'' and a visual go-signal (800 ms apart).
+Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
+The computer screen was blank while participants made their movement.
+When participants returned to the starting position, a red circle was displayed on the monitor.
+Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
+If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.
+
+Before the retention and transfer tests, participants were reminded about the task and its associated goals.
+All participants were asked to estimate their performance after each trial in retention and transfer.
+After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.
+The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a).
+Cronbach's alpha values for each questionnaire at each time point are reported in Table \ref{tab:table1}.
+
+\hypertarget{experiment-2-1}{%
+\subsubsection{Experiment 2}\label{experiment-2-1}}
+
+Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 22.37 years, \(SD_{age}\) = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 18.00 years, \(SD_{age}\) = 0.93, 28 females).
+Binary feedback for the spatial goal was provided as ``hit'' if performance was exactly 40 degrees (or 60 degrees in transfer) and as ``miss'' for everything else.
+For the timing goal, binary feedback was provided as ``hit'' when performance was exactly 225 ms and as ``miss'' for everything else.
+Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
 
@@
 \end{figure}
-
-A typical acquisition trial (see Figure \ref{fig:fig1}) began with the current trial number displayed (500 ms), followed by a visual ``Get Ready!'' and a visual go-signal (800 ms apart).
-Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
-The computer screen was blank while participants made their movement.
-When participants returned to the starting position, a red circle was displayed on the monitor.
-Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.
-
-Before the retention and transfer tests, participants were reminded about the task and its associated goals.
-All participants were asked to estimate their performance after each trial in retention and transfer.
-After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.
-The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a).
-Cronbach's alpha values for each questionnaire at each time point are reported in Table \ref{tab:table1}.
-
-\hypertarget{experiment-2-1}{%
-\subsubsection{Experiment 2}\label{experiment-2-1}}
-
-Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 22.37 years, \(SD_{age}\) = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 18.00 years, \(SD_{age}\) = 0.93, 28 females).
-Binary feedback for the spatial goal was provided as ``hit'' if performance was exactly 40 degrees (or 60 degrees in transfer) and as ``miss'' for everything else.
-For the timing goal, binary feedback was provided as ``hit'' when performance was exactly 225 ms and as ``miss'' for everything else.
-Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
 
@@
 
-\vspace{4ex}
+\hypertarget{acquisition}{%
+\subsection{Acquisition}\label{acquisition}}
+
+\hypertarget{experiment-1-3}{%
+\subsubsection{Experiment 1}\label{experiment-1-3}}
+
+All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
+\ref{fig:fig2}A).
+This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)).
+Timing error also decreased during the acquisition period (Fig.
+\ref{fig:fig2}B).
+The significant main effect of Block, \(F(1.75,259.59) = 55.44\), \(p < .001\), \(\eta_{G}^2 = .138\), was superseded by a significant Feedback x Block interaction, \(F(1.75, 259.59) = 3.56\), \(p = .035\), \(\eta_{G}^2 = .010\).
+Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)), but performance plateaued from block 2 onward in acquisition (\(p\)'s \(\geq .257\)).
+Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).
+
+\vspace{2ex}
 
@@
 
+\hypertarget{experiment-2-3}{%
+\subsubsection{Experiment 2}\label{experiment-2-3}}
+
+Spatial (Fig.
+\ref{fig:fig3}A) and timing (Fig.
+\ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period.
+None of the main effects or interactions for either task goals were significant.
+
+\vspace{2ex}
+
 \begin{figure}
@@
 \end{figure}
-
-\newpage
-
-\hypertarget{acquisition}{%
-\subsection{Acquisition}\label{acquisition}}
-
-\hypertarget{experiment-1-3}{%
-\subsubsection{Experiment 1}\label{experiment-1-3}}
-
-All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
-\ref{fig:fig2}A).
-This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)).
-Timing error also decreased during the acquisition period (Fig.
-\ref{fig:fig2}B).
-The significant main effect of Block, \(F(1.75,259.59) = 55.44\), \(p < .001\), \(\eta_{G}^2 = .138\), was superseded by a significant Feedback x Block interaction, \(F(1.75, 259.59) = 3.56\), \(p = .035\), \(\eta_{G}^2 = .010\).
-Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)), but performance plateaued from block 2 onward in acquisition (\(p\)'s \(\geq .257\)).
-Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).
-
-\hypertarget{experiment-2-3}{%
-\subsubsection{Experiment 2}\label{experiment-2-3}}
-
-Spatial (Fig.
-\ref{fig:fig3}A) and timing (Fig.
-\ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-None of the main effects or interactions for either task goals were significant.
 
@@
 
-\vspace{2.5ex}
-
-\hypertarget{funding}{%
-\section{Funding}\label{funding}}
-
-This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
+\vspace{10ex}
+
+\hypertarget{declarations}{%
+\section{Declarations}\label{declarations}}
+
+\noindent
+\textbf{Funding.} ~This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
 LSG was supported by an NSERC Postgraduate Scholarship.
@@
 
-\hypertarget{conflicts-of-interestcompeting-interests}{%
-\section{Conflicts of interest/Competing interests}\label{conflicts-of-interestcompeting-interests}}
-
-None.
-
-\hypertarget{availability-of-data-materials-and-code}{%
-\section{Availability of data, materials, and code}\label{availability-of-data-materials-and-code}}
-
-Can be accessed here: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}.
-
-\hypertarget{authors-contributions-using-credit}{%
-\section{Authors' contributions using CRediT}\label{authors-contributions-using-credit}}
-
-Laura St.~Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization.
+\noindent
+\textbf{Conflicts of interest/Competing interests.} ~None.
+
+\noindent
+\textbf{Ethics approval.} ~This project was approved and conducted in accordance with the approval of the McMaster University Research Ethics Board.
+
+\noindent
+\textbf{Consent to participate.} ~All participants gave informed consent.
+
+\noindent
+\textbf{Consent for publication.} ~All authors approve the manuscript.
+
+\noindent
+\textbf{Availability of data, materials, and code.} ~Can be accessed here: \url{https://github.com/cartermaclab/expt_sc-feedback-characteristics}.
+
+\noindent
+\textbf{Authors' contributions using CRediT.} ~Laura St.~Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization.
 Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing.

### 2022-05-06 docs/submission/supplementary.Rmd
init

--- 2022-05-05 docs/preprint/supplementary.Rmd
@@
   - \usepackage{setspace}
-  #- \pagewiselinenumbers
+  - \pagewiselinenumbers
   - \raggedbottom
@@
 Grey connected dots represent individual data for participants in each group.
-Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.
 
@@
 Grey connected dots represent individual data for participants in each group.
+Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.
 

### 2022-08-14 scripts/supplementary-b.R
update: rename for new order; add analysis SuppB

@@ -3,14 +3,14 @@
 # -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
 # and Carter
 #
-# Supplementary B (Shift functions) - Wrangle, analyses, and figures
+# Supplementary B (Error estimation) - Wrangle, analyses, and figures
 #
 # Authors:
 #   Laura St. Germain
 #   Brad McKay
 #   Mike Carter
 #
-# Last update: May 03 2022
+# Last update: August 14 2022
 #
 # Website: https://www.cartermaclab.org
 # -------------------------------------------
@@ -19,511 +19,1121 @@
 # SCRIPT SETUP ----
 #
 # Required libraries
-source("scripts/main_wrangle.R")
+source("scripts/libraries.R")
+
+# Seed for reproducible bootstrapped confidence intervals
+set.seed(8693)
+
+# Load data files
+expt1_estimation_data <- readr::read_csv("data/expt1_estimation-data.csv")
+expt2_estimation_data <- readr::read_csv("data/expt2_estimation-data.csv")
+expt1_performance_est_data <- readr::read_csv("data/expt1_performance-data.csv")
+expt2_performance_est_data <- readr::read_csv("data/expt2_performance-data.csv")
+
+# Function to calculate variable error (VE)
+ve <- function(x){
+  sd(x, na.rm = TRUE) * (sqrt((length(x) - 1) / length(x)))
+}
 
 
-# DATA SETUP ----
+# WRANGLE: DATA SETUP ----
 #
 # EXPERIMENT 1
 #
-# Trimmed means
-expt1_prt_trim_p <- expt1_performance_tib %>%
-  dplyr::filter(phase_id != 2) %>%
-  dplyr::group_by(id, group_id, choice_id, fb_id, phase_id, block_id) %>%
+# Add columns for choice, feedback, and constant error for each estimation and
+# actual performance for timing and spatial components
+expt1_estimation_tib <- expt1_estimation_data %>%
+  dplyr::mutate(choice_id = dplyr::if_else(group_id <= 2, 1, 2)) %>%
+  dplyr::mutate(fb_id = dplyr::if_else(group_id %in% c(1, 3), 1, 2)) %>%
[…]

### 2022-08-14 scripts/supplementary-c.R
init

@@ -1,0 +1,376 @@
+# -------------------------------------------
+# CHOICE AND FEEDBACK CHARACTERISTICS PROJECT
+# -- St. Germain, McKay, Poskus, Williams, Leshchyshen, Feldman, Cashaback,
+# and Carter
+#
+# Supplementary C (Questionnaire) - Wrangle and analyses
+#
+# Authors:
+#   Laura St. Germain
+#   Brad McKay
+#   Mike Carter
+#
+# Last update: August 13 2022
+#
+# Website: https://www.cartermaclab.org
+# -------------------------------------------
+
+
+# SCRIPT SETUP ----
+#
+# Required libraries
+source("scripts/main_wrangle.R")
+
+# Seed for reproducible bootstrapped confidence intervals
+set.seed(8693)
+
+
+# WRANGLE: DATA SETUP ----
+#
+# EXPERIMENT 1
+#
+# Create tibbles to work with. Collapse across feedback to get mean and SD
+# for choice and yoked
+#
+# Perceived autonomy
+expt1_qaire_choice_pa_g <- expt1_qaire_pa_p %>%
+  dplyr::group_by(choice_id, time_id) %>%
+  dplyr::summarise(
+    mean_rating = mean(score, na.rm = TRUE),
+    sd_rating = sd(score, na.rm = TRUE)
+  )
+
+# Perceived competence
+expt1_qaire_choice_pc_g <- expt1_qaire_pc_p %>%
+  dplyr::group_by(choice_id, time_id) %>%
+  dplyr::summarise(
+    mean_rating = mean(score, na.rm = TRUE),
+    sd_rating = sd(score, na.rm = TRUE)
+  )
+
+# Intrinsic motivation
+expt1_qaire_choice_im_g <- expt1_qaire_im_p %>%
+  dplyr::group_by(choice_id, time_id) %>%
+  dplyr::summarise(
+    mean_rating = mean(score, na.rm = TRUE),
+    sd_rating = sd(score, na.rm = TRUE)
+  )
+
+
+# EXPERIMENT 2
+#
[…]

### 2022-08-14 scripts/main_wrangle.R
update: addressing reviewer comments

@@ -10,7 +10,7 @@
 #   Brad McKay
 #   Mike Carter
 #
-# Last update: March 30 2022
+# Last update: August 10 2022
 #
 # Website: https://www.cartermaclab.org
 # -------------------------------------------
@@ -109,6 +109,44 @@ expt1_performance_acq_g <- expt1_performance_acq_p %>%
     ci_low_ms = ggplot2::mean_cl_boot(p_mean_e_ms)$ymin,
     ci_upp_ms = ggplot2::mean_cl_boot(p_mean_e_ms)$ymax,
     .groups = "drop"
+  )
+
+# Number of hits during acquisition at the participant (p) and group (g) levels
+expt1_deg_hit_p <- expt1_performance_tib %>%
+  dplyr::filter(phase_id == 2) %>%
+  dplyr::mutate(hit = dplyr::if_else(
+    xi_deg > 39.99 & xi_deg < 40.01, 1, 0)) %>%
+  dplyr::group_by(id, group_id) %>%
+  dplyr::summarize(
+    n = n(),
+    sum_hit = sum(hit, na.rm = TRUE)
+  )
+
+expt1_deg_hit_g <- expt1_deg_hit_p %>%
+  dplyr::group_by(group_id) %>%
+  dplyr::summarize(
+    n = n(),
+    total = sum(sum_hit, na.rm = TRUE),
+    min = min(sum_hit, na.rm = TRUE),
+    max = max(sum_hit, na.rm = TRUE)
+  )
+
+expt1_ms_hit_p <- expt1_performance_tib %>%
+  dplyr::filter(phase_id == 2) %>%
+  dplyr::mutate(hit = dplyr::if_else(xi_ms == 225, 1, 0)) %>%
+  dplyr::group_by(id, group_id) %>%
+  dplyr::summarize(
+    n = n(),
+    sum_hit = sum(hit, na.rm = TRUE)
+  )
+
+expt1_ms_hit_g <- expt1_ms_hit_p %>%
+  dplyr::group_by(group_id) %>%
+  dplyr::summarize(
+    n = n(),
+    total = sum(sum_hit, na.rm = TRUE),
+    min = min(sum_hit, na.rm = TRUE),
+    max = max(sum_hit, na.rm = TRUE)
   )
 
 # QUESTIONNAIRE DATA
[…]

### 2022-08-14 docs/revision-1/r1_supplementary.Rmd
init

--- 2022-05-05 docs/preprint/supplementary.Rmd
@@
   - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+  - \renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
 ---
@@
 library("papaja")
+library(kableExtra)
+library(tidyverse)
 ```
@@
 # Supplementary A
-
-We asked all participants to estimate their performance on the spatial (Fig.
-\@ref(fig:figS1)) and timing (Fig.
-\@ref(fig:figS2)) components of the motor task after each trial in retention and transfer, similar to past research [e.g., @barros2019; @carter2012; @carter2014].
-Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown).
-To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial.
-Next, we computed total estimation error (EE) using the equation:
-\begin{equation}
-EE = \sqrt{CE^2 + VE^2}
-\end{equation}
-where $CE$ was the average estimation bias and $VE$ was the standard deviation of these errors. This approach is consistent with that used by @bruechert2003.
-
-## Error estimation in retention and transfer
-
-Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig.
-\@ref(fig:figS1)) and timing (Fig.
-\@ref(fig:figS2)) domains in Experiments 1 and 2.
-For the spatial estimation error, we found a significant main effect of Test in Experiment 1, $F(1,148) = 32.40$, $p < .001$, $\eta_{G}^2 = .060$, and in Experiment 2, $F(1,74) = 18.79$, $p < .001$, $\eta_{G}^2 = .026$, with more accurate estimations in retention than transfer.
-Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, $F(1,148) = 7.12$, $p = .008$, $\eta_{G}^2 < .001$, we did not decompose the interaction as the effect size estimate was less than $.001$.
-There were no significant main effects or interactions for timing estimation error in Experiment 2.
-A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed.
-Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.
-
-```{r figS1, echo = FALSE, fig.cap = "(ref:figS1-caption)", fig.align = "center"}
-knitr::include_graphics("../../figs/figS1.pdf")
-```
-
-(ref:figS1-caption) \small \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 **(A)** and Experiment 2 **(B)**.
-The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
-Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
-Grey connected dots represent individual data for participants in each group.
-Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.
-
-```{r figS2, echo = FALSE, fig.cap = "(ref:figS2-caption)", fig.align = "center"}
-knitr::include_graphics("../../figs/figS2.pdf")
-```
-
-(ref:figS2-caption) \small \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 **(A)** and Experiment 2 **(B)**.
-The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
-Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
-Grey connected dots represent individual data for participants in each group.
-
-## Development of error estimation skills
-
-In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment.
-We found significant main effects of Test for both the spatial, $F(1.45,104.67) = 20.72$, $p < .001$, $\eta_{G}^2 = .144$, and timing, $F(1.10,79.40) = 46.88$, $p < .001$, $\eta_{G}^2 = .060$, error estimations.
-For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer ($p$'s < .001), and transfer had higher error than retention ($p$ < .001).
-Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test ($p$'s < .001).
-In Experiment 2, none of the main effects or interactions were significant.
-
-\newpage
-
-# Supplementary B
 
@@
 For Experiment 1, the 95% confidence intervals overlapped with zero at each decile when comparing the choice and yoked groups for both the spatial (Fig.
-\@ref(fig:figS3)A) and timing (Fig.
-\@ref(fig:figS3)B) goals.
+\@ref(fig:figS1)A) and timing (Fig.
+\@ref(fig:figS2)A) goals.
 Similarly, in Experiment 2 there were no significant differences between the choice and yoked groups in any decile for the spatial (Fig.
-\@ref(fig:figS3)C) and timing (Fig.
-\@ref(fig:figS3)D) goals.
+\@ref(fig:figS1)B) and timing (Fig.
+\@ref(fig:figS2)B) goals.
 The results from these shift function analyses are consistent with the analyses reported in the main manuscript and a recent meta-analysis [@mckay2021], suggesting that giving learners choice during practice is not advantageous for motor learning.
 
-```{r figS3, echo = FALSE, fig.cap = "(ref:figS3-caption)", fig.align = "center"}
-knitr::include_graphics("../../figs/figS3.pdf")
+```{r figS1, echo = FALSE, fig.cap = "(ref:figS1-caption)", fig.align = "center"}
+knitr::include_graphics("../../figs/figS1.pdf")
 ```
 
-(ref:figS3-caption) \small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) spatial E (deg) shift function.} The top row illustrates scatter plots of individual mean spatial E for each group in Experiment 1 **(A)** and Experiment 2 **(B)**.
+(ref:figS1-caption) \small \normalfont \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) spatial E (deg) shift function.} The top row illustrates scatter plots of individual mean spatial E for each group in Experiment 1 **(A)** and Experiment 2 **(B)**.
 The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines.
@@
 
-```{r figS4, echo = FALSE, fig.cap = "(ref:figS4-caption)", fig.align = "center"}
-knitr::include_graphics("../../figs/figS4.pdf")
+```{r figS2, echo = FALSE, fig.cap = "(ref:figS2-caption)", fig.align = "center"}
+knitr::include_graphics("../../figs/figS2.pdf")
 ```
 
-(ref:figS4-caption) \small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 **(A)** and Experiment 2 **(B)**.
+(ref:figS2-caption) \small \normalfont \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 **(A)** and Experiment 2 **(B)**.
 The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines.
@@
 
-\newpage
+\clearpage
+
+# Supplementary B
+
+We asked all participants to estimate their performance on the spatial (Fig.
+\@ref(fig:figS3)) and timing (Fig.
+\@ref(fig:figS4)) components of the motor task after each trial in retention and transfer, similar to past research [e.g., @barros2019; @carter2012; @carter2014].
+Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown).
+To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial.
+Next, we computed total estimation error (EE) using the equation:
+\begin{equation}
+EE = \sqrt{CE^2 + VE^2}
+\end{equation}
+where $CE$ was the average estimation bias and $VE$ was the standard deviation of these errors. This approach is consistent with that used by @bruechert2003.
+
+## Error estimation in retention and transfer
+
+Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig.
+\@ref(fig:figS3)) and timing (Fig.
+\@ref(fig:figS4)) domains in Experiments 1 and 2.
+For the spatial estimation error, we found a significant main effect of Test in Experiment 1, $F(1,148) = 32.40$, $p < .001$, $\eta_{G}^2 = .060$, and in Experiment 2, $F(1,74) = 18.79$, $p < .001$, $\eta_{G}^2 = .026$, with more accurate estimations in retention than transfer.
+Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, $F(1,148) = 7.12$, $p = .008$, $\eta_{G}^2 < .001$, we did not decompose the interaction as the effect size estimate was less than $.001$.
+There were no significant main effects or interactions for timing estimation error in Experiment 2.
+A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed.
+Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.
+
+\clearpage
+
+```{r figS3, echo = FALSE, fig.cap = "(ref:figS3-caption)", fig.align = "center"}
+knitr::include_graphics("../../figs/figS3.pdf")
+```
+
+(ref:figS3-caption) \small \normalfont \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 **(A)** and Experiment 2 **(B)**.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.
+
+```{r figS4, echo = FALSE, fig.cap = "(ref:figS4-caption)", fig.align = "center"}
+knitr::include_graphics("../../figs/figS4.pdf")
+```
+
+(ref:figS4-caption) \small \normalfont \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 **(A)** and Experiment 2 **(B)**.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.
+Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.
+
+\clearpage
+
+## Development of error estimation skills
+
+In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment.
+We found significant main effects of Test for both the spatial, $F(1.45,104.67) = 20.72$, $p < .001$, $\eta_{G}^2 = .144$, and timing, $F(1.10,79.40) = 46.88$, $p < .001$, $\eta_{G}^2 = .060$, error estimations.
+For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer ($p$'s < .001), and transfer had higher error than retention ($p$ < .001).
+Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test ($p$'s < .001).
+In Experiment 2, none of the main effects or interactions were significant.
+
+## Performance accuracy of estimators versus non-estimators
+
+\textcolor{blue}{We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not.
+Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment.
+None of the main effect or interactions were significant in Experiment 1 or Experiment 2.
+A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation} [@guadagnoli2001]\textcolor{blue}{.
+Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation} [e.g., @chiviacowsky2005].
+\textcolor{blue}{Given recent support for this idea} [@bacelar2022]\textcolor{blue}{, it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.}
+
+\clearpage
+
+# Supplementary C
+
+\textcolor{blue}{Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity.
+Equivalence tests can be used to null findings more informative} [@harms2018; @lakens2017; @schuirmann1987]\textcolor{blue}{; however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons.
+First, we did not specify an \emph{a priori} smallest effect size of interest for any of the psychological constructs.
+Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol.
+Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points.
+We instead report mean differences and 90\% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments.
+The present experiments can be considered inconsistent with all effects larger than $g = \pm$ the largest absolute confidence interval bound presented in} Table \@ref(tab:tableS1).
+
+\vspace{1em}
+
+<!-- \begin{landscape} -->
+
+```{r tableS1, echo = FALSE, results = "asis"}
+tableS1 <- tibble::tibble(
+    c1 = c("Perceived autonomy",
+           "Perceived competence",
+           "Intrinsic motivation",
+           "Perceived autonomy",
+           "Perceived competence",
+           "Intrinsic motivation"),
+    c2 = c(".10",
+           ".07",
+           ".27",
+           "-.02",
+           ".12",
+           "-.31"),
+    c3 = c("[-.17, .36]",
+           "[-.19, .34]",
+           "[0, .54]",
+           "[-.29, .24]",
+           "[-.15, .38]",
+           "[-.58, -.04]"),
+    c4 = c(".22",
+           ".10",
+           ".20",
+           ".12",
+           "-.08",
+           "-.22"),
+    c5 = c("[-.05, .49]",
+           "[-.17, .36]",
+           "[-.07, .46]",
+           "[-.15, .39]",
+           "[-.35, .18]",
+           "[-.48, .05]"),
+    c6 = c(".32",
+           "-.12",
+           ".17",
+           ".15",
+           ".22",
+           "-.20"),
+    c7 = c("[.05, .59]",
+           "[-.38, .15]",
+           "[-.09, .44]",
+           "[-.11, .42]",
+           "[-.05, .49]",
+           "[-.46, .07]"),
+    c8 = c(".28",
+           "-.11",
+           ".15",
+           "-.03",
+           ".10",
+           "-.17"),
+    c9 = c("[.01, .55]",
+           "[-.37, .16]",
+           "[-.11, .42]",
+           "[-.30, .23]",
+           "[-.16, .37]",
+           "[-.43, .10]"),
+)
+tableS1 %>%
+  kbl(position = "h!",
+      booktabs = TRUE,
+      linesep = "\\addlinespace",
+      caption = "Effect sizes for each questionnaire at each timepoint.",
+      col.names = c("Questionnaire",
+                    "$g$",
+                    "90\\% CI",
+                    "$g$",
+                    "90\\% CI",
+                    "$g$",
+                    "90\\% CI",
+                    "$g$",
+                    "90\\% CI"),
+      escape = FALSE
+  ) %>%
+  kable_styling(position = "left",
+                font_size = 11,
+                latex_options = "scale_down") %>%
+  column_spec(1, width = "11em") %>%
+  column_spec(2, width = "2em") %>%
+  column_spec(3, width = "5em") %>%
+  column_spec(4, width = "2em") %>%
+  column_spec(5, width = "5em") %>%
+  column_spec(6, width = "2em") %>%
+  column_spec(7, width = "5em") %>%
+  column_spec(8, width = "2em") %>%
+  column_spec(9, width = "5em") %>% 
+  add_header_above(c(" ",
+                     "After pre-test" = 2,
+                     "After block 1" = 2,
+                     "After block 6" = 2,
+                     "Before retention" = 2)) %>%
+  pack_rows("Experiment 1", 1, 3) %>%
+  pack_rows("Experiment 2", 4, 6) %>%
+  footnote(general = "Block 1 and 6 are from the acquisition phase. Negative values favor yoked group.",
+           general_title = "Note.",
+           title_format = "italic",
+           footnote_as_chunk = TRUE
+           )
+```
+
+<!-- \end{landscape} -->
+
+\clearpage
 

### 2022-08-14 docs/revision-1/r1_response-to-reviewers.Rmd
init

---
title       : "Exercising choice over feedback schedules during practice is not advantageous for motor learning"
authors     : "Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback & Michael J. Carter"
journal     : "Psychonomic Bulletin & Review"
manuscript  : "PBR-BR-22-135"

bibliography      : "../references.bib"

class       : "final" # or final which removes all progress labels
output      : papaja::revision_letter_pdf
# output:
#   papaja::revision_letter_pdf:
#     latex_engine: xelatex

header-includes:
  - \usepackage[sfdefault,condensed]{roboto}
  - \usepackage[T1]{fontenc}
---

Melody Wiseheart, PhD  
Action Editor, _`r rmarkdown::metadata$journal`_

Dear Dr. Wiseheart,

Thank you for overseeing the review of our manuscript for publication in _`r rmarkdown::metadata$journal`_. We appreciate the positive and helpful comments from the Reviewers. Below we provide our point-by-point response (in normal font) to the Reviewers' comments (in ***bold-italic***). All substantial changes in the revised manuscript are included in this response letter (in a text box) and appear in \textcolor{blue}{blue} text in the revised manuscript.

Based on comments from all of the Reviewers, we have made our rationale for Experiment 2 more clear in the Introduction. Although the Reviewers made suggestions ranging from combining the two experiments to removing Experiment 2 altogether, we elected to keep it as Experiment 2. Doing so ensures transparency in our reporting practices as our decision to conduct Experiment 2 was made after we had analyzed the data for Experiment 1. Additionally, it is important to not censor null results in this area of motor learning research given the recent meta-analysis on this topic revealed the supposed self-controlled learning advantage resulted from publication bias rather than being a real effect [@mckay2021]. Reviewer 3 made several suggestions for additional analyses; however, we did not include some of them in the revision. Our primary reason for this decision was that the analysis suggestions were about understanding the information-processing explanation of self-controlled learning advantages. Yet, a key discussion point and conclusion based on our experiments is that there is no self-controlled learning advantage; a conclusion that is consistent with the @mckay2021 meta-analysis and several recent well-powered (and often pre-registered) experiments. We contend contextualizing our results within this current information negates the usefulness of additional analyses related to the information-processing (or motivational) perspective. We elaborate on these decisions in the point-by-point reply.

I would like to draw your attention to a change in the revised submission regarding our Supplementary documents. In our revision, the sensitivity analyses are now Supplementary A (were B in the original submission) and the error estimation data are now Supplementary B (were A in the original submission). To incorporate suggestions from the Reviewers, we have added Supplementary C which contains information related to the equivalence analyses on the psychological data. Thank you again for considering our work and overseeing the review process.

Sincerely,

Michael J. Carter

\Done

# Reviewer \#1

\RC{\emph{The authors present a well-designed investigation into self-control of feedback effects on motor skill learning. With N=228 participants assigned to self-controlled or yoked groups (crossed with feedback of differing quality: binary, graded, continuous), this is the largest study to date on the topic that I am aware of, and well-powered to test the a priori hypotheses. On the whole, I think the study is methodologically sound and of great interest to the motor learning community. That said, I do have some concerns about the structure of the manuscript, the use of equivalence tests, the interpretation of some of the data, which I detail below.}}

Thank you for the positive comments about our manuscript.

\Done

\RC{\emph{Validity of "Experiment 2". Given the lack of a learning effect in Experiment 2, I am not sure what this experiment really adds to the literature, nor do I think the self-control effect should be included in meta-analytic estimates moving forward (e.g., in this paper on p. 17, g=0.05, or in other future papers). In essence, the self-control of feedback is thought to moderate the learning effect, but with binary feedback there was no learning effect to begin with. Thus, it would be erroneous to include the null-effect of self-controlled feedback from that experiment when really there was simply no learning effect to moderate. I appreciate the authors reporting this experiment for completeness, but I think it's data should be removed from the equivalence testing section and the Discussion updated accordingly.}}

We agree that the lack of an improvement in performance during practice is unfortunate in Experiment 2. Despite this, we do think these results contribute to the literature. Our goal in the present project was to critically test between the information-processing and motivational (i.e., OPTIMAL theory) accounts of the (supposed) self-controlled learning advantage. After we finished analyzing the data from Experiment 1, it became clear that a second experiment was necessary where the feedback provided to participants would not generate an error signal, which occurs with both error and graded feedback (i.e., both of these provide information about how to correct the error). So binary feedback paired with choice (or no-choice) would be an even stronger test of the two perspectives than that in Experiment 1. From the information-processing perspective, you'd expect no performance advantage of having choice over feedback in practice, retention, or transfer because the information in the binary feedback will be poor at reducing uncertainties about performance outcomes. In contrast, from the motivational perspective (OPTIMAL theory) you'd expect a performance advantage of having choice over feedback in practice, retention, and transfer because the benefits arise from being given the opportunity to exercise choice. Thus, the lack of 1) an improvement in practice and 2) a learning effect in retention and transfer is consistent with the information-processing perspective. However, we do not interpret this as support for the information-processing perspective over the motivational view given the putative self-controlled learning advantage seems to be the result of publication bias rather than a real effect [@mckay2021]. We make note of this in a footnote on page 22. As such, any in-depth discussions about whether the information-processing or OPTIMAL theory is correct seem unwarranted. Based on your concerns, we have updated the Introduction (see below) to be more clear about our rationale and the value of Experiment 2.

> Introduction (Page 4 line 91 continued on page 5 lines 92-100):
>
> To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task. In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage. Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback. As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.

Critically, we believe it is vital to report the combined estimate to combat publication bias, especially given the meta-analytic information that has begun to emerge revealing the putative self-controlled learning advantage is the result of publication bias rather than a real effect [@mckay2021]. We have kept the combined estimate and still focus on it in our Discussion; however, we now include in the Results section a separate estimate for each Experiment for the interested reader.

> Results (Page 19 Lines 349-352 continued on page 20 lines 353-355):
>
> Next, random effects meta-analyses were conducted on the retention test data^4^ to generate a summary point estimate and 90% confidence intervals (CI) with Experiments 1 and 2 combined and also separate. The overall estimated effect when combining both experiments} was *g* = .05 (favoring self-controlled) and 90% CI [-.12, .23]. The overall estimated effect for Experiment 1 was *g* = .03 (favoring self-controlled) and 90% CI [-.19, .25]. For Experiment 2, it was *g* = .09 (favoring self-controlled) and 90% CI [-.19, .37].

\Done

\RC{\emph{It is not clear to me why Experiment 2 is a separate experiment? This is the same task with a different type of feedback, right? Thus, I assume that this reflect the schedule of recruitment and all of the subjects in Experiment 2 were enrolled later. While not wrong to call it Experiment 2, I think it would be more parsimonious to have one experiment with 3 feedback types and then simply explain any cohort effects in the methods.}}

Yes, you are correct about the task, different type of feedback, and recruitment of participants for Experiment 2. We maintain referring to them as separate experiments as presenting it as a single experiment would pose some methodological problems. First, our decision to conduct Experiment 2 was conditional on observing the results of Experiment 1 (as mentioned in our above response), which would undermine the assumption of independence between observations. Second, random assignment to receive either error or graded feedback was done for participants in the self-controlled and yoked groups in Experiment 1. With the timing of the collection of these experiments, participants in Experiment 2 could not have been assigned to receive either error or graded feedback and Experiment 1 participants could not have been randomly assigned to receive binary feedback. Lastly, our *a priori* sample size calculation was not based on a design that included all groups in a single experiment.

\Done

\RC{\emph{Assignment of subjects to groups. From the authors' description, it sounds like ALL yoked participants were enrolled after ALL self-controlled participants in a given feedback condition. Albeit minor, this introduces a confound in the timing of the two groups. Something to consider for future studies would be a blocked assignment stratified by factors like gender age or handedness (e.g., the first right handed female to come into the lab gets self-control of a randomly assigned feedback type... the NEXT right handed female to come into the lab gets yoked to the same feedback schedule and type, etc). This would make the assignment order a bit more complicated, but would reduce the temporal disparity between the groups.}}

Yes, all participants in the self-controlled groups were collected before the yoked participants. We acknowledge in the original submission (and now Page 7 Lines 158-160 in the revised manuscript) that "this is typical in the self-controlled learning literature as the self-controlled participants' self-selected feedback schedules are required for providing feedback to the participants in the yoked (i.e., control) groups." We do agree that different assignment strategies could have been used; however, our decision was to follow the typical procedure for this area of research.

\Done

\RC{\emph{Lack of reporting for psychological variables. I might have missed it as there are many results presented, but could the authors report the (non-significant?) results of the self-control manipulation? The authors currently report the significant effects of Time and Feedback, but the effect of Self Control seems more theoretically relevant although non-significant.}}

We now report the effect of Choice in all analyses in the Results section. The effect of Choice was always non-significant.

\Done

\RC{\emph{Lack of equivalence tests for motivational variables. In the same way it is theoretically relevant to do equivalence tests at retention, it seems like it would be important to do equivalence tests for the different motivational variables as well?}}

We agree these would be theoretically relevant and have included them in Supplementary C.

\Done

# Review \#2

\RC{\emph{This manuscript reports a study that attempted to test different causal explanations for the self-controlled learning advantage. The explanations could not be examined because the experiment failed to find a self-controlled learning advantage. The study adds to a growing body of evidence which has failed to replicate the self-controlled learning advantage in the motor skills domain. Given the rigor with which the study was conducted and analyzed, the findings make an important contribution to the literature.}

\emph{I do not have any major concerns with the manuscript, though I may have called in to question the decision to limit practice to 72 trials had a self-controlled learning advantage been discovered. The reason is that Magill and Wood (1986) did not find a benefit of quantitative (error) versus qualitative (graded) feedback on a multi-movement timing task until the second half of practice. During the first half, learners derived the same benefit from quantitative and qualitative feedback. Consequently, it is not clear whether the amount of practice in the current experiment would have provided a fair test of the information processing account of the putative self-controlled learning advantage given that the informational value of quantitative feedback seems to increase with practice. Of course, that point is moot given the current findings.}}

Thank you for the encouraging and positive comments about our manuscript. The amount of practice is an interesting point given past motor learning research looking at this variable. We discuss the Magill and Wood paper below with another comment of yours.

\RC{\emph{In the abstract, the task is described as a rapid reaching task with spatial and temporal timing goals. I would not describe this task as a reaching task. I think it would be more appropriate to simply say “… while learning a planar upper limb movement with spatial and timing goals.” Note that it is referred to as a rapid aiming task on page 4, l. 25.}}

We have removed all reference to the task as a reaching task and now describe it as a "novel motor task" in the abstract.

\Done

\RC{\emph{I recommend stating that error and graded feedback have also been referred to as quantitative and qualitative feedback (e.g., Magill \& Wood, 1986) when you introduce error and graded feedback.}}

We have incorporated your suggestion as a footnote in the revised manuscript when we introduce error and graded feedback on page 3.

\Done

\RC{\emph{The description of the sample size estimation on page 5, l. 23 specifies that “groups = 2.” Shouldn’t the number of groups be 4?}}

Thank you for catching this typo. We have corrected it to say groups = 4 on page 6.

\Done

\RC{\emph{Comparisons were done to determine if error estimation improved with practice and whether the groups differed in terms of error estimation abilities at different stages of learning. However, it would be interesting to report if the participants who were asked to estimate during the pretest performed better in acquisition, retention and transfer than the participants who were not asked to estimate during the pretest. I realize this comparison was not an original purpose of the experiment, however, reporting this information would add value in my opinion.}}

We have added this analysis to Supplementary B and there were no significant main effects or interactions.

\Done

\RC{\emph{I understand the rationale for restricting the participants in the choice groups to 24 trials, however, it would be prudent to raise the possibility in the discussion that limiting choice in this way may have attenuated the self-controlled learning advantage.}}

We do not think this restriction contributed to our lack of a self-controlled learning advantage. Based on a recent meta-analysis [@mckay2021], we believe we did not find a self-controlled learning advantage because it either does not exist or is an extremely small effect. However, to your point earlier self-controlled feedback research actually found that limiting the number of choice opportunities does not negatively impact learning [@patterson2011] and can even lead to superior learning [@hansen2011]. Based on the conclusions of the self-controlled learning meta-analysis, we elected to not discuss this possibility and instead maintain the focus on our results being consistent with the meta-analytic estimates and conclusions of @mckay2021 regarding the self-controlled learning advantage being either a non-real effect or an extremely small effect.

\Done

\RC{\emph{I am not certain the findings from Experiment 2 offer much insight into self-controlled learning given that learners were not able to learn anything with this type of feedback. However, for the sake of thoroughness, Experiment 2 deserves to be described in the manuscript. I recommend reporting the number of “hits” in Experiment 2 to give readers a sense of the number of occasions learners received some sort of positive reinforcement. I think it would also be helpful to report the number of hits in Experiment 1 to potentially bolster the argument for the proposed disassociation between the informational and motivational impacts of knowledge of results.}}

Based on your comment (and a comment by Reviewer 1), we have updated the introduction to more clearly describe our rationale for and the value of Experiment 2. The lack of a performance improvement in practice is consistent with the information-processing perspective as the binary feedback would not be effective at reducing uncertainties about performance outcomes. As such, under such conditions you would expect the results we saw. However, the lack of improvement is inconsistent with a motivational perspective wherein having choice itself is the cause for any performance and learning benefits. We do not interpret this as support for the information-processing perspective over the motivational view given the putative self-controlled learning advantage seems to be the result of publication bias rather than a real effect [@mckay2021]. We make note of this in a footnote on page 22.

> Introduction (Page 4 line 91 continued on page 5 lines 92-100):
>
> To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task. In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage. Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback. As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.

Thank you for the suggestion of including the number of hits in both experiments. We have included this information in Table 2 (page 18) in the revised manuscript and we also make reference to it in the Discussion.

> Discussion (Page 23 Lines 447-450):
>
> The number of "hits" for the spatial and timing goals were both quite low for all groups. Although this may have also impacted perceptions of competence, the relatively low "hit" rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.

\Done

\RC{\emph{Were the questions from the Intrinsic Motivation Inventory modified in any way and were the perceived autonomy questions exactly the same as those used earlier?}}

We modified the questions for the IMI subscales so it referenced "the motor task" when participants were asked the various questions. An example for the perceived competence subscale is: "I think I am pretty good at this motor task". An example for the interest/enjoyment is: "This motor task was fun to do". The perceived autonomy questions (e.g., "There is not much opportunity for my to exercise choices during my practice session") were the same across both experiments and used in previous work [e.g., @carter2017b; @stgermain2022]. We have included a copy of all the questions used for perceived competence, intrinsic motivation, and perceived autonomy in the public repository for this experiment in a directory called "materials". We make a specific note of the availability of the questionnaires in a footnote on page 11.

\Done

\RC{\emph{Do you have any explanation for why the graded feedback group continued to improve during practice after the error feedback group had plateaued? This is a curious finding, as one would expect just the opposite based on Magill and Wood (1986).}}

It was an interesting result that @magill1986 did not find a difference in feedback types until the second half of practice with 100 trials; although there are some considerable differences between their experiment and ours. First, they used a motor task that required six movements and varying timing goals compared to our single movement with a timing and spatial goal. So there could be some differences due to complexity or difficulty of the to-be-learned motor task. Second, Magill and Wood report that they did not find an interaction between Block and Feedback type until they strayed from their *a priori* analysis plan and excluded a block after observing their data. This interaction was also only found in one of their three performance outcome variables. For these reasons, we think their result must be interpreted cautiously. However, we do think it would be of value for future studies to further probe this potential interaction between amount of practice and different characteristics of the feedback provided to the learners. In terms of the significant Feedback x Block interaction we found for the timing goal in Experiment 1, the improvements in the Graded feedback groups after block 2 were quite minimal. In Figure 2B, all four groups are very similar from blocks 4 to 6. A potential explanation for this could be that the high informational value of the error feedback could have led to those participants making short-term maladaptive corrections to their responses [@salmoni1984].

\Done

# Reviewer \#3

\RC{\emph{This paper reports two experiments (total n=228) on how exercising choice influences motor learning of a reaching task with spatial and timing goals. Participants practiced either with choice over feedback requests or under no-choice, yoked feedback conditions. In Experiment 1, two forms of knowledge of results feedback were tested (error feedback or graded feedback) and in Experiment 2, binary feedback was provided. Behavioral performance, error estimation, and psychosocial data were collected. Whereas the error and graded feedback conditions supported skill acquisition, the binary feedback did not yield significant improvements from pre-testing to retention. Across both experiments, there was no evidence that the opportunity to exert self-control enhanced learning compared to the no-choice groups.}

\emph{In my opinion, the presented manuscript is well-written and contributes a well-powered study to the current debate surrounding self-controlled learning. However, I think a stronger rationale for Experiment 2 (binary feedback) should be provided. It is not clear to me why this manipulation was presented as a standalone experiment rather than as additional feedback condition in Experiment 1, and perhaps it is not necessary to include the binary feedback groups in the manuscript at all. Additionally, as the manuscript discusses both the OPTIMAL and information-processing perspectives as potential explanations for self-controlled learning advantages, I feel that the inclusion of further analyses regarding participants’ feedback requests could help to better understand the mechanisms underpinning self-controlled learning. Overall, I generally believe that this paper is publishable pending some relatively minor revisions. I have noted page and line numbers (according to the authors’ submitted version) along with my more specific points below.}}

Thank you for the positive comments about our manuscript. In line with comments from the other two Reviewers, we have updated the Introduction to more clearly explain our rationale for and the value of Experiment 2. In short, after we had analyzed the data from Experiment 1, we realized that a second experiment was required where participants received a type of feedback that would have a very low informational value for how to correct one's behaviour (i.e., would not generate an error signal). This is why binary feedback was chosen for Experiment 1 because both error and graded feedback generate an error signal as both provide information about how to change one's behaviour. As such, we feel Experiment 2 was a stronger test of the information-processing and motivational perspectives. From the information-processing view, you'd expect no performance advantages of having choice over binary feedback in any experimental phase whereas from the motivational view, you'd still expect performance advantages in practice, retention, and transfer because these benefits arise out of having choice. Additionally, keeping the results of Experiment 2 in the manuscript is important for meta-analytic reasons, especially given the recent self-controlled learning meta-analysis found that the putative self-controlled learning advantage is the result of publication bias rather than a true effect [@mckay2021].

> Introduction (Page 4 line 91 continued on page 5 lines 92-100):
>
> To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task. In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage. Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback. As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.

\Done

\RC{\emph{p. 7, lines 16-17: “Additionally, half of the participants in each group were randomly selected to estimate their performance on the spatial and timing goals after each trial in the pre-test.” Please provide more detail on how participants provided their estimations (e.g., manual vs. verbal responses, spatial and/or timing estimations)}}

We have clarified that participants made their estimations verbally on pages 7 (line 168) and 11 (line 210).

\Done

\RC{\emph{p. 9, lines 1-2: “Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.” How did participants indicate whether they did or did not want feedback? (e.g., manual vs. verbal response?) Although this is nicely illustrated in Figure 1, it would be helpful to also include in the text that participants were made aware of how many feedback trials remained}}

We have clarified that participants made their feedback request verbally on page 9 (line 208) and in the Figure 1 caption (page 10). We have also included the information about the remaining feedback trials in the text on page 9 (lines 205-206).

\Done

\RC{\emph{p. 8, lines 17-18: “Graded feedback for the spatial goal was provided as “too short” if performance was < 40 degrees (or 60 degrees in transfer)”. I think it’s confusing to include the ’60 degrees in transfer’ here (as well as on page 9, lines 18-20) if there was no feedback provided in transfer (according to p. 7, lines 13-14: “No feedback about motor performance was provided in pre-test, retention, or transfer”).}}

Thank you for catching this. We have removed this confusing information.

\Done

\RC{\emph{p. 9, lines 9-12: “The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory and the perceived autonomy questions were used in earlier work”. Just to clarify, the perceived autonomy questions are not the same as the perceived choice subscale in the IMI? If this is a customized scale, please note if the specific items are available in a previous publication, and if not, consider including them in the supplementary materials.}}

The perceived autonomy questions we used are not the perceived choice subscale of the IMI. You are correct that they are a customized scale that we have used in the past [e.g., @carter2017b; @stgermain2022]. We have also added the questions we used for all questionnaires to the public repository for this project in the directory "materials".

\Done

\RC{\emph{Is the finding that exercising choice did not impact perceptions of autonomy compared to yoked groups unusual? Is there a different/perhaps more sensitive way to assess perceptions of autonomy?}}

It is actually quite common to not find an effect of choice over some practice variable like one's feedback schedule on measures of perceived autonomy [e.g., @barros2019; @carter2017b; @mckay2020b; @stemarie2013]. It was actually only very recently that some studies found higher perceptions of autonomy [e.g., @mckay2020a; @stgermain2022] in those participants given choice versus those not given the same choice opportunities. A key difference is both of those experiments had even larger sample sizes per group than what we had in the present work. For instance, St. Germain et al. (2022) had 50 participants per group. Thus, we think this highlights that the impact of being given choice over a practice variable has a rather small effect on perceived autonomy and requires larger sample sizes to reliably detect. As a side note, our perceived autonomy questions are those used in the St. Germain et al. paper, which found an effect favouring choice on perceived autonomy.

\Done

\RC{\emph{I felt there were a number of additional analyses that could be conducted to help provide a more fulsome story. For example:}}

Thank you for the following suggestions. In short, we did not perform any analyses regarding the distribution of feedback requests or how feedback requests related to performance. Both of these have been reported in several previous papers investigating self-controlled feedback schedules. We provide more details regarding our decision below when we respond to each analysis suggestion independently. We did, however, include details regarding the number of "hits" as this was something that Reviewer 2 also raised.

\Done

\RC{\emph{a. What was the distribution of feedback requests throughout acquisition? (e.g., did participants generally choose to fade their feedback? or perhaps are there early vs. late feedback requesters?)}}

Our main reason for not analyzing the distribution of feedback requests or early verus late requesters is these are not things we manipulated in our design. Thus, these analyses would be post-hoc and non-causal. As such, we do not think that would provide any new insight beyond what has already been reported in earlier self-controlled feedback research: sometimes participants seem to create faded request schedules [e.g., @chiviacowsky2002; @janelle1997] and sometimes schedules stay relatively consistent [e.g., @patterson2010]. Additionally, a recent meta-analysis [@mckay2022] did not find evidence for several feedback scheduling hypotheses: no evidence 1) that faded schedules are more effective than non-faded, 2) that performance-contingent or bandwidth schedules are more effective than fixed schedules, and 3) that feedback frequency does not have consistent effects. For these reasons, we elected to not conduct these analyses and instead keep our discussion more focused on the fact that our results are consistent with the recent self-controlled learning meta-analysis suggesting this supposed effect is likely non-existent and instead was the result of publication bias.

\Done

\RC{\emph{b. How did feedback requests relate to learners’ performance? (e.g., did feedback requests tend to follow relatively good vs. bad trials?). This seems particularly important to address with reference to the information-processing explanation of self-controlled learning advantages.}}

We did not query participants on their reasons why or why not feedback was requested during practice. Without knowing this information for each participant, it is not possible to know whether any relation to relatively good or relatively bad trials was strategic or coincidental. Given such an analysis would also be post-hoc and non-causal, we also do not think this analysis would provide new insight beyond that already reported in earlier self-controlled feedback experiments that have used multiple-choice questionnaires [e.g., @carter2012; @chiviacowsky2002; @patterson2010; @patterson2011] or open-ended questions [e.g., @carter2016; @laughlin2015]. Similar to above, not including these unplanned analyses allows us to remain focused on our main conclusion that there is a lot of evidence emerging that strongly suggests the supposed self-controlled learning advantage is not a replicable or real effect.

\Done

\RC{\emph{c. How often did participants actually "hit" the target? It seems that the success criteria were quite strict - can you be expected to “acquire/retain” a skill you haven’t successfully performed? Could the potential unlikelihood of success/limited expectancies for success have undermined potential motivational aspects of self-control?}}

We have added information about the number of "hits" in Table 2 (Page 18) of the revised manuscript based on your comment and that from Reviewer 2. Interestingly, the "hit" rate was low in both experiments and for all groups. Although the low success rates seem to have impacted perceptions of competence, particularly for those that received graded and binary feedback, the graded feedback groups improved their performance during practice, and retention and transfer were better than pre-test levels. Further, the graded feedback groups' ratings for perceived competence were numerically similar to those reported by the participants in Experiment 2 with binary feedback. Additionally, self-reported intrinsic motivation was numerically similar in all experimental groups. As such, we do not think the low "hit" rates in the present experiments undermined any potential motivational influences of self-controlled feedback schedules. We also now make reference to the hit data in the Discussion.

> Discussion (Page 23 Lines 447-450):
>
> The number of "hits" for the spatial and timing goals were both quite low for all groups. Although this may have also impacted perceptions of competence, the relatively low "hit" rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.

\Done

\RC{\emph{p. 18, lines 1-3: “...argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals”. Yes – as noted above, it would be helpful to understand whether these participants requested feedback in a performance dependent fashion}}

In line with our response above, we did not query participants on their reasons for requesting feedback. The idea that self-controlled feedback is effective because it reduces uncertainty about movement outcomes emerged from early work by @chiviacowsky2005 that showed a self-controlled feedback schedule was only effective if the feedback decision was made after and not before one's performance. Carter et al. (2014) extended this work with a group that made their feedback decision before a trial but could then change their mind after a trial. Thus, the key idea behind requesting feedback in a performance dependent way to reduce uncertainty is about making the decision *after* one's movement, which was the case for all self-controlled groups in the present experiment. But consistent with earlier responses and our stance in the manuscript, we do not think the self-controlled learning advantage is a real effect based on recent experiments with large samples (and often pre-registered) and the meta-analysis by @mckay2021. As such, analyses and discussions surrounding the information-processing explanation or the motivational (i.e., OPTIMAL theory) view seem moot. We instead contend that contextualizing our results within these larger, and often pre-registered, experiments and the McKay et al. meta-analysis is the more critical discussion point.

\Done

\RC{\emph{p. 19, lines 19-21: “Similarly, self-controlled feedback schedules did not enhance error estimation skills (see Supplementary A) [...], inconsistent with the information-processing perspective.” Similar to above, I think we need to know more about participants feedback choices to consider why error estimation skills did not improve and how this speaks to the information-processing perspective}}

To clarify, error estimation skills did improve from pre-test to retention and transfer for the subset of participants who estimated during pre-test in Experiment 1. We did not find that error estimation was enhanced in the choice groups compared to the yoked groups. We have made this more clear in the revised manuscript.

> Discussion (Page 22 Lines 420-421)
>
> Similarly, self-controlled feedback schedules did not enhance error estimation skills compared to yoked schedules (see **Supplementary B**) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.

Similar to our above comments, such a finding is consistent with the idea that there is no self-controlled learning advantage to explain from an information-processing or motivational view in motor learning [@mckay2021].

\Done

\RC{\emph{p. 20, lines 6-10: “Additionally, we used a strict criteria with binary feedback where any outcome other than zero error was considered a miss. Thus, binary feedback may be more effective when paired with a tolerance zone such as that used in the bandwidth technique” Agreed... As mentioned earlier, please indicate what the rate of success was in this group and consider whether this group can be integrated into Experiment 1 or removed}}

As mentioned above with respect to your earlier comment, we have added this information in the revised manuscript in Table 2 on page 18.

\Done

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-08-14 docs/revision-1/r1_manuscript.Rmd

--- 2022-05-06 docs/submission/manuscript.Rmd
@@
 
-  \noindent \textbf{Corresponding authors:} Michael J. Carter (michaelcarter@mcmaster.ca) or Laura St. Germain (stgerml@mcmaster.ca)
+  \noindent \textbf{Corresponding authors:} Laura St. Germain (stgerml@mcmaster.ca) or Michael J. Carter (cartem11@mcmaster; motorlab@mcmaster.ca)
 
@@
 In the information-processing view, choice allows learners to engage in performance-dependent strategies that reduce uncertainty about task outcomes.
-To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a rapid reaching task with spatial and timing goals.
+To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a \textcolor{blue}{novel motor} task with spatial and timing goals.
 Across both experiments (N = 228 participants), we did not find evidence to support a self-controlled learning advantage.
@@
 keywords          : "Self-controlled, Knowledge of results, OPTIMAL theory, Retention"
-wordcount         : "2978 for Introduction, Results, and Discussion"
+#wordcount         : "2978 for Introduction, Results, and Discussion"
 
@@
   - \usepackage{setspace}
-  - \pagewiselinenumbers
+  #- \pagewiselinenumbers
   - \raggedbottom
@@
 Knowledge of results feedback [@salmoni1984] can provide varying amounts of information to learners depending on its characteristics.
-Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., "too far"), and binary feedback indicates only success or failure information (e.g., "miss") [@luft2014].
-When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
+Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., "too far"), and binary feedback indicates only success or failure information (e.g., "miss") [@luft2014].[^1] When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
 These self-controlled feedback schedules have typically enhanced motor skill learning compared to yoked feedback schedules, wherein learners experience the feedback schedule created by a self-controlled counterpart, but without any choice [see @sanli2013; @stemarie2019 for reviews].
+
+[^1]: \textcolor{blue}{Others have referred to error feedback as quantitative feedback and graded feedback as qualitative feedback} [e.g., @magill1986]\textcolor{blue}{.
+We use the terminology error, graded, and binary feedback because graded and binary feedback are different forms of qualitative feedback.}
 
@@
 
-To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we provided participants in choice and yoked (i.e., no-choice) groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) during the acquisition of a rapid aiming task.
-Motor learning was assessed using delayed (~24 hours) retention and transfer tests.
+To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, \textcolor{blue}{we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task.
+In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage.
+Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback.
+As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.} Motor learning was assessed using delayed (~24 hours) retention and transfer tests.
 If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule *would not matter* for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups.
@@
 One hundred and fifty-two right-handed [@oldfield1971], healthy adults participated in Experiment 1 ($M_{age}$ = 20.64 years, $SD_{age}$ = 2.45, 88 females).
-Sample size was determined from an *a-priori* power analysis using the *ANOVA: fixed effects, main effects and interactions* option in G*Power [@faul2009] with the following parameters: $\alpha$ = 0.05, $\beta$ = .20, $f$ = 0.23, numerator = 1, and groups = 2.
+Sample size was determined from an *a-priori* power analysis using the *ANOVA: fixed effects, main effects and interactions* option in G\*Power [@faul2009] with the following parameters: $\alpha$ = 0.05, $\beta$ = .20, $f$ = 0.23, numerator = 1, and groups = \textcolor{blue}{4}.
 This revealed a required sample of 151 participants.
-Our chosen effect size was based on a meta-analytic estimate ($f$ = .32) by @mckay2014; however, we used a more conservative estimate given the uncertainty of how choice would interact with our feedback characteristic manipulation.
+Our chosen effect size was based on a meta-analytic estimate (*f* = .32) by @mckay2014; however, we used a more conservative estimate given the uncertainty of how choice would interact with our feedback characteristic manipulation.
 Participants were compensated $15 CAD or with course-credit for their time.
@@
 
-Data collection consisted of two sessions separated by approximately 24 hours.[^1] Session one included a pre-test (12 trials) and an acquisition phase (72 trials).
+Data collection consisted of two sessions separated by approximately 24 hours.[^2] Session one included a pre-test (12 trials) and an acquisition phase (72 trials).
 Session two included the delayed retention (12 trials) and transfer (12 trials) tests.
@@
 Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals.
-Additionally, half of the participants in each group were randomly selected to estimate their performance on the spatial and timing goals after each trial in the pre-test.
+Additionally, half of the participants in each group were randomly selected to \textcolor{blue}{verbally} estimate their performance on the spatial and timing goals after each trial in the pre-test.
 Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested [e.g., @chiviacowsky2005] to be adopted spontaneously by participants controlling their feedback schedule.
@@
 
-[^1]: Six participants (three Choice+Error-Feedback and three Choice+Graded-Feedback) had their second session completed approximately 48 hours later because a snowstorm closed the University.
+[^2]: Six participants (three Choice+Error-Feedback and three Choice+Graded-Feedback) had their second session completed approximately 48 hours later because a snowstorm closed the University.
 
@@
 Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.
+\textcolor{blue}{The number of remaining feedback trials was also displayed during this feedback delay interval.} If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected via \textcolor{blue}{verbal response} (or imposed on the yoked groups), it was also displayed for 3000 ms.
 
-Before the retention and transfer tests, participants were reminded about the task and its associated goals.
-All participants were asked to estimate their performance after each trial in retention and transfer.
-After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.
-The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory [@mcauley1989; @ryan1982] and the perceived autonomy questions were used in earlier work [@barros2019; @carter2017b].
-Cronbach's alpha values for each questionnaire at each time point are reported in Table \@ref(tab:table1).
-
-### Experiment 2
-
-Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group ($n$ = 38; $M_{age}$ = 22.37 years, $SD_{age}$ = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group ($n$ = 38; $M_{age}$ = 18.00 years, $SD_{age}$ = 0.93, 28 females).
-Binary feedback for the spatial goal was provided as "hit" if performance was exactly 40 degrees (or 60 degrees in transfer) and as "miss" for everything else.
-For the timing goal, binary feedback was provided as "hit" when performance was exactly 225 ms and as "miss" for everything else.
-Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
+\clearpage
 
@@
 
-(ref:fig1-caption) \small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
+(ref:fig1-caption) \small \normalfont \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
 Trials began by informing participants the trial number (500 ms) they were on in acquisition.
@@
 On trials where feedback was not requested, a blank screen **(A)** was shown for 3000 ms.
-When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group.
+When feedback was selected via \textcolor{blue}{verbal response}, feedback was provided for both the spatial and timing goals according to their experimental group.
 The error feedback group **(B)** saw their constant error, the graded feedback group **(C)** saw either "too far" or "too short" for the spatial goal and "too fast" or "too slow" for the timing goal, and the binary feedback group **(D)** saw either "hit" or "miss" for the task goals.
@@
 The sequence of events was similar in pre-test, retention, and transfer except all trials were no-feedback trials.
+
+\clearpage
 
@@
 
+Before the retention and transfer tests, participants were reminded about the task and its associated goals.
+All participants were asked to \textcolor{blue}{verbally} estimate their performance after each trial in retention and transfer.
+After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants \textcolor{blue}{verbally} answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.[^3] The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory [@mcauley1989; @ryan1982] and the perceived autonomy questions were used in earlier work [@barros2019; @carter2017b; @stgermain2022].
+Cronbach's alpha values for each questionnaire at each time point are reported in Table \@ref(tab:table1).
+
+[^3]: \textcolor{blue}{The questionnaires can be found in the publicly available project repository in the materials directory.}
+
+### Experiment 2
+
+Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group ($n$ = 38; $M_{age}$ = 22.37 years, $SD_{age}$ = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group ($n$ = 38; $M_{age}$ = 18.00 years, $SD_{age}$ = 0.93, 28 females).
+Binary feedback for the spatial goal was provided as "hit" if performance was exactly 40 degrees (or 60 degrees in transfer) and as "miss" for everything else.
+For the timing goal, binary feedback was provided as "hit" when performance was exactly 225 ms and as "miss" for everything else.
+Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
+
 ## Data Analysis
@@
 To test for performance differences during acquisition, total error for the spatial and timing goals during acquisition were analyzed in separate mixed ANOVAs (*Experiment 1:* 2 Choice x 2 Feedback x 6 Block; *Experiment 2:* 2 Choice x 6 Block).
+Model diagnostics of total error for the spatial and timing goals revealed skewed distributions.
+We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions [@rousselet2020; @wilcox2021].
+The results of these analyses (see **Supplementary A**) were consistent with those of the mixed ANOVAs, which we report below.
 Our primary psychological outcome variables were intrinsic motivation (i.e., interest/enjoyment), perceived competence, and perceived autonomy.
 The mean score of the responses for these constructs at each time point was calculated for each participant and analyzed in separate mixed ANOVAs (*Experiment 1:* 2 Choice x 2 Feedback x 4 Time; *Experiment 2:* 2 Choice x 4 Time).
-Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50% of the participants in each group in Experiments 1 and 2), retention, and transfer (see **Supplementary A**).
+Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50% of the participants in each group in Experiments 1 and 2), retention, and transfer (see **Supplementary B**).
 
@@
 # Results
-
-Model diagnostics of total error for the spatial and timing goals revealed skewed distributions.
-We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions [@rousselet2020; @wilcox2021].
-The results of these analyses (see **Supplementary B**) were consistent with those of the mixed ANOVAs, which we report below.
 
@@
 A main effect of Test was also found for timing error, $F(1.08,160.23) = 81.21$, $p < .001$, $\eta_{G}^2 = .245$, with pre-test performance more errorful than both retention and transfer ($p$'s < .001), and retention was less errorful than transfer ($p$ < .001).
+\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,148) = .52$, $p = .471$, $\eta_{G}^2 = .001$, and timing, $F(1,148) = .32$, $p = .547$, $\eta_{G}^2 < .001$, error.}
 
@@
 \@ref(fig:fig3)B) error did not change considerably from the pre-test to the retention and transfer tests.
-There were no significant main effects or interactions for either task goals.
+\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,74) = .23$, $p = .631$, $\eta_{G}^2 = .002$, and timing, $F(1,74) = .11$, $p = .738$, $\eta_{G}^2 = .001$, error.} All other main effects and interactions were also not significant.
+
+\clearpage
+
+```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center"}
+knitr::include_graphics("../../figs/fig2.pdf")
+```
+
+(ref:fig2-caption) \small \normalfont \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses.
+Error bars denote 95% bootstrapped confidence intervals.
+**(A)** Spatial total error (degrees) and **(B)** timing total error (ms) averaged across blocks and participants within each group.
+Dotted vertical lines denote the different experimental phases.
+Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2.
+Self-reported scores for perceived autonomy **(C)**, perceived competence **(D)**, and intrinsic motivation **(E)** after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2.
+Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree).
+Dots represent individual data points.
+
+\clearpage
+
+```{r fig3, echo = FALSE, fig.cap = "(ref:fig3-caption)", fig.align = "center"}
+knitr::include_graphics("../../figs/fig3.pdf")
+```
+(ref:fig3-caption) \small \normalfont \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares.
+Error bars denote 95% bootstrapped confidence intervals.
+**(A)** Spatial total error (degrees) and **(B)** timing total error (ms) averaged across blocks and participants within each group.
+Dotted vertical lines denote the different experimental phases.
+Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2.
+Self-reported scores for perceived autonomy **(C)**, perceived competence **(D)**, and intrinsic motivation **(E)** after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2.
+Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree).
+Dots represent individual data points.
+
+\clearpage
 
@@
 This was supported by a significant main effect of Block, $F(2.41,357.13) = 60.18$, $p < .001$, $\eta_{G}^2 = .130$, where block 1 was less accurate than all other blocks ($p$'s $< .001$), block 2 was less accurate than all subsequent blocks ($p$'s $\leq .021$), and blocks 3 and 4 were more errorful than block 6 ($p$'s $\leq .015$).
-Timing error also decreased during the acquisition period (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .06$, $p = .813$ $\eta_{G}^2 < .001$.} Timing error also decreased during the acquisition period (Fig.
 \@ref(fig:fig2)B).
@@
 Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks ($p$'s $< .001$); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 ($p$'s $\leq .028$).
-
-\vspace{2ex}
-
-```{r fig2, echo = FALSE, fig.cap = "(ref:fig2-caption)", fig.align = "center"}
-knitr::include_graphics("../../figs/fig2.pdf")
-```
-
-(ref:fig2-caption) \small \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses.
-Error bars denote 95% bootstrapped confidence intervals.
-**(A)** Spatial total error (degrees) and **(B)** timing total error (ms) averaged across blocks and participants within each group.
-Dotted vertical lines denote the different experimental phases.
-Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2.
-Self-reported scores for perceived autonomy **(C)**, perceived competence **(D)**, and intrinsic motivation **(E)** after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2.
-Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree).
-Dots represent individual data points.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .54$, $p = .465$ $\eta_{G}^2 = .002$.} Descriptives for the number of "hit" trials for each group are provided in Table \@ref(tab:table2).
 
@@
 \@ref(fig:fig3)B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-None of the main effects or interactions for either task goals were significant.
+\textcolor{blue}{The main effect of Choice for both the spatial, $F(1,74) = .08$, $p = .776$, $\eta_{G}^2 < .001$, and the timing, $F(1,74) = .37$, $p = .542$, $\eta_{G}^2 = .004$, goals were not significant.
+Al other main effects and interactions for both task goals were not significant.} Descriptives for the number of "hit" trials for each group are provided in Table \@ref(tab:table2).
 
-\vspace{2ex}
-
-```{r fig3, echo = FALSE, fig.cap = "(ref:fig3-caption)", fig.align = "center"}
-knitr::include_graphics("../../figs/fig3.pdf")
+```{r table2, echo = FALSE, results = "asis"}
+table2 <- tibble::tibble(
+    c1 = c("Choice+Error-Feedback",
+           "Choice+Graded-Feedback",
+           "Yoked+Error-Feedback",
+           "Yoked+Graded-Feedback",
+           "Choice+Binary-Feedback",
+           "Yoked+Binary-Feedback"),
+    c2 = c("4",
+           "2",
+           "1",
+           "3",
+           "2",
+           "4"),
+    c3 = c("0--2",
+           "0--1",
+           "0--1",
+           "0--1",
+           "0--1",
+           "0--1"),
+    c4 = c("30",
+           "26",
+           "28",
+           "33",
+           "14",
+           "10"),
+    c5 = c("0--4",
+           "0--4",
+           "0--3",
+           "0--3",
+           "0--3",
+           "0--2"),
+)
+table2 %>%
+  kbl(booktabs = TRUE,
+      escape = TRUE,
+      linesep = "\\addlinespace",
+      caption = 'Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.',
+      col.names = c("Group",
+                  "Total",
+                  "Min--Max",
+                  "Total",
+                  "Min--Max")
+  ) %>%
+  kable_styling(position = "left",
+                font_size = 11) %>%
+  column_spec(1, width = "15em") %>%
+  column_spec(2, width = "5em") %>%
+  column_spec(3, width = "5em") %>%
+  column_spec(4, width = "5em") %>%
+  column_spec(5, width = "5em") %>%
+  add_header_above(c(" ", "Spatial goal" = 2, "Timing goal" = 2)) %>%
+  pack_rows("Experiment 1", 1, 4) %>%
+  pack_rows("Experiment 2", 5, 6)
 ```
-(ref:fig3-caption) \small \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares.
-Error bars denote 95% bootstrapped confidence intervals.
-**(A)** Spatial total error (degrees) and **(B)** timing total error (ms) averaged across blocks and participants within each group.
-Dotted vertical lines denote the different experimental phases.
-Pre-test and acquisition occurred on Day 1 and retention and transfer occurred approximately 24-hours later on Day 2.
-Self-reported scores for perceived autonomy **(C)**, perceived competence **(D)**, and intrinsic motivation **(E)** after the pre-test and after blocks 1 and 6 of acquisition on Day 1, and before the retention test on Day 2.
-Scores could range on a Likert scale from 1 (Strongly disagree) to 7 (Strongly agree).
-Dots represent individual data points.
 
@@
 Perceptions of autonomy (Fig.
-\@ref(fig:fig2)C) showed a slight decrease across time points, supported by a main effect of Time, $F(2.25,332.95) = 3.69$, $p < .022$, $\eta_{G}^2 = .003$.
+\@ref(fig:fig2)C) showed a slight decrease across time points, supported by a main effect of Time, $F(2.25,332.95) = 3.69$, $p = .022$, $\eta_{G}^2 = .003$.
 Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test ($p = .031$).
-Self-ratings for perceived competence (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 2.38$, $p = .125$, $\eta_{G}^2 = .014$.} Self-ratings for perceived competence (Fig.
 \@ref(fig:fig2)D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic.
@@
 Perceived competence scores were not significantly different after the pre-test ($p = .232$); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points ($p$'s $< .001$).
-Self-reported scores for intrinsic motivation (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 0.03$, $p = .862$, $\eta_{G}^2 < .001$.} Self-reported scores for intrinsic motivation (Fig.
 \@ref(fig:fig2)E) generally decreased after block 1, which was supported by a main effect of Time, $F(2.40,355.90) = 14.69$, $p < .001$, $\eta_{G}^2 = .012$.
@@
 Self-reported ratings were also lower before retention compared to after the pre-test ($p = .043$).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 1.69$, $p = .195$, $\eta_{G}^2 = .010$.}
 
@@
 \@ref(fig:fig3)C) were similar across all time points.
-There were no main effects or interactions.
-Perceptions of competence (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.07$, $p = .792$, $\eta_{G}^2 < .001$.
+All other main effects and interactions were also not significant.} Perceptions of competence (Fig.
 \@ref(fig:fig3)D) showed a considerable decrease after the pre-test, $F(1.85,136.91) = 106.10$, $p < .001$, $\eta_{g}^2 = .298$, where scores were significantly greater after the pre-test compared to all other time points ($p$'s $< .001$), and were higher after block 1 of acquisition than before retention ($p = .004$).
-Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, $F(2.37,175.55) = 15.31$, $p < .001$, $\eta_{G}^2 = .018$.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.25$, $p = .620$, $\eta_{G}^2 = .002$.} Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, $F(2.37,175.55) = 15.31$, $p < .001$, $\eta_{G}^2 = .018$.
 Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention ($p$'s $< .001$), and higher after block 1 than after block 6 and before retention ($p$'s $< .026$).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 1.04$, $p = .312$, $\eta_{G}^2 < .013$.}
 
@@
 
-Our main comparison of interest was between choice and no-choice (i.e., yoked groups).
-To evaluate the self-controlled learning effect observed across Experiments 1 and 2, Hedges' *g* for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies.
-Next, a random effects meta-analysis was conducted on the retention test data[^2] to generate a summary point estimate and 90% confidence intervals (CI).
-This resulted in an overall estimated effect of $g = .05$ (favoring self-controlled) and $90\% \,CI \,[-.12,.23]$.
+Our main comparison of interest was between choice and yoked (i.e., no-choice) groups.
+To evaluate the self-controlled learning effect, Hedges' *g* for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies \textcolor{blue}{(see \textbf{Supplementary C} for the psychological data).
+Next, random effects meta-analyses were conducted on the retention test data}[^4] to generate a summary point estimate and 90% confidence intervals (CI) \textcolor{blue}{with Experiments 1 and 2 combined and also separate.
+The overall estimated effect when combining both experiments} was $g$ = .05 (favoring self-controlled) and 90% CI [-.12, .23].
+\textcolor{blue}{The overall estimated effect for Experiment 1 was $g$ = .03 (favoring self-controlled) and 90\% CI [-.19, .25].
+For Experiment 2, it was $g$ = .09 (favoring self-controlled) and 90\% CI [-.19, .37].}
 
-[^2]: We report an estimate for retention tests to facilitate comparison to a recent meta-analysis [@mckay2021] that produced estimated effects of self-controlled learning at retention specifically.
+[^4]: We report an estimate for retention tests to facilitate comparison to a recent meta-analysis [@mckay2021] that produced estimated effects of self-controlled learning at retention specifically.
 
@@
 All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not.
-Therefore, the present experiments can be considered inconsistent with all effects larger than $g = \pm.23$.
+Based on the \textcolor{blue}{combined overall estimate} the present experiments can be considered inconsistent with all effects larger than $g = \pm.23$.
 
@@
 According to the OPTIMAL theory [@wulf2016], self-controlled practice or choice conditions are advantageous because the provision of choice increases perceptions of autonomy and competence, which increase intrinsic motivation and ultimately both motor performance and learning.
-Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals [@carter2014; @carter2017a; @grand2015].
+Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals [@carter2014; @carter2017a; @grand2015] to enhance error detection and correction abilities [@barros2019; @carter2014; @chiviacowsky2005].
 In contrast to these predictions, we did not find evidence that providing learners with choice over their feedback schedule was beneficial for motor learning, despite collecting a much larger sample (*N* = 228 across both Experiments) than those commonly used in self-controlled learning experiments [median sample size *N* = 36 in a meta-analysis by @mckay2021] and motor learning experiments in general [median *n*/group = 11 in a review by @lohse2016].
@@
 Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results [@mckay2021].
-We estimated the overall effect of self-controlled practice in retention to be significantly smaller than any effect larger than $g = .23$.
+We estimated the overall effect of self-controlled practice in retention \textcolor{blue}{collapsed across experiments} to be significantly smaller than any effect larger than $g = .23$.
 This is consistent with the estimates from @mckay2021 after accounting for publication bias ($g =$ -.11 to .26), which suggested either no effect or a small effect in an unknown direction.
@@
 Given our current replication failure with those in recent years [@bacelar2022; @grand2017; @leiker2019; @mckay2020a; @mckay2020b; @stgermain2022; @yantha2021] and the conclusions from @mckay2021, motivational (i.e., OPTIMAL theory) versus information-processing explanations seem moot.
-Nevertheless, the present results are incompatible with both perspectives.
-Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
-Similarly, self-controlled feedback schedules did not enhance error estimation skills (see **Supplementary A**) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
+Nevertheless, the present results are incompatible with both perspectives.[^5] Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
+Similarly, self-controlled feedback schedules did not enhance error estimation skills \textcolor{blue}{compared to yoked schedules} (see **Supplementary B**) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
 Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose.
@@
 
+[^5]: \textcolor{blue}{Although the lack of performance improvements in Experiment 2 are compatible with the information-processing perspective, we do not interpret this as support for this view over the motivational one given the conclusions from McKay and colleagues' (in-press) recent meta-analysis.}
+
 Although unexpected, the influence of feedback characteristics on perceptions of competence may hint to a dissociation between informational and motivational impacts of knowledge-of-results feedback.
@@
 Participants in Experiment 2 who received binary feedback reported the lowest perceptions of competence and were also the only participants who did not show improvements in task performance from pre-test.
-Thus, future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
+\textcolor{blue}{The number of "hits" for the spatial and timing goals were quite low for all groups.
+Although this may have impacted perceptions of competence, the relatively low "hit" rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.} Future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
 
@@
 Although the present experiments were not pre-registered, the analysis plan was determined prior to viewing the data.
-In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see **Supplementary B**).
+In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see **Supplementary A**).
 The sensitivity analyses supported the conclusions of the primary analyses and are consistent with research that has followed pre-registered analysis plans [@bacelar2022; @grand2017; @leiker2019; @mckay2020a; @mckay2020b; @stgermain2022; @yantha2021].
@@
 \noindent
-**Funding.** &nbsp;This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
+**Funding.** &nbsp;This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University (MJC).
 LSG was supported by an NSERC Postgraduate Scholarship.
@@
 \noindent
-**Authors' contributions using CRediT.** &nbsp;Laura St.
+**Authors' contributions using CRediT.** &nbsp;Conceptualization (LSG, BM, JGAC, MJC); Data curation (LSG, BM, MJC); Formal analysis (LSG); Funding acquisition (MJC); Investigation (LSG, AP, AW, OL, SF); Methodology (LSG, BM, JGAC, MJC); Project administration (LSG, MJC); Software (LSG, MJC); Supervision (LSG, MJC); Validation (BM, MJC); Visualization (LSG, BM, JGAC, MJC); Writing -- original draft (LSG, BM, AP, AW, OL, SF, JGAC, MJC); Writing -- review & editing (LSG, BM, AP, AW, OL, SF, JGAC, MJC)
+<!-- &nbsp;Laura St.
 Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization.
@@
 Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.
+-->
 

### 2022-08-14 docs/revision-1/r1_supplementary.tex

--- 2022-05-06 docs/preprint/supplementary.tex
@@
 \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
+\renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
 \ifLuaTeX
@@
 
-We asked all participants to estimate their performance on the spatial (Fig.
-\ref{fig:figS1}) and timing (Fig.
-\ref{fig:figS2}) components of the motor task after each trial in retention and transfer, similar to past research (e.g., Barros et al., 2019; Carter et al., 2014; Carter \& Patterson, 2012).
-Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown).
-To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial.
-Next, we computed total estimation error (EE) using the equation:
-\begin{equation}
-EE = \sqrt{CE^2 + VE^2}
-\end{equation}
-where \(CE\) was the average estimation bias and \(VE\) was the standard deviation of these errors. This approach is consistent with that used by Bruechert et al. (2003).
-
-\hypertarget{error-estimation-in-retention-and-transfer}{%
-\subsection{Error estimation in retention and transfer}\label{error-estimation-in-retention-and-transfer}}
-
-Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig.
-\ref{fig:figS1}) and timing (Fig.
-\ref{fig:figS2}) domains in Experiments 1 and 2.
-For the spatial estimation error, we found a significant main effect of Test in Experiment 1, \(F(1,148) = 32.40\), \(p < .001\), \(\eta_{G}^2 = .060\), and in Experiment 2, \(F(1,74) = 18.79\), \(p < .001\), \(\eta_{G}^2 = .026\), with more accurate estimations in retention than transfer.
-Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, \(F(1,148) = 7.12\), \(p = .008\), \(\eta_{G}^2 < .001\), we did not decompose the interaction as the effect size estimate was less than \(.001\).
-There were no significant main effects or interactions for timing estimation error in Experiment 2.
-A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed.
-Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.
-
-\begin{figure}
-
-{\centering \includegraphics{../../figs/figS1}
-
-}
-
-\caption{\small \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
-The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
-Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
-Grey connected dots represent individual data for participants in each group.}\label{fig:figS1}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{../../figs/figS2}
-
-}
-
-\caption{\small \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
-The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
-Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
-Grey connected dots represent individual data for participants in each group.
-Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS2}
-\end{figure}
-
-\hypertarget{development-of-error-estimation-skills}{%
-\subsection{Development of error estimation skills}\label{development-of-error-estimation-skills}}
-
-In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment.
-We found significant main effects of Test for both the spatial, \(F(1.45,104.67) = 20.72\), \(p < .001\), \(\eta_{G}^2 = .144\), and timing, \(F(1.10,79.40) = 46.88\), \(p < .001\), \(\eta_{G}^2 = .060\), error estimations.
-For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer (\(p\)'s \textless{} .001), and transfer had higher error than retention (\(p\) \textless{} .001).
-Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test (\(p\)'s \textless{} .001).
-In Experiment 2, none of the main effects or interactions were significant.
-
-\newpage
-
-\hypertarget{supplementary-b}{%
-\section{Supplementary B}\label{supplementary-b}}
-
 Model diagnostics of total error (E) for the spatial and timing goals revealed skewed distributions.
@@
 For Experiment 1, the 95\% confidence intervals overlapped with zero at each decile when comparing the choice and yoked groups for both the spatial (Fig.
-\ref{fig:figS3}A) and timing (Fig.
-\ref{fig:figS3}B) goals.
+\ref{fig:figS1}A) and timing (Fig.
+\ref{fig:figS2}A) goals.
 Similarly, in Experiment 2 there were no significant differences between the choice and yoked groups in any decile for the spatial (Fig.
-\ref{fig:figS3}C) and timing (Fig.
-\ref{fig:figS3}D) goals.
+\ref{fig:figS1}B) and timing (Fig.
+\ref{fig:figS2}B) goals.
 The results from these shift function analyses are consistent with the analyses reported in the main manuscript and a recent meta-analysis (McKay et al., in-press), suggesting that giving learners choice during practice is not advantageous for motor learning.
@@
 
-{\centering \includegraphics{../../figs/figS3}
+{\centering \includegraphics{../../figs/figS1}
 
@@
 
-\caption{\small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) spatial E (deg) shift function.} The top row illustrates scatter plots of individual mean spatial E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+\caption{\small \normalfont \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) spatial E (deg) shift function.} The top row illustrates scatter plots of individual mean spatial E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
 The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines.
@@
 If a 95\% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution.
-There were no significant differences for any decile in either experiment.}\label{fig:figS3}
+There were no significant differences for any decile in either experiment.}\label{fig:figS1}
 \end{figure}
@@
 
-{\centering \includegraphics{../../figs/figS4}
+{\centering \includegraphics{../../figs/figS2}
 
@@
 
-\caption{\small \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+\caption{\small \normalfont \onehalfspacing \textbf{Post-test (collapsed across retention and transfer) timing E (ms) shift function.} The top row illustrates scatter plots of individual mean timing E for each group in Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
 The middle row illustrates the same scatter plots as the top row, but with the deciles of each distribution represented by the black lines.
@@
 If a 95\% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution.
-There were no significant differences for any decile in either experiment.}\label{fig:figS4}
+There were no significant differences for any decile in either experiment.}\label{fig:figS2}
 \end{figure}
 
-\newpage
+\clearpage
+
+\hypertarget{supplementary-b}{%
+\section{Supplementary B}\label{supplementary-b}}
+
+We asked all participants to estimate their performance on the spatial (Fig.
+\ref{fig:figS3}) and timing (Fig.
+\ref{fig:figS4}) components of the motor task after each trial in retention and transfer, similar to past research (e.g., Barros et al., 2019; Carter et al., 2014; Carter \& Patterson, 2012).
+Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown).
+To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial.
+Next, we computed total estimation error (EE) using the equation:
+\begin{equation}
+EE = \sqrt{CE^2 + VE^2}
+\end{equation}
+where \(CE\) was the average estimation bias and \(VE\) was the standard deviation of these errors. This approach is consistent with that used by Bruechert et al. (2003).
+
+\hypertarget{error-estimation-in-retention-and-transfer}{%
+\subsection{Error estimation in retention and transfer}\label{error-estimation-in-retention-and-transfer}}
+
+Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig.
+\ref{fig:figS3}) and timing (Fig.
+\ref{fig:figS4}) domains in Experiments 1 and 2.
+For the spatial estimation error, we found a significant main effect of Test in Experiment 1, \(F(1,148) = 32.40\), \(p < .001\), \(\eta_{G}^2 = .060\), and in Experiment 2, \(F(1,74) = 18.79\), \(p < .001\), \(\eta_{G}^2 = .026\), with more accurate estimations in retention than transfer.
+Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, \(F(1,148) = 7.12\), \(p = .008\), \(\eta_{G}^2 < .001\), we did not decompose the interaction as the effect size estimate was less than \(.001\).
+There were no significant main effects or interactions for timing estimation error in Experiment 2.
+A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed.
+Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.
+
+\clearpage
+
+\begin{figure}
+
+{\centering \includegraphics{../../figs/figS3}
+
+}
+
+\caption{\small \normalfont \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.}\label{fig:figS3}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{../../figs/figS4}
+
+}
+
+\caption{\small \normalfont \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.
+Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS4}
+\end{figure}
+
+\clearpage
+
+\hypertarget{development-of-error-estimation-skills}{%
+\subsection{Development of error estimation skills}\label{development-of-error-estimation-skills}}
+
+In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment.
+We found significant main effects of Test for both the spatial, \(F(1.45,104.67) = 20.72\), \(p < .001\), \(\eta_{G}^2 = .144\), and timing, \(F(1.10,79.40) = 46.88\), \(p < .001\), \(\eta_{G}^2 = .060\), error estimations.
+For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer (\(p\)'s \textless{} .001), and transfer had higher error than retention (\(p\) \textless{} .001).
+Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test (\(p\)'s \textless{} .001).
+In Experiment 2, none of the main effects or interactions were significant.
+
+\hypertarget{performance-accuracy-of-estimators-versus-non-estimators}{%
+\subsection{Performance accuracy of estimators versus non-estimators}\label{performance-accuracy-of-estimators-versus-non-estimators}}
+
+\textcolor{blue}{We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not.
+Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment.
+None of the main effect or interactions were significant in Experiment 1 or Experiment 2.
+A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation} (Guadagnoli \& Kohl, 2001)\textcolor{blue}{.
+Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation} (e.g., Chiviacowsky \& Wulf, 2005).
+\textcolor{blue}{Given recent support for this idea} (Bacelar et al., 2022)\textcolor{blue}{, it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.}
+
+\clearpage
+
+\hypertarget{supplementary-c}{%
+\section{Supplementary C}\label{supplementary-c}}
+
+\textcolor{blue}{Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity.
+Equivalence tests can be used to null findings more informative} (Harms \& Lakens, 2018; Lakens, 2017; Schuirmann, 1987)\textcolor{blue}{; however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons.
+First, we did not specify an \emph{a priori} smallest effect size of interest for any of the psychological constructs.
+Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol.
+Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points.
+We instead report mean differences and 90\% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments.
+The present experiments can be considered inconsistent with all effects larger than $g = \pm$ the largest absolute confidence interval bound presented in} Table \ref{tab:tableS1}.
+
+\vspace{1em}
+
+\begin{table}[h!]
+
+\caption{\label{tab:tableS1}Effect sizes for each questionnaire at each timepoint.}
+\resizebox{\linewidth}{!}{
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{11em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{After pre-test} & \multicolumn{2}{c}{After block 1} & \multicolumn{2}{c}{After block 6} & \multicolumn{2}{c}{Before retention} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
+Questionnaire & $g$ & 90\% CI & $g$ & 90\% CI & $g$ & 90\% CI & $g$ & 90\% CI\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{9}{l}{\textbf{Experiment 1}}\\
+\hspace{1em}Perceived autonomy & .10 & {}[-.17, .36] & .22 & {}[-.05, .49] & .32 & {}[.05, .59] & .28 & {}[.01, .55]\\
+\hspace{1em}Perceived competence & .07 & {}[-.19, .34] & .10 & {}[-.17, .36] & -.12 & {}[-.38, .15] & -.11 & {}[-.37, .16]\\
+\hspace{1em}Intrinsic motivation & .27 & {}[0, .54] & .20 & {}[-.07, .46] & .17 & {}[-.09, .44] & .15 & {}[-.11, .42]\\
+\addlinespace[0.3em]
+\multicolumn{9}{l}{\textbf{Experiment 2}}\\
+\hspace{1em}Perceived autonomy & -.02 & {}[-.29, .24] & .12 & {}[-.15, .39] & .15 & {}[-.11, .42] & -.03 & {}[-.30, .23]\\
+\hspace{1em}Perceived competence & .12 & {}[-.15, .38] & -.08 & {}[-.35, .18] & .22 & {}[-.05, .49] & .10 & {}[-.16, .37]\\
+\hspace{1em}Intrinsic motivation & -.31 & {}[-.58, -.04] & -.22 & {}[-.48, .05] & -.20 & {}[-.46, .07] & -.17 & {}[-.43, .10]\\
+\bottomrule
+\multicolumn{9}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase. Negative values favor yoked group.}\\
+\end{tabular}}
+\end{table}
+
+\clearpage
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-bacelar2022}{}}%
+Bacelar, M.
+F.
+B., Parma, J.
+O., Cabral, D., Daou, M., Lohse, K.
+R., \& Miller, M.
+W.
+(2022).
+Dissociating the contributions of motivational and information processing factors to the self-controlled feedback learning benefit.
+\emph{Psychology of Sport and Exercise}, \emph{59}, 102119.
+\url{https://doi.org/10.1016/j.psychsport.2021.102119}
+
 \leavevmode\vadjust pre{\hypertarget{ref-barros2019}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-chiviacowsky2005}{}}%
+Chiviacowsky, S., \& Wulf, G.
+(2005).
+Self-controlled feedback is effective if it is based on the learner's performance.
+\emph{Research Quarterly for Exercise and Sport}, \emph{76}(1), 42--48.
+\url{https://doi.org/10.1080/02701367.2005.10599260}
+
+\leavevmode\vadjust pre{\hypertarget{ref-guadagnoli2001}{}}%
+Guadagnoli, M.
+A., \& Kohl, R.
+M.
+(2001).
+Knowledge of results for motor learning: Relationship between error estimation and knowledge of results frequency.
+\emph{Journal of Motor Behavior}, \emph{33}(2), 217--224.
+
+\leavevmode\vadjust pre{\hypertarget{ref-harms2018}{}}%
+Harms, C., \& Lakens, D.
+(2018).
+Making 'null effects' informative: Statistical techniques and inferential frameworks.
+\emph{Translational Research}, \emph{3}(Suppl 2), 382--393.
+\url{https://doi.org/10.18053/jctres.03.2017S2.007}
+
 \leavevmode\vadjust pre{\hypertarget{ref-harrell1982}{}}%
@@
 Hochberg, Y. (1988). A sharper bonferroni procedure for multiple tests of significance. \emph{Biometrika}, \emph{75}(4), 800--802. \url{https://doi.org/10.1093/biomet/75.4.800}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lakens2017}{}}%
+Lakens, D.
+(2017).
+Equivalence tests: {A} practical primer for t tests, correlations, and meta-analyses.
+\emph{Social Psychological and Personality Science}, \emph{8}(4), 355--362.
+\url{https://doi.org/10.1177/1948550617697177}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-schuirmann1987}{}}%
+Schuirmann, D.
+J.
+(1987).
+A comparison of the Two One-Sided Tests Procedure and the Power Approach for assessing the equivalence of average bioavailability.
+\emph{Journal of Pharmacokinetics and Biopharmaceutics}, \emph{15}(6), 657--680.
+\url{https://doi.org/10.1007/BF01068419}
+
 \leavevmode\vadjust pre{\hypertarget{ref-wilcox2021}{}}%

### 2022-08-14 docs/revision-1/r1_manuscript.tex

--- 2022-05-06 docs/submission/manuscript.tex
@@
 {}{\PatchFailed}
-\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention\newline\indent Word count: 2978 for Introduction, Results, and Discussion}
+\keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
 \usepackage{lineno}
@@
 \usepackage{setspace}
-\pagewiselinenumbers
 \raggedbottom
@@
 
-\noindent \textbf{Corresponding authors:} Michael J.
-Carter (\href{mailto:michaelcarter@mcmaster.ca}{\nolinkurl{michaelcarter@mcmaster.ca}}) or Laura St.~Germain (\href{mailto:stgerml@mcmaster.ca}{\nolinkurl{stgerml@mcmaster.ca}})
+\noindent \textbf{Corresponding authors:} Laura St.~Germain (\href{mailto:stgerml@mcmaster.ca}{\nolinkurl{stgerml@mcmaster.ca}}) or Michael J.
+Carter (\href{mailto:cartem11@mcmaster}{\nolinkurl{cartem11@mcmaster}}; \href{mailto:motorlab@mcmaster.ca}{\nolinkurl{motorlab@mcmaster.ca}})
 
@@
 Knowledge of results feedback (Salmoni et al., 1984) can provide varying amounts of information to learners depending on its characteristics.
-Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., ``too far''), and binary feedback indicates only success or failure information (e.g., ``miss'') (Luft, 2014).
-When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
+Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., ``too far''), and binary feedback indicates only success or failure information (e.g., ``miss'') (Luft, 2014).\footnote{\textcolor{blue}{Others have referred to error feedback as quantitative feedback and graded feedback as qualitative feedback} (e.g., Magill \& Wood, 1986)\textcolor{blue}{.
+We use the terminology error, graded, and binary feedback because graded and binary feedback are different forms of qualitative feedback.}} When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
 These self-controlled feedback schedules have typically enhanced motor skill learning compared to yoked feedback schedules, wherein learners experience the feedback schedule created by a self-controlled counterpart, but without any choice (see Sanli et al., 2013; Ste-Marie et al., 2020 for reviews).
@@
 Exercising choice over the color of golf balls to putt (Lewthwaite et al., 2015 Experiment 1) or the mat underneath a target (Wulf et al., 2018 Experiment 1), which picture to hang in a lab (Lewthwaite et al., 2015 Experiment 2), hand order in a maximal force production task (Iwatsuki et al., 2017), which photos to look at while running (Iwatsuki et al., 2018), and the order of exercises to perform (Wulf et al., 2014) have been suggested to improve motor performance or learning.
-Other research, however, have failed to replicate this benefit of task-irrelevant or incidental choices on motor performance or learning (Carter \& Ste-Marie, 2017a; Grand et al., 2017; McKay \& Ste-Marie, 2020a, 2020b).
+Other research, however, have failed to replicate this benefit of task-irrelevant or incidental choices on motor performance or learning (Carter \& Ste-Marie, 2017a; Grand et al., 2017; McKay \& Ste-Marie, 2020, 2022).
 
@@
 
-To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we provided participants in choice and yoked (i.e., no-choice) groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) during the acquisition of a rapid aiming task.
-Motor learning was assessed using delayed (\textasciitilde24 hours) retention and transfer tests.
+To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, \textcolor{blue}{we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task.
+In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage.
+Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback.
+As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.} Motor learning was assessed using delayed (\textasciitilde24 hours) retention and transfer tests.
 If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule \emph{would not matter} for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups.
@@
 One hundred and fifty-two right-handed (Oldfield, 1971), healthy adults participated in Experiment 1 (\(M_{age}\) = 20.64 years, \(SD_{age}\) = 2.45, 88 females).
-Sample size was determined from an \emph{a-priori} power analysis using the \emph{ANOVA: fixed effects, main effects and interactions} option in G*Power (Faul et al., 2009) with the following parameters: \(\alpha\) = 0.05, \(\beta\) = .20, \(f\) = 0.23, numerator = 1, and groups = 2.
+Sample size was determined from an \emph{a-priori} power analysis using the \emph{ANOVA: fixed effects, main effects and interactions} option in G*Power (Faul et al., 2009) with the following parameters: \(\alpha\) = 0.05, \(\beta\) = .20, \(f\) = 0.23, numerator = 1, and groups = \textcolor{blue}{4}.
 This revealed a required sample of 151 participants.
-Our chosen effect size was based on a meta-analytic estimate (\(f\) = .32) by McKay et al.
+Our chosen effect size was based on a meta-analytic estimate (\emph{f} = .32) by McKay et al.
 (2014); however, we used a more conservative estimate given the uncertainty of how choice would interact with our feedback characteristic manipulation.
@@
 Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals.
-Additionally, half of the participants in each group were randomly selected to estimate their performance on the spatial and timing goals after each trial in the pre-test.
+Additionally, half of the participants in each group were randomly selected to \textcolor{blue}{verbally} estimate their performance on the spatial and timing goals after each trial in the pre-test.
 Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested (e.g., Chiviacowsky \& Wulf, 2005) to be adopted spontaneously by participants controlling their feedback schedule.
@@
 Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected (or imposed on the yoked groups), it was also displayed for 3000 ms.
-
-Before the retention and transfer tests, participants were reminded about the task and its associated goals.
-All participants were asked to estimate their performance after each trial in retention and transfer.
-After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.
-The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a).
-Cronbach's alpha values for each questionnaire at each time point are reported in Table \ref{tab:table1}.
-
-\hypertarget{experiment-2-1}{%
-\subsubsection{Experiment 2}\label{experiment-2-1}}
-
-Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 22.37 years, \(SD_{age}\) = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 18.00 years, \(SD_{age}\) = 0.93, 28 females).
-Binary feedback for the spatial goal was provided as ``hit'' if performance was exactly 40 degrees (or 60 degrees in transfer) and as ``miss'' for everything else.
-For the timing goal, binary feedback was provided as ``hit'' when performance was exactly 225 ms and as ``miss'' for everything else.
-Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
+\textcolor{blue}{The number of remaining feedback trials was also displayed during this feedback delay interval.} If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected via \textcolor{blue}{verbal response} (or imposed on the yoked groups), it was also displayed for 3000 ms.
+
+\clearpage
 
@@
 
-\caption{\small \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
+\caption{\small \normalfont \onehalfspacing \textbf{Overview of a typical acquisition trial for the choice groups.} The sequence of events a participant in the choice groups experienced during the acquisition phase.
 Trials began by informing participants the trial number (500 ms) they were on in acquisition.
@@
 On trials where feedback was not requested, a blank screen \textbf{(A)} was shown for 3000 ms.
-When feedback was selected, feedback was provided for both the spatial and timing goals according to their experimental group.
+When feedback was selected via \textcolor{blue}{verbal response}, feedback was provided for both the spatial and timing goals according to their experimental group.
 The error feedback group \textbf{(B)} saw their constant error, the graded feedback group \textbf{(C)} saw either ``too far'' or ``too short'' for the spatial goal and ``too fast'' or ``too slow'' for the timing goal, and the binary feedback group \textbf{(D)} saw either ``hit'' or ``miss'' for the task goals.
@@
 \end{figure}
+
+\clearpage
 
@@
 
+Before the retention and transfer tests, participants were reminded about the task and its associated goals.
+All participants were asked to \textcolor{blue}{verbally} estimate their performance after each trial in retention and transfer.
+After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants \textcolor{blue}{verbally} answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.\footnote{\textcolor{blue}{The questionnaires can be found in the publicly available project repository in the materials directory.}} The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a; St.
+Germain et al., 2022).
+Cronbach's alpha values for each questionnaire at each time point are reported in Table \ref{tab:table1}.
+
+\hypertarget{experiment-2-1}{%
+\subsubsection{Experiment 2}\label{experiment-2-1}}
+
+Similar to Experiment 1, the first half of participants were assigned to the Choice+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 22.37 years, \(SD_{age}\) = 3.13, 19 females) and the remaining participants were assigned to the Yoked+Binary-Feedback group (\(n\) = 38; \(M_{age}\) = 18.00 years, \(SD_{age}\) = 0.93, 28 females).
+Binary feedback for the spatial goal was provided as ``hit'' if performance was exactly 40 degrees (or 60 degrees in transfer) and as ``miss'' for everything else.
+For the timing goal, binary feedback was provided as ``hit'' when performance was exactly 225 ms and as ``miss'' for everything else.
+Data collection was identical to that of Experiment 1, except in the acquisition instructions participants in both groups were shown a sample binary feedback display and were asked to interpret it aloud for the researcher to verify understanding.
+
 \hypertarget{data-analysis}{%
@@
 To test for performance differences during acquisition, total error for the spatial and timing goals during acquisition were analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 6 Block; \emph{Experiment 2:} 2 Choice x 6 Block).
+Model diagnostics of total error for the spatial and timing goals revealed skewed distributions.
+We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions (Rousselet \& Wilcox, 2020; Wilcox, 2021).
+The results of these analyses (see \textbf{Supplementary A}) were consistent with those of the mixed ANOVAs, which we report below.
 Our primary psychological outcome variables were intrinsic motivation (i.e., interest/enjoyment), perceived competence, and perceived autonomy.
 The mean score of the responses for these constructs at each time point was calculated for each participant and analyzed in separate mixed ANOVAs (\emph{Experiment 1:} 2 Choice x 2 Feedback x 4 Time; \emph{Experiment 2:} 2 Choice x 4 Time).
-Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50\% of the participants in each group in Experiments 1 and 2), retention, and transfer (see \textbf{Supplementary A}).
+Of secondary interest, error estimation abilities were assessed as total error between a participant's estimation and actual performance in pre-test (50\% of the participants in each group in Experiments 1 and 2), retention, and transfer (see \textbf{Supplementary B}).
 
@@
 
-Model diagnostics of total error for the spatial and timing goals revealed skewed distributions.
-We therefore conducted sensitivity analyses using the shift function, which is a robust statistical method well-suited for skewed distributions (Rousselet \& Wilcox, 2020; Wilcox, 2021).
-The results of these analyses (see \textbf{Supplementary B}) were consistent with those of the mixed ANOVAs, which we report below.
-
 \hypertarget{pre-test-retention-and-transfer}{%
@@
 A main effect of Test was also found for timing error, \(F(1.08,160.23) = 81.21\), \(p < .001\), \(\eta_{G}^2 = .245\), with pre-test performance more errorful than both retention and transfer (\(p\)'s \textless{} .001), and retention was less errorful than transfer (\(p\) \textless{} .001).
+\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,148) = .52$, $p = .471$, $\eta_{G}^2 = .001$, and timing, $F(1,148) = .32$, $p = .547$, $\eta_{G}^2 < .001$, error.}
 
@@
 \ref{fig:fig3}B) error did not change considerably from the pre-test to the retention and transfer tests.
-There were no significant main effects or interactions for either task goals.
-
-\hypertarget{acquisition}{%
-\subsection{Acquisition}\label{acquisition}}
-
-\hypertarget{experiment-1-3}{%
-\subsubsection{Experiment 1}\label{experiment-1-3}}
-
-All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
-\ref{fig:fig2}A).
-This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)).
-Timing error also decreased during the acquisition period (Fig.
-\ref{fig:fig2}B).
-The significant main effect of Block, \(F(1.75,259.59) = 55.44\), \(p < .001\), \(\eta_{G}^2 = .138\), was superseded by a significant Feedback x Block interaction, \(F(1.75, 259.59) = 3.56\), \(p = .035\), \(\eta_{G}^2 = .010\).
-Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)), but performance plateaued from block 2 onward in acquisition (\(p\)'s \(\geq .257\)).
-Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).
-
-\vspace{2ex}
+\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,74) = .23$, $p = .631$, $\eta_{G}^2 = .002$, and timing, $F(1,74) = .11$, $p = .738$, $\eta_{G}^2 = .001$, error.} All other main effects and interactions were also not significant.
+
+\clearpage
 
@@
 
-\caption{\small \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses.
+\caption{\small \normalfont \onehalfspacing \textbf{Experiment 1 data.} The Choice with error feedback (Choice+Error) group is shown in dark blue circles, the Choice with graded feedback (Choice+Graded) group is shown in light blue squares, the Yoked with error feedback (Yoked+Error) group is shown in red triangles, and the Yoked with graded feedback (Yoked+Graded) group is shown in yellow crosses.
 Error bars denote 95\% bootstrapped confidence intervals.
@@
 
-\hypertarget{experiment-2-3}{%
-\subsubsection{Experiment 2}\label{experiment-2-3}}
-
-Spatial (Fig.
-\ref{fig:fig3}A) and timing (Fig.
-\ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-None of the main effects or interactions for either task goals were significant.
-
-\vspace{2ex}
+\clearpage
 
@@
 
-\caption{\small \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares.
+\caption{\small \normalfont \onehalfspacing \textbf{Experiment 2 data.} The Choice with binary feedback (Choice+Binary) group is shown in green circles and the Yoked with binary feedback (Yoked+Binary) group is shown in purple squares.
 Error bars denote 95\% bootstrapped confidence intervals.
@@
 
+\clearpage
+
+\hypertarget{acquisition}{%
+\subsection{Acquisition}\label{acquisition}}
+
+\hypertarget{experiment-1-3}{%
+\subsubsection{Experiment 1}\label{experiment-1-3}}
+
+All groups of participants improved their performance of the spatial goal during the acquisition phase (Fig.
+\ref{fig:fig2}A).
+This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .06$, $p = .813$ $\eta_{G}^2 < .001$.} Timing error also decreased during the acquisition period (Fig.
+\ref{fig:fig2}B).
+The significant main effect of Block, \(F(1.75,259.59) = 55.44\), \(p < .001\), \(\eta_{G}^2 = .138\), was superseded by a significant Feedback x Block interaction, \(F(1.75, 259.59) = 3.56\), \(p = .035\), \(\eta_{G}^2 = .010\).
+Post hoc comparisons showed that timing error for those receiving error feedback was reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)), but performance plateaued from block 2 onward in acquisition (\(p\)'s \(\geq .257\)).
+Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .54$, $p = .465$ $\eta_{G}^2 = .002$.} Descriptives for the number of ``hit'' trials for each group are provided in Table \ref{tab:table2}.
+
+\hypertarget{experiment-2-3}{%
+\subsubsection{Experiment 2}\label{experiment-2-3}}
+
+Spatial (Fig.
+\ref{fig:fig3}A) and timing (Fig.
+\ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period.
+\textcolor{blue}{The main effect of Choice for both the spatial, $F(1,74) = .08$, $p = .776$, $\eta_{G}^2 < .001$, and the timing, $F(1,74) = .37$, $p = .542$, $\eta_{G}^2 = .004$, goals were not significant.
+Al other main effects and interactions for both task goals were not significant.} Descriptives for the number of ``hit'' trials for each group are provided in Table \ref{tab:table2}.
+
+\begin{table}
+
+\caption{\label{tab:table2}Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.}
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{15em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{5em}}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Spatial goal} & \multicolumn{2}{c}{Timing goal} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
+Group & Total & Min--Max & Total & Min--Max\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Experiment 1}}\\
+\hspace{1em}Choice+Error-Feedback & 4 & 0--2 & 30 & 0--4\\
+\hspace{1em}Choice+Graded-Feedback & 2 & 0--1 & 26 & 0--4\\
+\hspace{1em}Yoked+Error-Feedback & 1 & 0--1 & 28 & 0--3\\
+\hspace{1em}Yoked+Graded-Feedback & 3 & 0--1 & 33 & 0--3\\
+\addlinespace[0.3em]
+\multicolumn{5}{l}{\textbf{Experiment 2}}\\
+\hspace{1em}Choice+Binary-Feedback & 2 & 0--1 & 14 & 0--3\\
+\hspace{1em}Yoked+Binary-Feedback & 4 & 0--1 & 10 & 0--2\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \hypertarget{psychological-variables}{%
@@
 Perceptions of autonomy (Fig.
-\ref{fig:fig2}C) showed a slight decrease across time points, supported by a main effect of Time, \(F(2.25,332.95) = 3.69\), \(p < .022\), \(\eta_{G}^2 = .003\).
+\ref{fig:fig2}C) showed a slight decrease across time points, supported by a main effect of Time, \(F(2.25,332.95) = 3.69\), \(p = .022\), \(\eta_{G}^2 = .003\).
 Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test (\(p = .031\)).
-Self-ratings for perceived competence (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 2.38$, $p = .125$, $\eta_{G}^2 = .014$.} Self-ratings for perceived competence (Fig.
 \ref{fig:fig2}D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic.
@@
 Perceived competence scores were not significantly different after the pre-test (\(p = .232\)); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points (\(p\)'s \(< .001\)).
-Self-reported scores for intrinsic motivation (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 0.03$, $p = .862$, $\eta_{G}^2 < .001$.} Self-reported scores for intrinsic motivation (Fig.
 \ref{fig:fig2}E) generally decreased after block 1, which was supported by a main effect of Time, \(F(2.40,355.90) = 14.69\), \(p < .001\), \(\eta_{G}^2 = .012\).
@@
 Self-reported ratings were also lower before retention compared to after the pre-test (\(p = .043\)).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 1.69$, $p = .195$, $\eta_{G}^2 = .010$.}
 
@@
 \ref{fig:fig3}C) were similar across all time points.
-There were no main effects or interactions.
-Perceptions of competence (Fig.
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.07$, $p = .792$, $\eta_{G}^2 < .001$.
+All other main effects and interactions were also not significant.} Perceptions of competence (Fig.
 \ref{fig:fig3}D) showed a considerable decrease after the pre-test, \(F(1.85,136.91) = 106.10\), \(p < .001\), \(\eta_{g}^2 = .298\), where scores were significantly greater after the pre-test compared to all other time points (\(p\)'s \(< .001\)), and were higher after block 1 of acquisition than before retention (\(p = .004\)).
-Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, \(F(2.37,175.55) = 15.31\), \(p < .001\), \(\eta_{G}^2 = .018\).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.25$, $p = .620$, $\eta_{G}^2 = .002$.} Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, \(F(2.37,175.55) = 15.31\), \(p < .001\), \(\eta_{G}^2 = .018\).
 Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention (\(p\)'s \(< .001\)), and higher after block 1 than after block 6 and before retention (\(p\)'s \(< .026\)).
+\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 1.04$, $p = .312$, $\eta_{G}^2 < .013$.}
 
@@
 
-Our main comparison of interest was between choice and no-choice (i.e., yoked groups).
-To evaluate the self-controlled learning effect observed across Experiments 1 and 2, Hedges' \emph{g} for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies.
-Next, a random effects meta-analysis was conducted on the retention test data\footnote{We report an estimate for retention tests to facilitate comparison to a recent meta-analysis (McKay et al., in-press) that produced estimated effects of self-controlled learning at retention specifically.} to generate a summary point estimate and 90\% confidence intervals (CI).
-This resulted in an overall estimated effect of \(g = .05\) (favoring self-controlled) and \(90\% \,CI \,[-.12,.23]\).
+Our main comparison of interest was between choice and yoked (i.e., no-choice) groups.
+To evaluate the self-controlled learning effect, Hedges' \emph{g} for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies \textcolor{blue}{(see \textbf{Supplementary C} for the psychological data).
+Next, random effects meta-analyses were conducted on the retention test data}\footnote{We report an estimate for retention tests to facilitate comparison to a recent meta-analysis (McKay et al., in-press) that produced estimated effects of self-controlled learning at retention specifically.} to generate a summary point estimate and 90\% confidence intervals (CI) \textcolor{blue}{with Experiments 1 and 2 combined and also separate.
+The overall estimated effect when combining both experiments} was \(g\) = .05 (favoring self-controlled) and 90\% CI {[}-.12, .23{]}.
+\textcolor{blue}{The overall estimated effect for Experiment 1 was $g$ = .03 (favoring self-controlled) and 90\% CI [-.19, .25].
+For Experiment 2, it was $g$ = .09 (favoring self-controlled) and 90\% CI [-.19, .37].}
 
@@
 All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not.
-Therefore, the present experiments can be considered inconsistent with all effects larger than \(g = \pm.23\).
+Based on the \textcolor{blue}{combined overall estimate} the present experiments can be considered inconsistent with all effects larger than \(g = \pm.23\).
 
@@
 According to the OPTIMAL theory (Wulf \& Lewthwaite, 2016), self-controlled practice or choice conditions are advantageous because the provision of choice increases perceptions of autonomy and competence, which increase intrinsic motivation and ultimately both motor performance and learning.
-Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals (Carter et al., 2014; Carter \& Ste-Marie, 2017b; Grand et al., 2015).
+Conversely, others have argued that self-controlled feedback is effective because it provides the opportunity to request feedback in a performance dependent way that reduces uncertainty about movement outcomes relative to task goals (Carter et al., 2014; Carter \& Ste-Marie, 2017b; Grand et al., 2015) to enhance error detection and correction abilities (Barros et al., 2019; Carter et al., 2014; Chiviacowsky \& Wulf, 2005).
 In contrast to these predictions, we did not find evidence that providing learners with choice over their feedback schedule was beneficial for motor learning, despite collecting a much larger sample (\emph{N} = 228 across both Experiments) than those commonly used in self-controlled learning experiments (median sample size \emph{N} = 36 in a meta-analysis by McKay et al., in-press) and motor learning experiments in general (median \emph{n}/group = 11 in a review by Lohse et al., 2016).
@@
 The failed replication of a self-controlled learning advantage was surprising given the dominant view for the past 25 years has been that it is a robust effect and one that should be recommended to coaches and practitioners (Sanli et al., 2013; Ste-Marie et al., 2020; Wulf \& Lewthwaite, 2016).
-Our findings are, however, consistent with a growing list of relatively large--often pre-registered--experiments that have not found self-controlled learning benefits (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press).
+Our findings are, however, consistent with a growing list of relatively large--often pre-registered--experiments that have not found self-controlled learning benefits (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020, 2022; St.
+Germain et al., 2022; Yantha et al., in-press).
 One possible explanation for this discrepancy between earlier and more recent experiments may be that the self-controlled learning advantage was the result of underpowered designs, which has been highlighted as a problem in motor learning research (see Lohse et al., 2016 for a discussion).
@@
 Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results (McKay et al., in-press).
-We estimated the overall effect of self-controlled practice in retention to be significantly smaller than any effect larger than \(g = .23\).
+We estimated the overall effect of self-controlled practice in retention \textcolor{blue}{collapsed across experiments} to be significantly smaller than any effect larger than \(g = .23\).
 This is consistent with the estimates from McKay et al.
@@
 
-Given our current replication failure with those in recent years (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press) and the conclusions from McKay et al.
+Given our current replication failure with those in recent years (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020, 2022; St.
+Germain et al., 2022; Yantha et al., in-press) and the conclusions from McKay et al.
 (in-press), motivational (i.e., OPTIMAL theory) versus information-processing explanations seem moot.
-Nevertheless, the present results are incompatible with both perspectives.
-Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
-Similarly, self-controlled feedback schedules did not enhance error estimation skills (see \textbf{Supplementary A}) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
+Nevertheless, the present results are incompatible with both perspectives.\footnote{\textcolor{blue}{Although the lack of performance improvements in Experiment 2 are compatible with the information-processing perspective, we do not interpret this as support for this view over the motivational one given the conclusions from McKay and colleagues' (in-press) recent meta-analysis.}} Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
+Similarly, self-controlled feedback schedules did not enhance error estimation skills \textcolor{blue}{compared to yoked schedules} (see \textbf{Supplementary B}) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
 Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose.
@@
 Although the present experiments were not pre-registered, the analysis plan was determined prior to viewing the data.
-In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see \textbf{Supplementary B}).
-The sensitivity analyses supported the conclusions of the primary analyses and are consistent with research that has followed pre-registered analysis plans (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020a, 2020b; St Germain et al., in-press; Yantha et al., in-press).
+In addition, a suite of sensitivity analyses were conducted to determine the extent to which the present results depended on the chosen analysis methods (see \textbf{Supplementary A}).
+The sensitivity analyses supported the conclusions of the primary analyses and are consistent with research that has followed pre-registered analysis plans (Bacelar et al., 2022; Grand et al., 2017; Leiker et al., 2019; McKay \& Ste-Marie, 2020, 2022; St.
+Germain et al., 2022; Yantha et al., in-press).
 Lastly, our results and conclusions are in line with a recent meta-analysis (McKay et al., in-press) that suggests the apparent benefits of self-controlled practice are due to selection bias rather than true effects.
@@
 \noindent
-\textbf{Funding.} ~This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University.
+\textbf{Funding.} ~This work was supported by the Natural Sciences and Engineering Research Council (NSERC) of Canada (RGPIN-2018-05589; MJC) and McMaster University (MJC).
 LSG was supported by an NSERC Postgraduate Scholarship.
@@
 \noindent
-\textbf{Authors' contributions using CRediT.} ~Laura St.~Germain served as lead for data curation, formal analysis,investigation - performed experiment, project administration, and software - task programming, writing - original draft preparation, and writing - review and editing, contributed equally to conceptualization, methodology, validation, and visualization.
-Brad McKay contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing.
-Andrew Poskus served as a lead for investigation - performed experiment and served in a supporting role for writing- original draft preparation and writing - review and editing.
-Allison Williams served as a lead for investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing.
-Olena Leshchyshen contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing.
-Sherry Feldman contributed equally to investigation - performed experiment and served in a supporting role for writing - original draft preparation and writing - review and editing.
-Joshua G.A.
-Cashaback contributed equally to conceptualization, methodology, writing - original draft preparation, and writing - review and editing.
-Michael J.
-Carter served as lead for funding acquisition, resources, and supervision, contributed equally to conceptualization, methodology, validation, visualization, writing - original draft preparation, and writing - review and editing, and served in a supporting role for data curation, formal analysis, project administration, and software - task programming.
+\textbf{Authors' contributions using CRediT.} ~Conceptualization (LSG, BM, JGAC, MJC); Data curation (LSG, BM, MJC); Formal analysis (LSG); Funding acquisition (MJC); Investigation (LSG, AP, AW, OL, SF); Methodology (LSG, BM, JGAC, MJC); Project administration (LSG, MJC); Software (LSG, MJC); Supervision (LSG, MJC); Validation (BM, MJC); Visualization (LSG, BM, JGAC, MJC); Writing -- original draft (LSG, BM, AP, AW, OL, SF, JGAC, MJC); Writing -- review \& editing (LSG, BM, AP, AW, OL, SF, JGAC, MJC)
 
@@
 (2002).
-Self-controlled feedback: {Does} it enhance learning because performers get feedback when they need it?
+Self-controlled feedback: Does it enhance learning because performers get feedback when they need it?
 \emph{Research Quarterly for Exercise and Sport}, \emph{73}(4), 408--415.
-\url{https://doi.org/10.1080/02701367.2002.10609040}
 
@@
 M.
-(2020a).
+(2020).
 Autonomy support and reduced feedback frequency have trivial effects on learning and performance of a golf putting task.
@@
 M.
-(2020b).
-Autonomy {Support} via {Instructionally} {Irrelevant} {Choice} {Not} {Beneficial} for {Motor} {Performance} or {Learning}.
-\emph{Research Quarterly for Exercise and Sport}, 1--13.
+(2022).
+Autonomy support via instructionally irrelevant choice not beneficial for motor performance or learning.
+\emph{Research Quarterly for Exercise and Sport}, \emph{93}, 64--76.
 \url{https://doi.org/10.1080/02701367.2020.1795056}
@@
 \leavevmode\vadjust pre{\hypertarget{ref-stgermain2022}{}}%
-St Germain, L., Williams, A., Balbaa, N., Poskus, A., Leshchyshen, O., Lohse, K.
+St.
+Germain, L., Williams, A., Balbaa, N., Poskus, A., Leshchyshen, O., Lohse, K.
 R., \& Carter, M.
 J.
-(in-press).
+(2022).
 Increased perceptions of autonomy through choice fail to enhance motor skill retention.
-\emph{Journal of Experimental Psychology: Human Perception and Performance}.
-In-press.
+\emph{Journal of Experimental Psychology: Human Perception and Performance}, \emph{48}(4), 370--379.
 \url{https://doi.org/10.1037/xhp0000992}

### 2022-08-22 docs/preprint/preprint.Rmd
update: preprint and supplementary versions

--- 2022-08-14 docs/revision-1/r1_manuscript.Rmd
@@
 shorttitle        : "Choice and feedback characteristics"
-
-# note: |
-#   \vspace{5ex}
-#   \textcolor{orange}{\textbf{\emph{NOT PEER-REVIEWED}}}
 
@@
 In the information-processing view, choice allows learners to engage in performance-dependent strategies that reduce uncertainty about task outcomes.
-To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a \textcolor{blue}{novel motor} task with spatial and timing goals.
+To disentangle these potential explanations, we provided participants in choice and yoked groups with error or graded feedback (Experiment 1) and binary feedback (Experiment 2) while learning a novel motor task with spatial and timing goals.
 Across both experiments (N = 228 participants), we did not find evidence to support a self-controlled learning advantage.
@@
 footnotelist      : no
-linenumbers       : yes
+linenumbers       : no
 mask              : no
@@
 documentclass     : "apa7"
-classoption       : "man, donotrepeattitle"
+classoption       : "doc, donotrepeattitle"
 #fontsize          : 11pt
@@
   - \usepackage{setspace}
+  - \usepackage{tcolorbox}
   #- \pagewiselinenumbers
@@
   - \renewcommand\affiliation[1]{}
-  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St.
-Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A.
-Cashaback, Michael J.
-Carter\vspace{2ex}}
-  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
+  - \authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
+  - \authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
 ---
@@
 
+\vspace{-1.1em}
+\begin{center}
+\begin{tcolorbox}[colframe=blue!75!black,boxrule=0.75pt,arc=5pt,width=4in]
+\centering\textcolor{blue!75!black}{In-press at \emph{Psychonomic Bulletin \& Review}}
+\end{tcolorbox}
+\end{center}
+\vspace{0.5em}
+
 The underlying source of errors in skilled actions are often ambiguous and difficult to assign as the learner must rely on noisy and delayed sensory information.
@@
 
-[^1]: \textcolor{blue}{Others have referred to error feedback as quantitative feedback and graded feedback as qualitative feedback} [e.g., @magill1986]\textcolor{blue}{.
-We use the terminology error, graded, and binary feedback because graded and binary feedback are different forms of qualitative feedback.}
+[^1]: Others have referred to error feedback as quantitative feedback and graded feedback as qualitative feedback [e.g., @magill1986].
+We use the terminology error, graded, and binary feedback because graded and binary feedback are different forms of qualitative feedback.
 
@@
 
-To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, \textcolor{blue}{we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task.
+To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acquisition of a novel motor task.
 In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage.
 Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback.
-As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.} Motor learning was assessed using delayed (~24 hours) retention and transfer tests.
+As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.
+Motor learning was assessed using delayed (~24 hours) retention and transfer tests.
 If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule *would not matter* for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups.
@@
 One hundred and fifty-two right-handed [@oldfield1971], healthy adults participated in Experiment 1 ($M_{age}$ = 20.64 years, $SD_{age}$ = 2.45, 88 females).
-Sample size was determined from an *a-priori* power analysis using the *ANOVA: fixed effects, main effects and interactions* option in G\*Power [@faul2009] with the following parameters: $\alpha$ = 0.05, $\beta$ = .20, $f$ = 0.23, numerator = 1, and groups = \textcolor{blue}{4}.
+Sample size was determined from an *a-priori* power analysis using the *ANOVA: fixed effects, main effects and interactions* option in G\*Power [@faul2009] with the following parameters: $\alpha$ = 0.05, $\beta$ = .20, $f$ = 0.23, numerator = 1, and groups = 4.
 This revealed a required sample of 151 participants.
@@
 Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals.
-Additionally, half of the participants in each group were randomly selected to \textcolor{blue}{verbally} estimate their performance on the spatial and timing goals after each trial in the pre-test.
+Additionally, half of the participants in each group were randomly selected to verbally estimate their performance on the spatial and timing goals after each trial in the pre-test.
 Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested [e.g., @chiviacowsky2005] to be adopted spontaneously by participants controlling their feedback schedule.
@@
 
-A typical acquisition trial (see Figure \@ref(fig:fig1)) began with the current trial number displayed (500 ms), followed by a visual "Get Ready!" and a visual go-signal (800 ms apart).
-Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
-The computer screen was blank while participants made their movement.
-When participants returned to the starting position, a red circle was displayed on the monitor.
-Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-\textcolor{blue}{The number of remaining feedback trials was also displayed during this feedback delay interval.} If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected via \textcolor{blue}{verbal response} (or imposed on the yoked groups), it was also displayed for 3000 ms.
-
 \clearpage
@@
 On trials where feedback was not requested, a blank screen **(A)** was shown for 3000 ms.
-When feedback was selected via \textcolor{blue}{verbal response}, feedback was provided for both the spatial and timing goals according to their experimental group.
+When feedback was selected via verbal response, feedback was provided for both the spatial and timing goals according to their experimental group.
 The error feedback group **(B)** saw their constant error, the graded feedback group **(C)** saw either "too far" or "too short" for the spatial goal and "too fast" or "too slow" for the timing goal, and the binary feedback group **(D)** saw either "hit" or "miss" for the task goals.
@@
   kable_styling(position = "left",
-                font_size = 11) %>%
+                font_size = 11,
+                latex_options = "scale_down") %>%
   column_spec(1, width = "12em") %>%
@@
 
+A typical acquisition trial (see Figure \@ref(fig:fig1)) began with the current trial number displayed (500 ms), followed by a visual "Get Ready!" and a visual go-signal (800 ms apart).
+Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
+The computer screen was blank while participants made their movement.
+When participants returned to the starting position, a red circle was displayed on the monitor.
+Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
+The number of remaining feedback trials was also displayed during this feedback delay interval.
+If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected via verbal response (or imposed on the yoked groups), it was also displayed for 3000 ms.
+
 Before the retention and transfer tests, participants were reminded about the task and its associated goals.
-All participants were asked to \textcolor{blue}{verbally} estimate their performance after each trial in retention and transfer.
-After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants \textcolor{blue}{verbally} answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.[^3] The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory [@mcauley1989; @ryan1982] and the perceived autonomy questions were used in earlier work [@barros2019; @carter2017b; @stgermain2022].
+All participants were asked to verbally estimate their performance after each trial in retention and transfer.
+After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants verbally answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.[^3] The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory [@mcauley1989; @ryan1982] and the perceived autonomy questions were used in earlier work [@barros2019; @carter2017b; @stgermain2022].
 Cronbach's alpha values for each questionnaire at each time point are reported in Table \@ref(tab:table1).
 
-[^3]: \textcolor{blue}{The questionnaires can be found in the publicly available project repository in the materials directory.}
+[^3]: The questionnaires can be found in the publicly available project repository in the materials directory.
 
@@
 A main effect of Test was also found for timing error, $F(1.08,160.23) = 81.21$, $p < .001$, $\eta_{G}^2 = .245$, with pre-test performance more errorful than both retention and transfer ($p$'s < .001), and retention was less errorful than transfer ($p$ < .001).
-\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,148) = .52$, $p = .471$, $\eta_{G}^2 = .001$, and timing, $F(1,148) = .32$, $p = .547$, $\eta_{G}^2 < .001$, error.}
+The main effect of Choice was not significant for both spatial, $F(1,148) = .52$, $p = .471$, $\eta_{G}^2 = .001$, and timing, $F(1,148) = .32$, $p = .547$, $\eta_{G}^2 < .001$, error.
 
@@
 \@ref(fig:fig3)B) error did not change considerably from the pre-test to the retention and transfer tests.
-\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,74) = .23$, $p = .631$, $\eta_{G}^2 = .002$, and timing, $F(1,74) = .11$, $p = .738$, $\eta_{G}^2 = .001$, error.} All other main effects and interactions were also not significant.
+The main effect of Choice was not significant for both spatial, $F(1,74) = .23$, $p = .631$, $\eta_{G}^2 = .002$, and timing, $F(1,74) = .11$, $p = .738$, $\eta_{G}^2 = .001$, error.
+All other main effects and interactions were also not significant.
 
@@
 This was supported by a significant main effect of Block, $F(2.41,357.13) = 60.18$, $p < .001$, $\eta_{G}^2 = .130$, where block 1 was less accurate than all other blocks ($p$'s $< .001$), block 2 was less accurate than all subsequent blocks ($p$'s $\leq .021$), and blocks 3 and 4 were more errorful than block 6 ($p$'s $\leq .015$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .06$, $p = .813$ $\eta_{G}^2 < .001$.} Timing error also decreased during the acquisition period (Fig.
+The main effect of Choice was not significant, $F(1,148) = .06$, $p = .813$ $\eta_{G}^2 < .001$.
+Timing error also decreased during the acquisition period (Fig.
 \@ref(fig:fig2)B).
@@
 Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks ($p$'s $< .001$); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 ($p$'s $\leq .028$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .54$, $p = .465$ $\eta_{G}^2 = .002$.} Descriptives for the number of "hit" trials for each group are provided in Table \@ref(tab:table2).
+The main effect of Choice was not significant, $F(1,148) = .54$, $p = .465$ $\eta_{G}^2 = .002$.
+Descriptives for the number of "hit" trials for each group are provided in Table \@ref(tab:table2).
 
@@
 \@ref(fig:fig3)B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-\textcolor{blue}{The main effect of Choice for both the spatial, $F(1,74) = .08$, $p = .776$, $\eta_{G}^2 < .001$, and the timing, $F(1,74) = .37$, $p = .542$, $\eta_{G}^2 = .004$, goals were not significant.
-Al other main effects and interactions for both task goals were not significant.} Descriptives for the number of "hit" trials for each group are provided in Table \@ref(tab:table2).
+The main effect of Choice for both the spatial, $F(1,74) = .08$, $p = .776$, $\eta_{G}^2 < .001$, and the timing, $F(1,74) = .37$, $p = .542$, $\eta_{G}^2 = .004$, goals were not significant.
+Al other main effects and interactions for both task goals were not significant.
+Descriptives for the number of "hit" trials for each group are provided in Table \@ref(tab:table2).
 
@@
   kable_styling(position = "left",
-                font_size = 11) %>%
+                font_size = 11,
+                latex_options = "scale_down") %>%
   column_spec(1, width = "15em") %>%
@@
 Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test ($p = .031$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 2.38$, $p = .125$, $\eta_{G}^2 = .014$.} Self-ratings for perceived competence (Fig.
+The main effect of Choice was not significant, $F(1,148) = 2.38$, $p = .125$, $\eta_{G}^2 = .014$.
+Self-ratings for perceived competence (Fig.
 \@ref(fig:fig2)D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic.
@@
 Perceived competence scores were not significantly different after the pre-test ($p = .232$); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points ($p$'s $< .001$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 0.03$, $p = .862$, $\eta_{G}^2 < .001$.} Self-reported scores for intrinsic motivation (Fig.
+The main effect of Choice was not significant, $F(1,148) = 0.03$, $p = .862$, $\eta_{G}^2 < .001$.
+Self-reported scores for intrinsic motivation (Fig.
 \@ref(fig:fig2)E) generally decreased after block 1, which was supported by a main effect of Time, $F(2.40,355.90) = 14.69$, $p < .001$, $\eta_{G}^2 = .012$.
@@
 Self-reported ratings were also lower before retention compared to after the pre-test ($p = .043$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 1.69$, $p = .195$, $\eta_{G}^2 = .010$.}
+The main effect of Choice was not significant, $F(1,148) = 1.69$, $p = .195$, $\eta_{G}^2 = .010$.
 
@@
 \@ref(fig:fig3)C) were similar across all time points.
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.07$, $p = .792$, $\eta_{G}^2 < .001$.
-All other main effects and interactions were also not significant.} Perceptions of competence (Fig.
+The main effect of Choice was not significant, $F(1,74) = 0.07$, $p = .792$, $\eta_{G}^2 < .001$.
+All other main effects and interactions were also not significant.
+Perceptions of competence (Fig.
 \@ref(fig:fig3)D) showed a considerable decrease after the pre-test, $F(1.85,136.91) = 106.10$, $p < .001$, $\eta_{g}^2 = .298$, where scores were significantly greater after the pre-test compared to all other time points ($p$'s $< .001$), and were higher after block 1 of acquisition than before retention ($p = .004$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.25$, $p = .620$, $\eta_{G}^2 = .002$.} Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, $F(2.37,175.55) = 15.31$, $p < .001$, $\eta_{G}^2 = .018$.
+The main effect of Choice was not significant, $F(1,74) = 0.25$, $p = .620$, $\eta_{G}^2 = .002$.
+Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, $F(2.37,175.55) = 15.31$, $p < .001$, $\eta_{G}^2 = .018$.
 Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention ($p$'s $< .001$), and higher after block 1 than after block 6 and before retention ($p$'s $< .026$).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 1.04$, $p = .312$, $\eta_{G}^2 < .013$.}
+The main effect of Choice was not significant, $F(1,74) = 1.04$, $p = .312$, $\eta_{G}^2 < .013$.
 
@@
 Our main comparison of interest was between choice and yoked (i.e., no-choice) groups.
-To evaluate the self-controlled learning effect, Hedges' *g* for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies \textcolor{blue}{(see \textbf{Supplementary C} for the psychological data).
-Next, random effects meta-analyses were conducted on the retention test data}[^4] to generate a summary point estimate and 90% confidence intervals (CI) \textcolor{blue}{with Experiments 1 and 2 combined and also separate.
-The overall estimated effect when combining both experiments} was $g$ = .05 (favoring self-controlled) and 90% CI [-.12, .23].
-\textcolor{blue}{The overall estimated effect for Experiment 1 was $g$ = .03 (favoring self-controlled) and 90\% CI [-.19, .25].
-For Experiment 2, it was $g$ = .09 (favoring self-controlled) and 90\% CI [-.19, .37].}
+To evaluate the self-controlled learning effect, Hedges' *g* for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies (see **Supplementary C** for the psychological data).
+Next, random effects meta-analyses were conducted on the retention test data[^4] to generate a summary point estimate and 90% confidence intervals (CI) with Experiments 1 and 2 combined and also separate.
+The overall estimated effect when combining both experiments was $g$ = .05 (favoring self-controlled) and 90% CI [-.12, .23].
+The overall estimated effect for Experiment 1 was $g$ = .03 (favoring self-controlled) and 90% CI [-.19, .25].
+For Experiment 2, it was $g$ = .09 (favoring self-controlled) and 90% CI [-.19, .37].
 
@@
 All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not.
-Based on the \textcolor{blue}{combined overall estimate} the present experiments can be considered inconsistent with all effects larger than $g = \pm.23$.
+Based on the combined overall estimate the present experiments can be considered inconsistent with all effects larger than $g = \pm.23$.
 
@@
 Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results [@mckay2021].
-We estimated the overall effect of self-controlled practice in retention \textcolor{blue}{collapsed across experiments} to be significantly smaller than any effect larger than $g = .23$.
+We estimated the overall effect of self-controlled practice in retention collapsed across experiments to be significantly smaller than any effect larger than $g = .23$.
 This is consistent with the estimates from @mckay2021 after accounting for publication bias ($g =$ -.11 to .26), which suggested either no effect or a small effect in an unknown direction.
@@
 Nevertheless, the present results are incompatible with both perspectives.[^5] Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
-Similarly, self-controlled feedback schedules did not enhance error estimation skills \textcolor{blue}{compared to yoked schedules} (see **Supplementary B**) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
+Similarly, self-controlled feedback schedules did not enhance error estimation skills compared to yoked schedules (see **Supplementary B**) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
 Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose.
@@
 
-[^5]: \textcolor{blue}{Although the lack of performance improvements in Experiment 2 are compatible with the information-processing perspective, we do not interpret this as support for this view over the motivational one given the conclusions from McKay and colleagues' (in-press) recent meta-analysis.}
+[^5]: Although the lack of performance improvements in Experiment 2 are compatible with the information-processing perspective, we do not interpret this as support for this view over the motivational one given the conclusions from McKay and colleagues' (in-press) recent meta-analysis.
 
@@
 Participants in Experiment 2 who received binary feedback reported the lowest perceptions of competence and were also the only participants who did not show improvements in task performance from pre-test.
-\textcolor{blue}{The number of "hits" for the spatial and timing goals were quite low for all groups.
-Although this may have impacted perceptions of competence, the relatively low "hit" rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.} Future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
+The number of "hits" for the spatial and timing goals were quite low for all groups.
+Although this may have impacted perceptions of competence, the relatively low "hit" rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.
+Future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
 
@@
 
-\vspace{10ex}
+\clearpage
 

### 2022-08-22 docs/preprint/supplementary.tex
update: preprint and supplementary versions

@@
 \usepackage{csquotes}
-\usepackage{pdflscape}
 \usepackage{setspace}
@@
 If a 95\% confidence interval overlaps with zero, there is no significant difference between the two groups on that decile of the distribution.
-There were no significant differences for any decile in either experiment.}\label{fig:figS4}
+There were no significant differences for any decile in either experiment.}\label{fig:figS2}
 \end{figure}
 
-\newpage
+\clearpage
+
+\hypertarget{supplementary-b}{%
+\section{Supplementary B}\label{supplementary-b}}
+
+We asked all participants to estimate their performance on the spatial (Fig.
+\ref{fig:figS3}) and timing (Fig.
+\ref{fig:figS4}) components of the motor task after each trial in retention and transfer, similar to past research (e.g., Barros et al., 2019; Carter et al., 2014; Carter \& Patterson, 2012).
+Additionally, half of the participants in each group were randomly selected to also estimate their performance after each trial in the pre-test (not shown).
+To assess error estimation for the spatial and timing components, we first calculated the difference between a participant's estimated performance and their actual performance on each trial.
+Next, we computed total estimation error (EE) using the equation:
+\begin{equation}
+EE = \sqrt{CE^2 + VE^2}
+\end{equation}
+where \(CE\) was the average estimation bias and \(VE\) was the standard deviation of these errors. This approach is consistent with that used by Bruechert et al. (2003).
+
+\hypertarget{error-estimation-in-retention-and-transfer}{%
+\subsection{Error estimation in retention and transfer}\label{error-estimation-in-retention-and-transfer}}
+
+Total estimation error was generally lower in retention compared to transfer for both the spatial (Fig.
+\ref{fig:figS3}) and timing (Fig.
+\ref{fig:figS4}) domains in Experiments 1 and 2.
+For the spatial estimation error, we found a significant main effect of Test in Experiment 1, \(F(1,148) = 32.40\), \(p < .001\), \(\eta_{G}^2 = .060\), and in Experiment 2, \(F(1,74) = 18.79\), \(p < .001\), \(\eta_{G}^2 = .026\), with more accurate estimations in retention than transfer.
+Although there was a significant Choice x Feedback x Test interaction in Experiment 1 for timing estimation error, \(F(1,148) = 7.12\), \(p = .008\), \(\eta_{G}^2 < .001\), we did not decompose the interaction as the effect size estimate was less than \(.001\).
+There were no significant main effects or interactions for timing estimation error in Experiment 2.
+A potential explanation for the difference in estimation accuracy between retention and transfer for the spatial component and not the the timing component is that only the spatial goal changed.
+Specifically, it was 40 deg in retention and 60 deg in transfer whereas the timing goal remained 225 ms in both tests.
+
+\clearpage
+
+\begin{figure}
+
+{\centering \includegraphics{../../figs/figS3}
+
+}
+
+\caption{\small \normalfont \onehalfspacing \textbf{Total spatial error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.}\label{fig:figS3}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics{../../figs/figS4}
+
+}
+
+\caption{\small \normalfont \onehalfspacing \textbf{Total timing error estimation data.} Boxplots of retention and transfer data from all participants for Experiment 1 \textbf{(A)} and Experiment 2 \textbf{(B)}.
+The Choice with error feedback (Choice+Error) group is shown in dark blue, the Choice with graded feedback (Choice+Graded) group is shown in light blue, the Choice with binary feedback (Choice+Binary) group is shown in green, the Yoked with error feedback (Yoked+Error) group is shown in red, the Yoked with graded feedback (Yoked+Graded) group is shown in yellow, and the Yoked with binary feedback (Yoked+Binary) group is shown in purple.
+Boxplots represent 25th, 50th, and 75th percentiles, and the solid black line denotes the group mean.
+Grey connected dots represent individual data for participants in each group.
+Individual data of 1 participant in each of the Choice+Error, Yoked+Error, and Yoked+Binary groups is not shown as their error exceeded 500 ms.}\label{fig:figS4}
+\end{figure}
+
+\clearpage
+
+\hypertarget{development-of-error-estimation-skills}{%
+\subsection{Development of error estimation skills}\label{development-of-error-estimation-skills}}
+
+In Experiment 1, the subset of participants in each group who estimated their error after each pre-test trial improved the accuracy of their estimation skills throughout the experiment.
+We found significant main effects of Test for both the spatial, \(F(1.45,104.67) = 20.72\), \(p < .001\), \(\eta_{G}^2 = .144\), and timing, \(F(1.10,79.40) = 46.88\), \(p < .001\), \(\eta_{G}^2 = .060\), error estimations.
+For the spatial error estimations, Holm-Bonferonni post-hoc tests revealed that pre-test had higher error than retention and transfer (\(p\)'s \textless{} .001), and transfer had higher error than retention (\(p\) \textless{} .001).
+Similarly, timing error estimations were more accurate in retention and transfer compared to the pre-test (\(p\)'s \textless{} .001).
+In Experiment 2, none of the main effects or interactions were significant.
+
+\hypertarget{performance-accuracy-of-estimators-versus-non-estimators}{%
+\subsection{Performance accuracy of estimators versus non-estimators}\label{performance-accuracy-of-estimators-versus-non-estimators}}
+
+We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not.
+Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment.
+None of the main effect or interactions were significant in Experiment 1 or Experiment 2.
+A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation (Guadagnoli \& Kohl, 2001).
+Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation (e.g., Chiviacowsky \& Wulf, 2005).
+Given recent support for this idea (Bacelar et al., 2022), it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.
+
+\clearpage
+
+\hypertarget{supplementary-c}{%
+\section{Supplementary C}\label{supplementary-c}}
+
+Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity.
+Equivalence tests can be used to null findings more informative (Harms \& Lakens, 2018; Lakens, 2017; Schuirmann, 1987); however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons.
+First, we did not specify an \emph{a priori} smallest effect size of interest for any of the psychological constructs.
+Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol.
+Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points.
+We instead report mean differences and 90\% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments.
+The present experiments can be considered inconsistent with all effects larger than \(g = \pm\) the largest absolute confidence interval bound presented in Table \ref{tab:tableS1}.
+
+\vspace{1em}
+
+\begin{table}[h!]
+
+\caption{\label{tab:tableS1}Effect sizes for each questionnaire at each timepoint.}
+\resizebox{\linewidth}{!}{
+\fontsize{11}{13}\selectfont
+\begin{tabular}[t]{>{\raggedright\arraybackslash}p{11em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}>{\raggedright\arraybackslash}p{2em}>{\raggedright\arraybackslash}p{5em}}
+\toprule
+\multicolumn{1}{c}{ } & \multicolumn{2}{c}{After pre-test} & \multicolumn{2}{c}{After block 1} & \multicolumn{2}{c}{After block 6} & \multicolumn{2}{c}{Before retention} \\
+\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9}
+Questionnaire & $g$ & 90\% CI & $g$ & 90\% CI & $g$ & 90\% CI & $g$ & 90\% CI\\
+\midrule
+\addlinespace[0.3em]
+\multicolumn{9}{l}{\textbf{Experiment 1}}\\
+\hspace{1em}Perceived autonomy & .10 & {}[-.17, .36] & .22 & {}[-.05, .49] & .32 & {}[.05, .59] & .28 & {}[.01, .55]\\
+\hspace{1em}Perceived competence & .07 & {}[-.19, .34] & .10 & {}[-.17, .36] & -.12 & {}[-.38, .15] & -.11 & {}[-.37, .16]\\
+\hspace{1em}Intrinsic motivation & .27 & {}[0, .54] & .20 & {}[-.07, .46] & .17 & {}[-.09, .44] & .15 & {}[-.11, .42]\\
+\addlinespace[0.3em]
+\multicolumn{9}{l}{\textbf{Experiment 2}}\\
+\hspace{1em}Perceived autonomy & -.02 & {}[-.29, .24] & .12 & {}[-.15, .39] & .15 & {}[-.11, .42] & -.03 & {}[-.30, .23]\\
+\hspace{1em}Perceived competence & .12 & {}[-.15, .38] & -.08 & {}[-.35, .18] & .22 & {}[-.05, .49] & .10 & {}[-.16, .37]\\
+\hspace{1em}Intrinsic motivation & -.31 & {}[-.58, -.04] & -.22 & {}[-.48, .05] & -.20 & {}[-.46, .07] & -.17 & {}[-.43, .10]\\
+\bottomrule
+\multicolumn{9}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase. Negative values favor yoked group.}\\
+\end{tabular}}
+\end{table}
+
+\clearpage
 

### 2022-08-22 docs/accepted/manuscript.Rmd
init

--- 2022-08-22 docs/preprint/preprint.Rmd
@@
   - \usepackage{setspace}
-  - \usepackage{tcolorbox}
   #- \pagewiselinenumbers
@@
 ```
-
-\vspace{-1.1em}
-\begin{center}
-\begin{tcolorbox}[colframe=blue!75!black,boxrule=0.75pt,arc=5pt,width=4in]
-\centering\textcolor{blue!75!black}{In-press at \emph{Psychonomic Bulletin \& Review}}
-\end{tcolorbox}
-\end{center}
-\vspace{0.5em}
 
@@
 
+A typical acquisition trial (see Figure \@ref(fig:fig1)) began with the current trial number displayed (500 ms), followed by a visual "Get Ready!" and a visual go-signal (800 ms apart).
+Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
+The computer screen was blank while participants made their movement.
+When participants returned to the starting position, a red circle was displayed on the monitor.
+Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
+The number of remaining feedback trials was also displayed during this feedback delay interval.
+If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected via verbal response (or imposed on the yoked groups), it was also displayed for 3000 ms.
+
 \clearpage
@@
   kable_styling(position = "left",
-                font_size = 11,
-                latex_options = "scale_down") %>%
+                font_size = 11) %>%
   column_spec(1, width = "12em") %>%
@@
 ```
-
-A typical acquisition trial (see Figure \@ref(fig:fig1)) began with the current trial number displayed (500 ms), followed by a visual "Get Ready!" and a visual go-signal (800 ms apart).
-Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
-The computer screen was blank while participants made their movement.
-When participants returned to the starting position, a red circle was displayed on the monitor.
-Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-The number of remaining feedback trials was also displayed during this feedback delay interval.
-If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected via verbal response (or imposed on the yoked groups), it was also displayed for 3000 ms.
 
@@
   kable_styling(position = "left",
-                font_size = 11,
-                latex_options = "scale_down") %>%
+                font_size = 11) %>%
   column_spec(1, width = "15em") %>%
@@
 
-\clearpage
+\vspace{10ex}
 

### 2022-08-22 docs/accepted/manuscript.tex

--- 2022-08-14 docs/revision-1/r1_manuscript.tex
@@
 Knowledge of results feedback (Salmoni et al., 1984) can provide varying amounts of information to learners depending on its characteristics.
-Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., ``too far''), and binary feedback indicates only success or failure information (e.g., ``miss'') (Luft, 2014).\footnote{\textcolor{blue}{Others have referred to error feedback as quantitative feedback and graded feedback as qualitative feedback} (e.g., Magill \& Wood, 1986)\textcolor{blue}{.
-We use the terminology error, graded, and binary feedback because graded and binary feedback are different forms of qualitative feedback.}} When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
+Error feedback provides precise information about the magnitude and direction of the error (e.g., -42 cm), graded feedback provides coarse information about either the magnitude or direction of the error (e.g., ``too far''), and binary feedback indicates only success or failure information (e.g., ``miss'') (Luft, 2014).\footnote{Others have referred to error feedback as quantitative feedback and graded feedback as qualitative feedback (e.g., Magill \& Wood, 1986).
+We use the terminology error, graded, and binary feedback because graded and binary feedback are different forms of qualitative feedback.} When to provide this feedback is often decided by an external agent; however, this feedback decision can also be made by the learner, a form of self-controlled learning.
 These self-controlled feedback schedules have typically enhanced motor skill learning compared to yoked feedback schedules, wherein learners experience the feedback schedule created by a self-controlled counterpart, but without any choice (see Sanli et al., 2013; Ste-Marie et al., 2020 for reviews).
@@
 
-To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, \textcolor{blue}{we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acqusition of a novel motor task.
+To dissociate between the motivational and information-processing accounts of the self-controlled learning advantage, we manipulated the amount of information participants in choice and yoked (i.e., no-choice) groups experienced with their feedback schedule during acquisition of a novel motor task.
 In Experiment 1, participants received error or graded feedback to assess how high and moderate levels of informational value impact the self-controlled learning advantage.
 Given both error and graded feedback provide salient information about how to correct one's behavior relative to the task goal (i.e., both generate an error signal), in Experiment 2 we provided participants with binary feedback.
-As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.} Motor learning was assessed using delayed (\textasciitilde24 hours) retention and transfer tests.
+As binary feedback is devoid of information about the necessary change to improve one's behavior (i.e., does not generate an error signal), we could better isolate the motivational nature of choice to test between the two explanations for the self-controlled learning advantage.
+Motor learning was assessed using delayed (\textasciitilde24 hours) retention and transfer tests.
 If the OPTIMAL theory is correct, we hypothesized that the characteristics of one's feedback schedule \emph{would not matter} for the self-controlled learning advantage as this advantage arises from the opportunity for choice--a common feature of all choice groups.
@@
 One hundred and fifty-two right-handed (Oldfield, 1971), healthy adults participated in Experiment 1 (\(M_{age}\) = 20.64 years, \(SD_{age}\) = 2.45, 88 females).
-Sample size was determined from an \emph{a-priori} power analysis using the \emph{ANOVA: fixed effects, main effects and interactions} option in G*Power (Faul et al., 2009) with the following parameters: \(\alpha\) = 0.05, \(\beta\) = .20, \(f\) = 0.23, numerator = 1, and groups = \textcolor{blue}{4}.
+Sample size was determined from an \emph{a-priori} power analysis using the \emph{ANOVA: fixed effects, main effects and interactions} option in G*Power (Faul et al., 2009) with the following parameters: \(\alpha\) = 0.05, \(\beta\) = .20, \(f\) = 0.23, numerator = 1, and groups = 4.
 This revealed a required sample of 151 participants.
@@
 Prior to the pre-test, all participants received instructions about the task and its associated spatial and timing goals.
-Additionally, half of the participants in each group were randomly selected to \textcolor{blue}{verbally} estimate their performance on the spatial and timing goals after each trial in the pre-test.
+Additionally, half of the participants in each group were randomly selected to verbally estimate their performance on the spatial and timing goals after each trial in the pre-test.
 Only a subset of participants were asked to estimate their performance in pre-test to mitigate the potential that doing so would prompt participants to adopt this strategy during the experiment as error estimation has been suggested (e.g., Chiviacowsky \& Wulf, 2005) to be adopted spontaneously by participants controlling their feedback schedule.
@@
 Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-\textcolor{blue}{The number of remaining feedback trials was also displayed during this feedback delay interval.} If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected via \textcolor{blue}{verbal response} (or imposed on the yoked groups), it was also displayed for 3000 ms.
+The number of remaining feedback trials was also displayed during this feedback delay interval.
+If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected via verbal response (or imposed on the yoked groups), it was also displayed for 3000 ms.
 
@@
 On trials where feedback was not requested, a blank screen \textbf{(A)} was shown for 3000 ms.
-When feedback was selected via \textcolor{blue}{verbal response}, feedback was provided for both the spatial and timing goals according to their experimental group.
+When feedback was selected via verbal response, feedback was provided for both the spatial and timing goals according to their experimental group.
 The error feedback group \textbf{(B)} saw their constant error, the graded feedback group \textbf{(C)} saw either ``too far'' or ``too short'' for the spatial goal and ``too fast'' or ``too slow'' for the timing goal, and the binary feedback group \textbf{(D)} saw either ``hit'' or ``miss'' for the task goals.
@@
 Before the retention and transfer tests, participants were reminded about the task and its associated goals.
-All participants were asked to \textcolor{blue}{verbally} estimate their performance after each trial in retention and transfer.
-After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants \textcolor{blue}{verbally} answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.\footnote{\textcolor{blue}{The questionnaires can be found in the publicly available project repository in the materials directory.}} The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a; St.
+All participants were asked to verbally estimate their performance after each trial in retention and transfer.
+After the pre-test, trials 12 and 72 in acquisition, and before the delayed retention test, participants verbally answered a series of questions pertaining to perceived competence, task interest and enjoyment, and perceived autonomy.\footnote{The questionnaires can be found in the publicly available project repository in the materials directory.} The perceived competence and task interest and enjoyment questions were from the Intrinsic Motivation Inventory (McAuley et al., 1989; Ryan, 1982) and the perceived autonomy questions were used in earlier work (Barros et al., 2019; Carter \& Ste-Marie, 2017a; St.
 Germain et al., 2022).
@@
 A main effect of Test was also found for timing error, \(F(1.08,160.23) = 81.21\), \(p < .001\), \(\eta_{G}^2 = .245\), with pre-test performance more errorful than both retention and transfer (\(p\)'s \textless{} .001), and retention was less errorful than transfer (\(p\) \textless{} .001).
-\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,148) = .52$, $p = .471$, $\eta_{G}^2 = .001$, and timing, $F(1,148) = .32$, $p = .547$, $\eta_{G}^2 < .001$, error.}
+The main effect of Choice was not significant for both spatial, \(F(1,148) = .52\), \(p = .471\), \(\eta_{G}^2 = .001\), and timing, \(F(1,148) = .32\), \(p = .547\), \(\eta_{G}^2 < .001\), error.
 
@@
 \ref{fig:fig3}B) error did not change considerably from the pre-test to the retention and transfer tests.
-\textcolor{blue}{The main effect of Choice was not significant for both spatial, $F(1,74) = .23$, $p = .631$, $\eta_{G}^2 = .002$, and timing, $F(1,74) = .11$, $p = .738$, $\eta_{G}^2 = .001$, error.} All other main effects and interactions were also not significant.
+The main effect of Choice was not significant for both spatial, \(F(1,74) = .23\), \(p = .631\), \(\eta_{G}^2 = .002\), and timing, \(F(1,74) = .11\), \(p = .738\), \(\eta_{G}^2 = .001\), error.
+All other main effects and interactions were also not significant.
 
@@
 This was supported by a significant main effect of Block, \(F(2.41,357.13) = 60.18\), \(p < .001\), \(\eta_{G}^2 = .130\), where block 1 was less accurate than all other blocks (\(p\)'s \(< .001\)), block 2 was less accurate than all subsequent blocks (\(p\)'s \(\leq .021\)), and blocks 3 and 4 were more errorful than block 6 (\(p\)'s \(\leq .015\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .06$, $p = .813$ $\eta_{G}^2 < .001$.} Timing error also decreased during the acquisition period (Fig.
+The main effect of Choice was not significant, \(F(1,148) = .06\), \(p = .813\) \(\eta_{G}^2 < .001\).
+Timing error also decreased during the acquisition period (Fig.
 \ref{fig:fig2}B).
@@
 Timing error for the participants that received graded feedback was also reduced from block 1 in all subsequent blocks (\(p\)'s \(< .001\)); however, these participants continued to improve across acquisition blocks as block 2 was more errorful than blocks 3 to 6 (\(p\)'s \(\leq .028\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = .54$, $p = .465$ $\eta_{G}^2 = .002$.} Descriptives for the number of ``hit'' trials for each group are provided in Table \ref{tab:table2}.
+The main effect of Choice was not significant, \(F(1,148) = .54\), \(p = .465\) \(\eta_{G}^2 = .002\).
+Descriptives for the number of ``hit'' trials for each group are provided in Table \ref{tab:table2}.
 
@@
 \ref{fig:fig3}B) error remained relatively flat from block 1 to block 6 in the acquisition period.
-\textcolor{blue}{The main effect of Choice for both the spatial, $F(1,74) = .08$, $p = .776$, $\eta_{G}^2 < .001$, and the timing, $F(1,74) = .37$, $p = .542$, $\eta_{G}^2 = .004$, goals were not significant.
-Al other main effects and interactions for both task goals were not significant.} Descriptives for the number of ``hit'' trials for each group are provided in Table \ref{tab:table2}.
+The main effect of Choice for both the spatial, \(F(1,74) = .08\), \(p = .776\), \(\eta_{G}^2 < .001\), and the timing, \(F(1,74) = .37\), \(p = .542\), \(\eta_{G}^2 = .004\), goals were not significant.
+Al other main effects and interactions for both task goals were not significant.
+Descriptives for the number of ``hit'' trials for each group are provided in Table \ref{tab:table2}.
 
@@
 Perceived autonomy was higher after block 1 of acquisition compared to self-reported ratings prior to completing the retention test (\(p = .031\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 2.38$, $p = .125$, $\eta_{G}^2 = .014$.} Self-ratings for perceived competence (Fig.
+The main effect of Choice was not significant, \(F(1,148) = 2.38\), \(p = .125\), \(\eta_{G}^2 = .014\).
+Self-ratings for perceived competence (Fig.
 \ref{fig:fig2}D) were similar across groups after the pre-test, but then began to diverge after block 1 based on feedback characteristic.
@@
 Perceived competence scores were not significantly different after the pre-test (\(p = .232\)); however, perceptions of competence were significantly lower in those participants receiving graded feedback compared to error feedback at all other time points (\(p\)'s \(< .001\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 0.03$, $p = .862$, $\eta_{G}^2 < .001$.} Self-reported scores for intrinsic motivation (Fig.
+The main effect of Choice was not significant, \(F(1,148) = 0.03\), \(p = .862\), \(\eta_{G}^2 < .001\).
+Self-reported scores for intrinsic motivation (Fig.
 \ref{fig:fig2}E) generally decreased after block 1, which was supported by a main effect of Time, \(F(2.40,355.90) = 14.69\), \(p < .001\), \(\eta_{G}^2 = .012\).
@@
 Self-reported ratings were also lower before retention compared to after the pre-test (\(p = .043\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,148) = 1.69$, $p = .195$, $\eta_{G}^2 = .010$.}
+The main effect of Choice was not significant, \(F(1,148) = 1.69\), \(p = .195\), \(\eta_{G}^2 = .010\).
 
@@
 \ref{fig:fig3}C) were similar across all time points.
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.07$, $p = .792$, $\eta_{G}^2 < .001$.
-All other main effects and interactions were also not significant.} Perceptions of competence (Fig.
+The main effect of Choice was not significant, \(F(1,74) = 0.07\), \(p = .792\), \(\eta_{G}^2 < .001\).
+All other main effects and interactions were also not significant.
+Perceptions of competence (Fig.
 \ref{fig:fig3}D) showed a considerable decrease after the pre-test, \(F(1.85,136.91) = 106.10\), \(p < .001\), \(\eta_{g}^2 = .298\), where scores were significantly greater after the pre-test compared to all other time points (\(p\)'s \(< .001\)), and were higher after block 1 of acquisition than before retention (\(p = .004\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 0.25$, $p = .620$, $\eta_{G}^2 = .002$.} Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, \(F(2.37,175.55) = 15.31\), \(p < .001\), \(\eta_{G}^2 = .018\).
+The main effect of Choice was not significant, \(F(1,74) = 0.25\), \(p = .620\), \(\eta_{G}^2 = .002\).
+Self-ratings for intrinsic motivation generally decreased across time points, which was supported by a main effect of Time, \(F(2.37,175.55) = 15.31\), \(p < .001\), \(\eta_{G}^2 = .018\).
 Intrinsic motivation was higher after the pre-test than after block 6 of acquisition and before retention (\(p\)'s \(< .001\)), and higher after block 1 than after block 6 and before retention (\(p\)'s \(< .026\)).
-\textcolor{blue}{The main effect of Choice was not significant, $F(1,74) = 1.04$, $p = .312$, $\eta_{G}^2 < .013$.}
+The main effect of Choice was not significant, \(F(1,74) = 1.04\), \(p = .312\), \(\eta_{G}^2 < .013\).
 
@@
 Our main comparison of interest was between choice and yoked (i.e., no-choice) groups.
-To evaluate the self-controlled learning effect, Hedges' \emph{g} for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies \textcolor{blue}{(see \textbf{Supplementary C} for the psychological data).
-Next, random effects meta-analyses were conducted on the retention test data}\footnote{We report an estimate for retention tests to facilitate comparison to a recent meta-analysis (McKay et al., in-press) that produced estimated effects of self-controlled learning at retention specifically.} to generate a summary point estimate and 90\% confidence intervals (CI) \textcolor{blue}{with Experiments 1 and 2 combined and also separate.
-The overall estimated effect when combining both experiments} was \(g\) = .05 (favoring self-controlled) and 90\% CI {[}-.12, .23{]}.
-\textcolor{blue}{The overall estimated effect for Experiment 1 was $g$ = .03 (favoring self-controlled) and 90\% CI [-.19, .25].
-For Experiment 2, it was $g$ = .09 (favoring self-controlled) and 90\% CI [-.19, .37].}
+To evaluate the self-controlled learning effect, Hedges' \emph{g} for the spatial and timing goals were aggregated within each experiment while accounting for within-subject dependencies (see \textbf{Supplementary C} for the psychological data).
+Next, random effects meta-analyses were conducted on the retention test data\footnote{We report an estimate for retention tests to facilitate comparison to a recent meta-analysis (McKay et al., in-press) that produced estimated effects of self-controlled learning at retention specifically.} to generate a summary point estimate and 90\% confidence intervals (CI) with Experiments 1 and 2 combined and also separate.
+The overall estimated effect when combining both experiments was \(g\) = .05 (favoring self-controlled) and 90\% CI {[}-.12, .23{]}.
+The overall estimated effect for Experiment 1 was \(g\) = .03 (favoring self-controlled) and 90\% CI {[}-.19, .25{]}.
+For Experiment 2, it was \(g\) = .09 (favoring self-controlled) and 90\% CI {[}-.19, .37{]}.
 
@@
 All effect sizes outside this interval would be rejected by the two-one sided tests procedure while all values inside the interval would not.
-Based on the \textcolor{blue}{combined overall estimate} the present experiments can be considered inconsistent with all effects larger than \(g = \pm.23\).
+Based on the combined overall estimate the present experiments can be considered inconsistent with all effects larger than \(g = \pm.23\).
 
@@
 Consistent with these ideas, a recent meta-analysis provided compelling evidence that the self-controlled learning advantage is not robust and its prominence in the motor learning literature is due to selective publication of statistically significant results (McKay et al., in-press).
-We estimated the overall effect of self-controlled practice in retention \textcolor{blue}{collapsed across experiments} to be significantly smaller than any effect larger than \(g = .23\).
+We estimated the overall effect of self-controlled practice in retention collapsed across experiments to be significantly smaller than any effect larger than \(g = .23\).
 This is consistent with the estimates from McKay et al.
@@
 (in-press), motivational (i.e., OPTIMAL theory) versus information-processing explanations seem moot.
-Nevertheless, the present results are incompatible with both perspectives.\footnote{\textcolor{blue}{Although the lack of performance improvements in Experiment 2 are compatible with the information-processing perspective, we do not interpret this as support for this view over the motivational one given the conclusions from McKay and colleagues' (in-press) recent meta-analysis.}} Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
-Similarly, self-controlled feedback schedules did not enhance error estimation skills \textcolor{blue}{compared to yoked schedules} (see \textbf{Supplementary B}) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
+Nevertheless, the present results are incompatible with both perspectives.\footnote{Although the lack of performance improvements in Experiment 2 are compatible with the information-processing perspective, we do not interpret this as support for this view over the motivational one given the conclusions from McKay and colleagues' (in-press) recent meta-analysis.} Specifically, having choice opportunities during practice did not enhance perceptions of autonomy, competence, or intrinsic motivation in either experiment, inconsistent with OPTIMAL theory.
+Similarly, self-controlled feedback schedules did not enhance error estimation skills compared to yoked schedules (see \textbf{Supplementary B}) and choice did not interact with feedback characteristics, inconsistent with the information-processing perspective.
 Instead, the results from Experiments 1 and 2 suggest that feedback characteristics were a more important determinant of motor performance during acquisition and delayed tests of learning than the opportunity to choose.
@@
 Participants in Experiment 2 who received binary feedback reported the lowest perceptions of competence and were also the only participants who did not show improvements in task performance from pre-test.
-\textcolor{blue}{The number of "hits" for the spatial and timing goals were quite low for all groups.
-Although this may have impacted perceptions of competence, the relatively low "hit" rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.} Future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
+The number of ``hits'' for the spatial and timing goals were quite low for all groups.
+Although this may have impacted perceptions of competence, the relatively low ``hit'' rate did not seem to differentially impact intrinsic motivation as self-reported levels were quite similar for all groups.
+Future research is necessary to better understand this dissociation of informational and motivational influences of feedback characteristics and how it interacts with the task, individual, and environment.
 

### 2022-08-22 docs/accepted/supplementary.Rmd

--- 2022-08-14 docs/revision-1/r1_supplementary.Rmd
@@
 header-includes   :
-  - \usepackage{pdflscape}
+  #- \usepackage{pdflscape}
   - \usepackage{setspace}
@@
 
-\textcolor{blue}{We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not.
+We assessed whether performance accuracy differed between the subset of participants who were randomly assigned to estimate their error in pre-test compared to those who were not.
 Total error for the spatial and timing goals were analyzed in separate mixed ANOVAs (\emph{Acquisition}: 2 Estimation x 6 Block; \emph{Learning}: 2 Estimation x 2 Test) for each experiment.
 None of the main effect or interactions were significant in Experiment 1 or Experiment 2.
-A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation} [@guadagnoli2001]\textcolor{blue}{.
-Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation} [e.g., @chiviacowsky2005].
-\textcolor{blue}{Given recent support for this idea} [@bacelar2022]\textcolor{blue}{, it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.}
+A possible explanation for this finding is that estimating one's error is most effective when knowledge of results feedback is provided following the estimation [@guadagnoli2001].
+Another possible explanation is that self-controlled feedback schedules promote spontaneous error estimation [e.g., @chiviacowsky2005].
+Given recent support for this idea [@bacelar2022], it seems plausible that all participants in a self-controlled group in the present experiments engaged is some form of error estimation activities throughout acquisition when they deliberated about using (or not using) one of their limited feedback requests.
 
@@
 
-\textcolor{blue}{Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity.
-Equivalence tests can be used to null findings more informative} [@harms2018; @lakens2017; @schuirmann1987]\textcolor{blue}{; however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons.
-First, we did not specify an \emph{a priori} smallest effect size of interest for any of the psychological constructs.
+Contrary to the motivational perspective (i.e., OPTIMAL theory), we did not find that the opportunity to exercise choice over feedback during practice enhanced perceptions of competence, autonomy, or intrinsic motivation relative to not having this same choice opportunity.
+Equivalence tests can be used to null findings more informative [@harms2018; @lakens2017; @schuirmann1987]; however, a typical two one-sided test procedure may not be appropriate for this analysis for a couple reasons.
+First, we did not specify an *a priori* smallest effect size of interest for any of the psychological constructs.
 Second, the questionnaires were administered at various time points---after pre-test, after acquisition blocks 1 and 6, and before retention---during the experimental protocol.
 Given the choice and feedback manipulations were present at after acquisitions blocks 1 and 6 and not after pre-test or before retention, it would be inappropriate to aggregate across time points.
-We instead report mean differences and 90\% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments.
-The present experiments can be considered inconsistent with all effects larger than $g = \pm$ the largest absolute confidence interval bound presented in} Table \@ref(tab:tableS1).
+We instead report mean differences and 90% confidence intervals between choice and yoked groups at each questionnaire time point for both experiments.
+The present experiments can be considered inconsistent with all effects larger than $g = \pm$ the largest absolute confidence interval bound presented in Table \@ref(tab:tableS1).
 

### 2022-08-22 docs/preprint/preprint.tex

--- 2022-08-22 docs/accepted/manuscript.tex
@@
 \documentclass[
-  man, donotrepeattitle,floatsintext]{apa7}
+  doc, donotrepeattitle,floatsintext]{apa7}
 \usepackage{amsmath,amssymb}
@@
 \keywords{Self-controlled, Knowledge of results, OPTIMAL theory, Retention}
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
@@
 \usepackage{setspace}
+\usepackage{tcolorbox}
 \raggedbottom
@@
 \renewcommand\affiliation[1]{}
-\authorsnames[1, 1, 1, 1, 1, 1, {2,3,4,5}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
-\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Department of Mechanical Engineering, University of Delaware}, {Biomechanics and Movements Science Program, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
+\authorsnames[1, 1, 1, 1, 1, 1, {2,3}, 1]{Laura St. Germain, Brad McKay, Andrew Poskus, Allison Williams, Olena Leshchyshen, Sherry Feldman, Joshua G.A. Cashaback, Michael J. Carter\vspace{2ex}}
+\authorsaffiliations{{Department of Kinesiology, McMaster University}, {Department of Biomedical Engineering, University of Delaware}, {Interdisciplinary Neuroscience Graduate Program, University of Delaware}}
 \ifLuaTeX
@@
 \maketitle
+
+\vspace{-1.1em}
+\begin{center}
+\begin{tcolorbox}[colframe=blue!75!black,boxrule=0.75pt,arc=5pt,width=4in]
+\centering\textcolor{blue!75!black}{In-press at \emph{Psychonomic Bulletin \& Review}}
+\end{tcolorbox}
+\end{center}
+\vspace{0.5em}
 
@@
 All participants were shown a sample feedback display that corresponded to their experimental group and were asked to interpret it aloud for the researcher to verify understanding.
-
-A typical acquisition trial (see Figure \ref{fig:fig1}) began with the current trial number displayed (500 ms), followed by a visual ``Get Ready!'' and a visual go-signal (800 ms apart).
-Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
-The computer screen was blank while participants made their movement.
-When participants returned to the starting position, a red circle was displayed on the monitor.
-Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
-The number of remaining feedback trials was also displayed during this feedback delay interval.
-If feedback was not selected, a blank screen was displayed for 3000 ms.
-If feedback was selected via verbal response (or imposed on the yoked groups), it was also displayed for 3000 ms.
 
@@
 \caption{\label{tab:table1}Cronbach's alpha for each questionnaire at each timepoint.}
+\resizebox{\linewidth}{!}{
 \fontsize{11}{13}\selectfont
@@
 \multicolumn{5}{l}{\rule{0pt}{1em}\textit{Note.} Block 1 and 6 are from the acquisition phase.}\\
-\end{tabular}
+\end{tabular}}
 \end{table}
+
+A typical acquisition trial (see Figure \ref{fig:fig1}) began with the current trial number displayed (500 ms), followed by a visual ``Get Ready!'' and a visual go-signal (800 ms apart).
+Participants were free to begin their movement when ready following the visual go-signal (i.e., green circle) as this was not a reaction time task.
+The computer screen was blank while participants made their movement.
+When participants returned to the starting position, a red circle was displayed on the monitor.
+Following a 2000 ms feedback delay interval, the feedback decision prompt was presented for the self-controlled groups.
+The number of remaining feedback trials was also displayed during this feedback delay interval.
+If feedback was not selected, a blank screen was displayed for 3000 ms.
+If feedback was selected via verbal response (or imposed on the yoked groups), it was also displayed for 3000 ms.
 
@@
 \caption{\label{tab:table2}Total number of "hits" for the spatial and timing goals during acquisition for each group, and the minimum and maximum "hits" at the participant level within each group.}
+\resizebox{\linewidth}{!}{
 \fontsize{11}{13}\selectfont
@@
 \bottomrule
-\end{tabular}
+\end{tabular}}
 \end{table}

### 2022-08-22 scripts/supplementary-a.R
update: fix fig name order

@@ -10,7 +10,7 @@
 #   Brad McKay
 #   Mike Carter
 #
-# Last update: August 13 2022
+# Last update: August 21 2022
 #
 # Website: https://www.cartermaclab.org
 # -------------------------------------------
@@ -252,11 +252,11 @@ expt1_deg_choice_p <- rogme::plot_hd_links(
 expt1_deg_choice_p
 
 # Choice versus yoked combine the 3 plots
-figS3A <- expt1_deg_choice_shift_ps +
+figS1A <- expt1_deg_choice_shift_ps +
   expt1_deg_choice_p +
   expt1_deg_choice_psf[[1]] +
   patchwork::plot_layout(ncol = 1)
-figS3A
+figS1A
 
 
 # Timing goal choice shift function
@@ -338,11 +338,11 @@ expt1_ms_choice_p <- rogme::plot_hd_links(
 expt1_ms_choice_p
 
 # Choice versus yoked combine the 3 plots
-figS4A <- expt1_ms_choice_shift_ps +
+figS2A <- expt1_ms_choice_shift_ps +
   expt1_ms_choice_p +
   expt1_ms_choice_psf[[1]] +
   patchwork::plot_layout(ncol = 1)
-figS4A
+figS2A
 
 
 # EXPERIMENT 2
@@ -426,11 +426,11 @@ expt2_deg_choice_p <- rogme::plot_hd_links(
 expt2_deg_choice_p
 
 # Choice versus yoked combine the 3 plots
-figS3B <- expt2_deg_choice_shift_ps +
+figS1B <- expt2_deg_choice_shift_ps +
   expt2_deg_choice_p +
   expt2_deg_choice_psf[[1]] +
   patchwork::plot_layout(ncol = 1)
-figS3B
+figS1B
 
 
 # Timing goal choice shift function
@@ -512,18 +512,18 @@ expt2_ms_choice_p <- rogme::plot_hd_links(
 expt2_ms_choice_p
 
 # Choice versus yoked combine the 3 plots
-figS4B <- expt2_ms_choice_shift_ps +
+figS2B <- expt2_ms_choice_shift_ps +
   expt2_ms_choice_p +
   expt2_ms_choice_psf[[1]] +
   patchwork::plot_layout(ncol = 1)
-figS4B
+figS2B
 
 
 # MULTIPANEL PLOTS FOR SUPPLEMENTARY
 #
[…]

### 2022-08-22 scripts/supplementary-b.R

@@ -10,7 +10,7 @@
 #   Brad McKay
 #   Mike Carter
 #
-# Last update: August 14 2022
+# Last update: August 21 2022
 #
 # Website: https://www.cartermaclab.org
 # -------------------------------------------
@@ -269,7 +269,7 @@ expt2_estimation_pre_g <- expt2_estimation_pre_p %>%
 # in pre-test and those who were not asked to compare acquisition performance
 expt2_performance_est_tib <- expt2_performance_est_data %>%
   dplyr::mutate(est_id = dplyr::if_else(phase_id == 0, 1, 2)) %>%
-  dplyr::mutate(block_id = rep(rep(1:9, each = 12), 152)) %>%
+  dplyr::mutate(block_id = rep(rep(1:9, each = 12), 76)) %>%
   dplyr::mutate(ce2_deg = dplyr::if_else(phase_id != 4, (xi_deg - 40)^2,
                                          (xi_deg - 60)^2)) %>%
   dplyr::mutate(ce2_ms = (xi_ms - 225)^2)
@@ -530,7 +530,7 @@ expt1_ykg_ee_p <- expt1_estimation_all_p %>%
 
 
 # Spatial goal
-figS1_sce_deg <- ggplot2::ggplot(
+figS3_sce_deg <- ggplot2::ggplot(
   expt1_sce_ee_p,
   aes(x = phase_id,
       y = p_mean_ee_deg,
@@ -579,7 +579,7 @@ figS1_sce_deg <- ggplot2::ggplot(
     axis.text.x = element_blank()
   )
 
-figS1_scg_deg <- ggplot2::ggplot(
+figS3_scg_deg <- ggplot2::ggplot(
   expt1_scg_ee_p,
   aes(x = phase_id,
       y = p_mean_ee_deg,
@@ -628,7 +628,7 @@ figS1_scg_deg <- ggplot2::ggplot(
     axis.text.x = element_blank()
   )
 
-figS1_yke_deg <- ggplot2::ggplot(
+figS3_yke_deg <- ggplot2::ggplot(
   expt1_yke_ee_p,
   aes(x = phase_id,
       y = p_mean_ee_deg,
@@ -676,7 +676,7 @@ figS1_yke_deg <- ggplot2::ggplot(
[…]
